### 2019-08-01 paper/paper.tex
Initial Commit

% Created 2019-08-01 jeu. 17:56
% Intended LaTeX compiler: pdflatex
\documentclass[9pt, technote, a4paper]{ieeeconf}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{1} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{1}dehaeze.thomas@gmail.com}}
\date{2019-08-01}
\title{On the Design of Complementary Filters for Control}
\hypersetup{
 pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{1} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{1}dehaeze.thomas@gmail.com}},
 pdftitle={On the Design of Complementary Filters for Control},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

\maketitle
\bibliographystyle{IEEEtran}

\begin{abstract}
Abstract text to be done
\end{abstract}

\begin{IEEEkeywords}
complementary filters, h-infinity, feedback control
\end{IEEEkeywords}

\section{Introduction}
\label{sec:org9c365b8}
\label{sec:introduction}

Complementary filters: \cite{hua05_low_ligo}.

\section{H-Infinity synthesis of complementary filters}
\label{sec:org23f9d38}
  \label{sec:hinf_filters}
First order complementary filters are easy to synthesize. For instance, one can use the following filters
\begin{equation}
H_H(s) = \frac{s/\w_0}{1 + s/\w_0}; \quad H_L(s) = \frac{1}{1 + s/\w_0}
\end{equation}
with \(\w_0\) is the tuning parameter corresponding to the crossover frequency of the filters.

However, the manual design of higher order complementary filters is far more complex and we have to use an automatic synthesis technique.

As shown in Sec. \ref{sec:trans_perf}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.

Thus, the \(\mathcal{H}_\infty\) framework seems adapted and we here propose a technique to synthesis complementary filters while specifying uppers bounds on their magnitudes.

\subsection{\(\hinf\) problem formulation}
\label{sec:org3034ecb}
   \label{sec:hinf_conf}
In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.

The synthesis objective is to shape an high pass filter \(H_H\) and a low pass filter \(H_L\) while ensuring their complementary property (\(H_H + H_L = 1\)).

To do so, we define two weighting functions \(w_L\) and \(w_H\) that will respectively used to shape \(H_L\) and \(H_H\).

The synthesis problem is then
\begin{subnumcases}{\text{Find } H_L, H_H \text{ such that}}
  H_L \text{ and } H_H \text{ are stable} \label{eq:hinf_cond_stability}\\
  H_L + H_H = 1 \label{eq:hinf_cond_complementarity} \\
  |w_L H_L| \le 1 \quad \forall\omega \label{eq:hinf_cond_hl} \\
  |w_H H_H| \le 1 \quad \forall\omega \label{eq:hinf_cond_hh}
\end{subnumcases}

To express this synthesis problem into an \(\hinf\) synthesis problem, we define the following generalized plant \(P\) (also shown on Fig. \ref{fig:sf_hinf_filters_plant_b}):
\begin{equation}
\label{eq:generalized_plant}
  \colvec{w\\u} = P \colvec{z_H \\ z_L \\ v}; \quad P = \begin{bmatrix} w_H & -w_H \\ 0 & w_L \\ 1 & 0 \end{bmatrix}
\end{equation}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{./figs/sf_hinf_filters_plant_b.pdf}
\caption{\label{fig:sf_hinf_filters_plant_b}
Generalized plant for the synthesis of the complementary filters}
\end{figure}

The \(\hinf\) synthesis objective is then to design a stable filter \(H_L\) (Fig. \ref{fig:sf_hinf_filters_b}) such that the \(\mathcal{H}_\infty\) norm of the transfer function from \(w\) to \([z_H, \ z_L]\) is less than \(1\):
\begin{equation}
  \hnorm{\begin{matrix} (1 - H_L) w_H \\ H_L w_L \end{matrix}} \le 1
\end{equation}
Which is equivalent to
\begin{equation}
\label{eq:hinf_problem}
  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} < 1 \text{ by choosing } H_H = 1 - H_L
\end{equation}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{./figs/sf_hinf_filters_b.pdf}
\caption{\label{fig:sf_hinf_filters_b}
\(\hinf\text{-synthesis}\) of complementary filters}
\end{figure}

Performance conditions \eqref{eq:hinf_cond_hl} and \eqref{eq:hinf_cond_hl} are satisfied by \eqref{eq:hinf_problem}.
Complementary condition \eqref{eq:hinf_cond_complementarity} is satisfied by design: \(H_H = 1 - H_L\) and thus \(H_L + H_H = 1\).
The stability condition \eqref{eq:hinf_cond_stability} is guaranteed by the \(H_\infty\) synthesis (\textbf{reference}).

Using this synthesis method, we are then able to shape at the same time the high pass and low pass filters while ensuring their complementary.

\subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
\label{sec:org6b171b3}
As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
However, robust performance condition \eqref{eq:robust_perf_a} is not.

With the \(\mathcal{H}_\infty\) synthesis the condition \eqref{eq:hinf_problem} only ensure
\begin{align*}
  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} \le 1 &\Leftrightarrow \max_\omega \sqrt{|w_L H_L|^2 + |w_H H_H|^2} \le 1\\
                                                             &\Rightarrow |w_L H_L| + |w_H H_H| \le \sqrt{2} \quad \forall\omega
\end{align*}

And thus we have almost robust stability.

\subsection{Choice of the weighting functions}
\label{sec:orgced69fd}
   \label{sec:hinf_weighting_func}
We here give some advice on the choice of the weighting functions used for the synthesis of the complementary filters.

The shape should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.

However, one should be careful when designing the complementary filters, and should only use stable and minimum phase transfer functions.
The order of the weights should stay reasonably small as this will increase the complexity of the optimization problem.

One should not forget the fundamental limitations of feedback control such that \(S + T = 1\).
Similarly, we here have that \(H_L + H_H = 1\) which implies that \(H_L\) and \(H_H\) cannot be made small at the same time.

\subsection{Trade-off between performance and robustness}
\label{sec:orgafc6c17}

\subsection{Analytical formula of complementary filters}
\label{sec:orgd297585}
  \label{sec:analytical_complementary_filters}
To simplify the synthesis, one can use already synthesized filters

\begin{align}
  H_L(s) = \frac{1}{1 + \frac{s}{\omega_0}}\\
  H_H(s) = \frac{\frac{s}{\omega_0}}{1 + \frac{s}{\omega_0}}
\end{align}

\begin{align}
  H_L(s) &= \frac{(1+\alpha) (\frac{s}{\omega_0})+1}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}\\
  H_H(s) &= \frac{(\frac{s}{\omega_0})^2 \left((\frac{s}{\omega_0})+1+\alpha\right)}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}
\end{align}

\begin{align}
  H_L(s) &= \frac{\left(1+(\alpha+1)(\beta+1)\right) (\frac{s}{\omega_0})^2 + (1+\alpha+\beta)(\frac{s}{\omega_0}) + 1}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}\\
  H_H(s) &= \frac{(\frac{s}{\omega_0})^3 \left( (\frac{s}{\omega_0})^2 + (1+\alpha+\beta) (\frac{s}{\omega_0}) + (1+(\alpha+1)(\beta+1)) \right)}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}
\end{align}

\section{Discussion}
\label{sec:orgcc9e8fe}
\section{Conclusion}
\label{sec:org7919028}
\label{sec:conclusion}

\section{Acknowledgment}
\label{sec:orgecc7116}

\bibliography{ref}
\end{document}

### 2019-08-01 tikz/config.tex
Initial Commit

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[french, english]{babel} % Last language is main language

\usepackage{lmodern} % Latin Modern Font
\usepackage{gensymb} % Generic symbols for both text and math mode

\usepackage{standalone} % Used to generate standalone Tikz

\usepackage{amsmath}   % Main math Package
\usepackage{mathtools} % Extension package to amsmath
\usepackage{amsthm}    % Typesetting theorems (AMS style)
\usepackage{amsfonts}  % More fonts from the AMS
\usepackage{textcomp}  % provide many text symbols
\usepackage{steinmetz} % For phase symbol

\usepackage{xstring}  % Utils to manipulate strings
\usepackage{etoolbox} % Add basic if/then
\usepackage{esvect}   % Beautyfull vectors
\usepackage{graphicx} % Enhanced support for graphics
\usepackage{grffile}  % Used by matlab2tikz

\usepackage{microtype} % typographic tuning
\usepackage{setspace}  % for line spacing, e.g. \onehalfspacing
\usepackage{tabularx}  % table features
\usepackage{enumitem}  % for simple list modifications
\usepackage{booktabs}  % better table support

\usepackage{stackengine} %

\usepackage[load-configurations=abbreviations]{siunitx} % SI units
\sisetup{
    locale = US,
    detect-all,
    range-phrase=--,
    range-units=single
}

\usepackage{tikz}       % Tikz
\usepackage{tikzscale}  % Used to scale Tikz graphics
\usepackage{adjustbox}  % Used to proper positioning of tikz pictures
\usepackage{circuitikz} % Draw electronic circuits
\usepackage{pgfpages}   % Needed to use notes
\usepackage{pgfplots}   % Used to plot functions

\usetikzlibrary{arrows}                   % Arrow tip library
\usetikzlibrary{arrows.meta}              % Add some arrows
\usetikzlibrary{calc}                     % The library allows advanced Coordinate Calculations
\usetikzlibrary{intersections}            % calculate intersections of paths
\usetikzlibrary{matrix}                   %
\usetikzlibrary{patterns}                 %
\usetikzlibrary{shapes}                   % Defines circle and rectangle
\usetikzlibrary{shapes.geometric}         % Use for the shape diamond and isosceles triangle
\usetikzlibrary{snakes}                   % snake=coil and snake=zigzag using segment amplitude=10pt
\usetikzlibrary{positioning}              % Additional options for placing nodes
\usetikzlibrary{3d}                       % Plot 3D shapes
\usetikzlibrary{spy}                      % Creating a magnified area
\usetikzlibrary{decorations.text}         % Used to make text follows a curve
\usetikzlibrary{decorations.pathmorphing} % deformation of a path
\usetikzlibrary{decorations.markings}     % Used for spring and damper
\usetikzlibrary{babel}                    % A tiny library that make the interaction with the babel package easier
\usetikzlibrary{plotmarks}                % This library defines a number of plot marks
\usetikzlibrary{fit}                      % Used to make rectangle as nodes by specifying two points
\usetikzlibrary{backgrounds}              % Used to put things under others

\usepgfplotslibrary{patchplots}
\usepgfplotslibrary{groupplots}

\pgfplotsset{compat=newest}
\pgfplotsset{plot coordinates/math parser=false}

\newlength{\fheight}
\newlength{\fwidth}

\setlength{\fwidth}{85mm}
\setlength{\fheight}{112mm}

\tikzset{>=Stealth}
% Setup default Linewidth
\tikzset{every path/.style={line width=1pt}}

\usepackage{xcolor}% Color extension

\definecolor{colorblack}{rgb}{0, 0, 0}
\definecolor{colorblue}{rgb}{0, 0.4470, 0.7410}
\definecolor{colorred}{rgb}{0.8500, 0.3250, 0.0980}
\definecolor{coloryellow}{rgb}{0.9290, 0.6940, 0.1250}
\definecolor{colorpurple}{rgb}{0.4940, 0.1840, 0.5560}
\definecolor{colorgreen}{rgb}{0.4660, 0.6740, 0.1880}
\definecolor{colorcyan}{rgb}{0.3010, 0.7450, 0.9330}
\definecolor{colorbordeau}{rgb}{0.6350, 0.0780, 0.1840}

% Main color
\definecolor{maincolor}{RGB}{89, 9, 38}
\definecolor{secondcolor}{RGB}{20, 9, 89}

\tikzset{%
  block/.style n args={2}{%
    draw,
    fill=white,
    minimum width  = #1,
    minimum height = #2,
  },
  block/.default={1.2cm}{1.0cm}
}

\tikzstyle{branch}=[fill,shape=circle,minimum size=4pt,inner sep=0pt]
\tikzstyle{->top}=[-{Stealth[color=black, scale=0.8]}, draw=white, double=black, double distance=1pt, line width=1pt]
\tikzstyle{<-top}=[{stealth[color=black, scale=0.8]}-, draw=white, double=black, double distance=1pt, line width=1pt]

\tikzstyle{handwriten}=[decorate,decoration={random steps,amplitude=0.1pt,segment length=0.8pt}]

\tikzset{%
  DAC/.style={%
    draw,
    signal,
  }
}

\tikzset{%
  ADC/.style={%
    draw,
    signal,
    signal to = west,
  }
}

\tikzset{%
  gain right/.style={%
    draw,
    regular polygon,
    regular polygon sides = 3,
    inner sep = 2pt,
    shape border rotate=-90
  },
  gain left/.style={%
    draw,
    regular polygon,
    regular polygon sides = 3,
    inner sep = 2pt,
    shape border rotate=90
  },
  gain top/.style={%
    draw,
    regular polygon,
    regular polygon sides = 3,
    inner sep = 2pt,
    shape border rotate=0
  },
  gain bottom/.style={%
    draw,
    regular polygon,
    regular polygon sides = 3,
    inner sep = 2pt,
    shape border rotate=180
  },
}

\tikzset{% Add block with Circled operations
  addc/.style n args={5}{%
    draw,
    fill=white,
    circle,
    outer sep = 0pt,
    inner sep = 0pt,
    minimum size = 2em,
    execute at begin node={\LARGE $#1$},
    append after command={\pgfextra{\let\mainnode=\tikzlastnode}
      \ifx#2\empty\else
      node[draw, circle, outer sep=6pt, inner sep=0pt, above left] at (\mainnode.west) {$#2$}%
      \fi
      \ifx#3\empty\else
      node[draw, circle, outer sep=6pt, inner sep=0pt, above right] at (\mainnode.north) {$#3$}%
      \fi
      \ifx#4\empty\else
      node[draw, circle, outer sep=6pt, inner sep=0pt, below right] at (\mainnode.east) {$#4$}%
      \fi
      \ifx#5\empty\else
      node[draw, circle, outer sep=6pt, inner sep=0pt, below left] at (\mainnode.south) {$#5$}%
      \fi
      }
  },
  addc/.default={+}{}{}{}{},
}

\tikzset{% Add Block
  addb/.style n args={5}{%
    draw,
    fill=white,
    circle,
    outer sep = 0pt,
    inner sep = 0pt,
    minimum size = 2em,
    execute at begin node={\LARGE $#1$},
    append after command={\pgfextra{\let\mainnode=\tikzlastnode}
      \ifx#2\empty\else
      node[outer sep=2pt, inner sep=0pt, above left] at (\mainnode.west) {$#2$}%
      \fi
      \ifx#3\empty\else
      node[outer sep=2pt, inner sep=0pt, above right] at (\mainnode.north) {$#3$}%
      \fi
      \ifx#4\empty\else
      node[outer sep=2pt, inner sep=0pt, below right] at (\mainnode.east) {$#4$}%
      \fi
      \ifx#5\empty\else
      node[outer sep=2pt, inner sep=0pt, below left] at (\mainnode.south) {$#5$}%
      \fi
      }
  },
  addb/.default={+}{}{}{}{},
}

\pgfplotsset{grid style={black}}
\pgfplotsset{major grid style={black!30!white}}
\pgfplotsset{minor grid style={black!10!white}}
\pgfplotsset{xmajorgrids}
\pgfplotsset{ymajorgrids}

\pgfplotsset{separate axis lines=false} % draw axis as rectangle and not as 4 lines
\pgfplotsset{every outer x axis line/.append style={black}}
\pgfplotsset{every outer y axis line/.append style={black}}
\pgfplotsset{axis background/.style={fill=white}}
\pgfplotsset{axis x line*=bottom} % solid line on the bottom with thin on the top
\pgfplotsset{axis y line*=left} % solid line on the left with thin on the right

\pgfplotsset{every y tick label/.append style={font=\color{black}}}
\pgfplotsset{every y tick/.append style={black}}
\pgfplotsset{every x tick label/.append style={font=\color{black}}}
\pgfplotsset{every x tick/.append style={black}}

\pgfplotsset{scale only axis=true}

\pgfplotsset{ylabel absolute}

% https://tex.stackexchange.com/questions/54794/using-a-pgfplots-style-legend-in-a-plain-old-tikzpicture#54834

% argument #1: any options
\newenvironment{customlegend}[1][]{%
  \begingroup
  % inits/clears the lists (which might be populated from previous
  % axes):
  \csname pgfplots@init@cleared@structures\endcsname
  \pgfplotsset{#1}%
}{%
  % draws the legend:
  \csname pgfplots@createlegend\endcsname
  \endgroup
}%

% makes \addlegendimage available (typically only available within an
% axis environment):
\def\addlegendimage{\csname pgfplots@addlegendimage\endcsname}

% definition to insert numbers
% \pgfkeys{/pgfplots/number in legend/.style={%
%     /pgfplots/legend image code/.code={%
%       \node at (0.125,-0.0225){#1}; % <= changed x value
%     },%
%   },
% }
\pgfplotsset{
  every legend to name picture/.style={west}
}

\tikzstyle{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
\tikzstyle{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]

\pgfplotsset{
  /pgfplots/upperbound/.style 1 args={
    legend image code/.code={
      \draw[##1, upperbound]
        plot coordinates {
        (0cm,0cm)
        (0.6cm,0cm)
      }
    }
  }
}

\tikzset{%
  pole/.style{%
    color=red,
    cross out,
    draw,
    inner sep=0pt,
    outer sep=0pt,
    minimum size=#1pt
  },
  pole/.default={4}
}

\tikzset{%
  zero/.style{%
    color=red,
    circle,
    draw,
    inner sep=0pt,
    outer sep=0pt,
    minimum size=#1pt
  },
  zero/.default={4}
}

\tikzset{%
  spring/.style={%
    thick,
    decoration={
      zigzag,
      pre length  = #1cm,
      post length = #1cm,
      segment length = 6
    },
    decorate
  },
  spring/.default={0.2}
}

\tikzset{%
  coil/.style n args={2}{%
    thick,
    decoration={
      coil,
      pre length  = #1cm,
      post length = #2cm,
      segment length = 4
    },
    decorate
  },
  coil/.default={0.3}{0.3}
}

\tikzset{%
  damper/.style n args={2}{%
    thick,
    decoration={markings, mark connection node=dmp, mark=at position 0.5 with {
        \node (dmp) [thick,
                     inner sep = 0pt,
                     transform shape,
                     rotate  =-90,
                     minimum width  = #1pt,
                     minimum height = #2pt,
                     draw=none] {};
        \draw [thick] ($(dmp.north east)+(0.6*#2pt,0)$) -- (dmp.south east) -- (dmp.south west) -- ($(dmp.north west)+(0.6*#2pt,0)$);
        \draw [thick] ($(dmp.north)+(0,-0.3*#1pt)$) -- ($(dmp.north)+(0,0.3*#1pt)$);
      }
    },
    decorate
  },
  damper/.default={12}{3}
}

\tikzset{%
  actuator/.style n args={2}{%
    thick,
    draw=none,
    decoration={
      markings,
      mark connection node=my node,
      mark=at position .5 with {
        \node [draw, inner sep=0pt, minimum width=#1cm, minimum height=#2cm,
        transform shape, fill=white] (my node) {};
      },
      mark=at position .0 with {
        \draw[<-] (0, 0) -- (my node);
      },
      mark=at position 1.0 with {
        \draw[<-] (0, 0) -- (my node);
      }
    },
    decorate
  },
  actuator/.default={0.5}{0.2}
}

\tikzset{%
  ground/.style n args={2}{%
    fill,
    pattern = north east lines,
    draw = none,
    anchor = north,
    minimum width  = #1cm,
    minimum height = #2cm,
    append after command={
      (\tikzlastnode.north west) edge (\tikzlastnode.north east)
    }
  },
  ground/.default={2.5}{0.3}
}

\tikzset{%
  forcesensor/.style n args={2}{%
    rectangle,
    outer sep=0pt,
    inner sep=0pt,
    draw=black,
    fill=white!60!black,
    anchor=south,
    minimum width =#1cm,
    minimum height=#2cm,
    append after command={
      [every edge/.append style={
        thick,
        black,
      }]
      (\tikzlastnode.north west) edge (\tikzlastnode.south east)
      (\tikzlastnode.north east) edge (\tikzlastnode.south west)
    }
  },
  forcesensor/.default={2.0}{0.5}
}

\tikzset{%
  inertialsensor/.style={%
    rectangle,
    outer sep=0pt,
    inner sep=0pt,
    draw=black,
    fill=white!60!black,
    anchor=south east,
    minimum size=#1cm,
    append after command={
      [every edge/.append style={
        thick,
        black,
      }]
      (\tikzlastnode.north west) edge (\tikzlastnode.south east)
      (\tikzlastnode.north east) edge (\tikzlastnode.south west)
    }
  },
  inertialsensor/.default={0.3}
}

\newcommand{\AxisRotator}[1][rotate=0]{%
  \tikz [x=0.1cm,y=0.30cm,-stealth,#1] \draw (0,0) arc (-150:150:1 and 1);%
}

\tikzstyle{cross}=[path picture={
  \draw[black]
  (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);
}]

\tikzset{%
  piezo/.style n args={3}{%
    draw,
    rectangle,
    minimum width  = #1cm,
    minimum height = #2cm,
    fill=blue!10!white,
    anchor=center,
    append after command={
      [every edge/.append style={
        thick,
        black,
      }]
      \foreach \i in {1,...,#3}{
        (${\i/(1+#3)}*(\tikzlastnode.north west)+{(1+#3-\i)/(1+#3)}*(\tikzlastnode.south west)+0.1*(#1,0)$) edge (${\i/(1+#3)}*(\tikzlastnode.north east)+{(1+#3-\i)/(1+#3)}*(\tikzlastnode.south east)-0.1*(#1,0)$)
      }
    }
  },
  piezo/.default={2}{4}{10}
}

\def\voicecoil#1#2#3{
  % ======================
  % Parameters
  % ======================
  \def\voicecoilw{#1} % Total Width
  \def\voicecoilh{#2} % Total Height

  \def\magnetw{\voicecoilw} % Width of the magnet
  \def\magneth{\voicecoilh/1.4} % Height of the magnet

  \def\magnetwb{0.15*\magnetw} % Width of the borders of the magnet
  \def\magnetmw{0.15*\magnetw} % Width of the middle part of the magnet
  \def\magnetwg{0.5*\magnetw} % Width of the gap of the magnet

  \def\magnethl{\magnetwb} % Height of the low part of the magnet
  \def\magnetmh{0.15*\magneth} % Height of the middle part of the magnet
  \def\magnethg{0.2*\magneth} % Height of the gap of the magnet
  % ======================

  \begin{scope}[shift={(0.5*\voicecoilw, 0.5*\voicecoilh)}, rotate=#3, shift={(0, -0.5*\voicecoilh)}]
    % ======================
    % Magnet
    % ======================
    \draw[fill=white] (0, 0) -| ++(0.5*\magnetw, \magneth) -| ++(-0.5*\magnetw+0.5*\magnetwg, -\magnethg) -| (0.5*\magnetw-\magnetwb, \magnethl) -| (-0.5*\magnetw+\magnetwb, \magneth-\magnethg) -| (-0.5*\magnetwg, \magneth) -| (-0.5*\magnetw, 0) -- (cycle);
    \begin{scope}[shift={(0, \magnethl)}]
      \draw[fill=red]  (-0.5*\magnetmw, 0) rectangle (0.5*\magnetmw, \magnetmh);
      \draw[fill=blue] (-0.5*\magnetmw, \magnetmh) rectangle (0.5*\magnetmw, 2*\magnetmh);
      % Top conductive Magnet
      \draw[fill=white] (-0.5*\magnetmw, 2*\magnetmh) -| (0.5*\magnetmw, -\magnethl+\magneth-\magnethg) -| ++(0.1, \magnethg) -| ++(-0.2-\magnetmw, -\magnethg) -| (-0.5*\magnetmw, \magnetmh);
    \end{scope}
    % ======================

    % ======================
    % Coil
    % ======================
    \pgfmathsetmacro{\coilwidth}{0.5*0.5*\magnetmw+0.5*0.1+0.25*\magnetwg}%
    \draw[] ( \coilwidth, 0.5*\magneth) -- ++(0, 0.7*\magneth);
    \draw[] (-\coilwidth, 0.5*\magneth) -- ++(0, 0.7*\magneth);
    % Point on the coil
    \foreach \x in {0,1,...,9}
    {
      \node[circle,inner sep=0.6pt,fill] at ( \coilwidth, \x*0.7*\magneth/10+0.5*\magneth);
      \node[circle,inner sep=0.6pt,fill] at (-\coilwidth, \x*0.7*\magneth/10+0.5*\magneth);
    }
    \draw[fill=white] (-0.5*\magnetw, 1.2*\magneth) rectangle ++(\magnetw, \magnethg);
    % ======================

    % ======================
    % Coordinates
    % ======================
    % Force
    \coordinate[] (vc_force) at (0, \magneth-0.5*\magnethg);
    % Coil
    \coordinate[] (vc_coil) at (0, \voicecoilh);
    % Magnet
    \coordinate[] (vc_magnet) at (0, 0);
    % Coil Wires
    \coordinate[] (vc_wire_one) at ( \coilwidth, 1.2*\magneth);
    \coordinate[] (vc_wire_two) at (-\coilwidth, 1.2*\magneth);
    % ======================
  \end{scope}
}

\tikzset{%
  ->-/.style={
    decoration={
      markings,
      mark = at position #1 with {\arrow{>}
      }
    },
    postaction={decorate}
  }
}
\tikzset{%
  -<-/.style={
    decoration={
      markings,
      mark = at position #1 with {\arrow{<}
      }
    },
    postaction={decorate}
  }
}

\tikzset{%
  labelc/.style= {%
    draw,
    fill=white,
    shape=circle,
    inner sep=2pt,
    outer sep=6pt,
  }
}

### 2019-08-12 paper/paper.tex
Add one paper in the bibliography and start the introduction

@@
-% Created 2019-08-01 jeu. 17:56
+% Created 2019-08-12 lun. 16:02
 % Intended LaTeX compiler: pdflatex
@@
 \input{config.tex}
-\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{1} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{1}dehaeze.thomas@gmail.com}}
-\date{2019-08-01}
+\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
+\date{2019-08-12}
 \title{On the Design of Complementary Filters for Control}
 \hypersetup{
- pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{1} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{1}dehaeze.thomas@gmail.com}},
+ pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
  pdftitle={On the Design of Complementary Filters for Control},
@@
 \section{Introduction}
-\label{sec:org9c365b8}
+\label{sec:orgb15ebed}
   \label{sec:introduction}
+The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
+To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
+A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.
 
-Complementary filters: \cite{hua05_low_ligo}.
+The proper design of this particular kind of filter is of primary importance in a wide range of applications.
+Often, multiple sensors with different noise or dynamical properties are used to measure the same physical quantity.
+In such case, complementary filters can be used to merge the sensors and forms a "super sensor" that has gives a better estimate of the physical quantity over a wider bandwidth.
+This is called sensor blending or sensor fusion.
+
+This is widely used for the attitude estimation of unmanned aerial vehicles using various kind of sensors (accelerometers, gyroscopes, vision sensors, inclinometer) \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}.
+
+\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel} Fast position measurement of flexible structure
+
+\cite{matichard15_seism_isolat_advan_ligo} (relative displacement measurement at low frequencies with inertial at high frequencies)
+
+\cite{hua04_polyp_fir_compl_filter_contr_system}
+
+\cite{collette15_sensor_fusion_method_high_perfor}
+The design methods for such filters goes from simple analytical formulas
+
+\cite{corke04_inert_visual_sensin_system_small_auton_helic}
+
+\cite{min15_compl_filter_desig_angle_estim}
+\cite{jensen13_basic_uas}
+
+\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel}
+\cite{zimmermann92_high_bandw_orien_measur_contr}
+\cite{matichard15_seism_isolat_advan_ligo}
+\cite{collette15_sensor_fusion_method_high_perfor}
+
+\cite{hua05_low_ligo}
+\cite{hua04_polyp_fir_compl_filter_contr_system}
+\cite{matichard15_seism_isolat_advan_ligo}
+
+\cite{mahony08_nonlin_compl_filter_special_orthog_group}
+
+\cite{pascoal99_navig_system_desig_using_time}
+
+\cite{jensen13_basic_uas} (feedback system, P, PI, classical control theory for filter design)
+\cite{brown72_integ_navig_system_kalman_filter}
+
+\cite{pascoal99_navig_system_desig_using_time}
+
+\cite{min15_compl_filter_desig_angle_estim}
+Although
+In this paper, we propose
+The body of the paper consists of five parts followed by a conclusion.
 
 \section{H-Infinity synthesis of complementary filters}
-\label{sec:org23f9d38}
+\label{sec:org303afb5}
   \label{sec:hinf_filters}
@@
 \subsection{\(\hinf\) problem formulation}
-\label{sec:org3034ecb}
+\label{sec:org9dcb2b1}
    \label{sec:hinf_conf}
@@
 \subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
-\label{sec:org6b171b3}
+\label{sec:orgb7d25ea}
 As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
@@
 \subsection{Choice of the weighting functions}
-\label{sec:orgced69fd}
+\label{sec:org2d7aa5b}
    \label{sec:hinf_weighting_func}
@@
 \subsection{Trade-off between performance and robustness}
-\label{sec:orgafc6c17}
+\label{sec:org7af3efe}
 
 \subsection{Analytical formula of complementary filters}
-\label{sec:orgd297585}
+\label{sec:org477b4a4}
   \label{sec:analytical_complementary_filters}
@@
 \section{Discussion}
-\label{sec:orgcc9e8fe}
+\label{sec:org4fb9d01}
 \section{Conclusion}
-\label{sec:org7919028}
+\label{sec:orgecd9d50}
 \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:orgecc7116}
+\label{sec:org5cf5157}
 

### 2019-08-16 tikz/config.tex
Add many Tikz figures

@@
 
+\pgfplotsset{
+  every axis plot/.append style={line join=round},
+  every axis plot/.append style={line cap=round},
+}
+
 \pgfplotsset{grid style={black}}
@@
 
-\tikzstyle{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
-\tikzstyle{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]
+\pgfplotsset{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
+\pgfplotsset{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]
 
@@
 
-\tikzset{%
+\pgfplotsset{%
   pole/.style{%

### 2019-08-16 paper/paper.tex
Worked on the structure of the paper. All the figures are added

@@
-% Created 2019-08-12 lun. 16:02
+% Created 2019-08-16 ven. 22:07
 % Intended LaTeX compiler: pdflatex
@@
 \input{config.tex}
-\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
-\date{2019-08-12}
+\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
+\date{2019-08-16}
 \title{On the Design of Complementary Filters for Control}
 \hypersetup{
- pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
+ pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
  pdftitle={On the Design of Complementary Filters for Control},
@@
 \section{Introduction}
-\label{sec:orgb15ebed}
+\label{sec:org1592c87}
   \label{sec:introduction}
@@
 
-\section{H-Infinity synthesis of complementary filters}
-\label{sec:org303afb5}
-  \label{sec:hinf_filters}
+\section{Requirements on the Design of Complementary Filters}
+\label{sec:org045537e}
+\label{sec:requirements}
+
+\subsection{Sensor Fusion}
+\label{sec:org68eba14}
+
+Let's consider two sensors measuring the physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\) and with noise \(n_1\) and \(n_2\) respectively.
+
+\(H_1(s)\) and \(H_2(s)\) are complementary filters:
+\begin{equation}
+  H_1(s) + H_2(s) = 1
+\end{equation}
+
+\begin{equation}
+  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
+\end{equation}
+
+If we now consider sensors with perfect dynamics (\(G_1(s) = G_2(s) = 1\)), we have that the estimate of \(x\) using the two sensors are shown on figure \ref{fig:fusion_two_noisy_sensors_with_dyn_ter} is:
+
+\begin{equation}
+  \hat{x} = x + H_1 n_1 + H_2 n_2
+\end{equation}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/fusion_two_noisy_sensors_with_dyn_ter.pdf}
+\caption{\label{fig:fusion_two_noisy_sensors_with_dyn_ter}
+Sensor Fusion Architecture}
+\end{figure}
+
+We see that the complementary filters \(H_1(s)\) and \(H_2(s)\) operates only on the noise of the sensors.
+
+Thus, this architecture permits to filter each of the sensors without introducing any distortion in the physical quantity to measure.
+
+\begin{equation}
+  \delta x = \hat{x} - x = H_1 n_1 + H_2 n_2
+\end{equation}
+
+Usually, the two sensors have higher noise levels over distinct yet complementary frequency regions.
+The two complementary filters are used to combine the filtered noise and yield to a better estimate \(\hat{x}\) over a larger bandwidth.
+
+The noise of the super sensor is determine by the norm of the complementary filters.
+
+\subsection{Noise Sensor Filtering}
+\label{sec:orgce86efa}
+
+\subsection{Robustness of the Fusion}
+\label{sec:orgc52988d}
+
+\subsection{Upper bounds as a mathematical translation of the requirements}
+\label{sec:org4ab877a}
+\begin{quote}
+The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity
+\end{quote}
+
+\section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
+\label{sec:org4728e0e}
+\label{sec:hinf_method}
 First order complementary filters are easy to synthesize. For instance, one can use the following filters
@@
 
-As shown in Sec. \ref{sec:trans_perf}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
+As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
 
@@
 
-\subsection{\(\hinf\) problem formulation}
-\label{sec:org9dcb2b1}
+\subsection{\(\mathcal{H}_\infty\) problem formulation}
+\label{sec:orgdd7b8f5}
    \label{sec:hinf_conf}
@@
 \centering
-\includegraphics[scale=1]{./figs/sf_hinf_filters_plant_b.pdf}
-\caption{\label{fig:sf_hinf_filters_plant_b}
-Generalized plant for the synthesis of the complementary filters}
+\includegraphics[scale=1]{figs/h_infinity_robust_fusion.pdf}
+\caption{\label{fig:h_infinity_robust_fusion}
+Architecture used for the \(\mathcal{H}_\infty\) synthesis of complementary filters}
 \end{figure}
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{./figs/sf_hinf_filters_b.pdf}
-\caption{\label{fig:sf_hinf_filters_b}
-\(\hinf\text{-synthesis}\) of complementary filters}
-\end{figure}
-
 Performance conditions \eqref{eq:hinf_cond_hl} and \eqref{eq:hinf_cond_hl} are satisfied by \eqref{eq:hinf_problem}.
@@
 \subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
-\label{sec:orgb7d25ea}
+\label{sec:org8724b71}
 As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
@@
 \subsection{Choice of the weighting functions}
-\label{sec:org2d7aa5b}
+\label{sec:org04e66eb}
    \label{sec:hinf_weighting_func}
@@
 
-\subsection{Trade-off between performance and robustness}
-\label{sec:org7af3efe}
+\begin{equation}
+  W(s) = G_c * \left(\frac{\frac{1}{\omega_0}\sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}}{\frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{\left(\frac{G_\infty}{G_c}\right)^{\frac{2}{n}} - 1}} s + 1}\right)^n
+\end{equation}
 
-\subsection{Analytical formula of complementary filters}
-\label{sec:org477b4a4}
-  \label{sec:analytical_complementary_filters}
-To simplify the synthesis, one can use already synthesized filters
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/weight_formula.pdf}
+\caption{\label{fig:weight_formula}
+Amplitude of the proposed formula for the weighting functions}
+\end{figure}
 
-\begin{align}
-  H_L(s) = \frac{1}{1 + \frac{s}{\omega_0}}\\
-  H_H(s) = \frac{\frac{s}{\omega_0}}{1 + \frac{s}{\omega_0}}
-\end{align}
+\subsection{Example}
+\label{sec:orgf8bbd7b}
 
-\begin{align}
-  H_L(s) &= \frac{(1+\alpha) (\frac{s}{\omega_0})+1}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}\\
-  H_H(s) &= \frac{(\frac{s}{\omega_0})^2 \left((\frac{s}{\omega_0})+1+\alpha\right)}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}
-\end{align}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/weights_wl_wh.pdf}
+\caption{\label{fig:weights_wl_wh}
+Weighting Functions used for the \(\mathcal{H}_\infty\) Synthesis}
+\end{figure}
 
-\begin{align}
-  H_L(s) &= \frac{\left(1+(\alpha+1)(\beta+1)\right) (\frac{s}{\omega_0})^2 + (1+\alpha+\beta)(\frac{s}{\omega_0}) + 1}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}\\
-  H_H(s) &= \frac{(\frac{s}{\omega_0})^3 \left( (\frac{s}{\omega_0})^2 + (1+\alpha+\beta) (\frac{s}{\omega_0}) + (1+(\alpha+1)(\beta+1)) \right)}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}
-\end{align}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
+\caption{\label{fig:hinf_synthesis_results}
+Obtain Complementary Filters}
+\end{figure}
 
-\section{Discussion}
-\label{sec:org4fb9d01}
+\subsection{Synthesis of Three Complementary Filters}
+\label{sec:org916d6f2}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_filter_three_hinf.pdf}
+\caption{\label{fig:comp_filter_three_hinf}
+Architecture for the \(\mathcal{H}_\infty\) synthesis of three complementary filters}
+\end{figure}
+
+\section{Application to the design of}
+\label{sec:org7e3fe3e}
+\label{sec:application}
+
+\subsection{Specifications}
+\label{sec:org7f6a128}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/ligo_specifications.pdf}
+\caption{\label{fig:ligo_specifications}
+Specifications on the norms of the complementary filters}
+\end{figure}
+
+\subsection{Weighting functions design}
+\label{sec:orgdd7b46d}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/ligo_weights.pdf}
+\caption{\label{fig:ligo_weights}
+Weighting Functions used for the \(\mathcal{H}_\infty\) synthesis}
+\end{figure}
+
+\subsection{Comparison}
+\label{sec:orge13017e}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
+\caption{\label{fig:comp_fir_ligo_hinf}
+Comparison of the filters obtain with the \(\mathcal{H}_\infty\) synthesis and the FIR filters designed in \cite{hua05_low_ligo}}
+\end{figure}
+
 \section{Conclusion}
-\label{sec:orgecd9d50}
+\label{sec:org7a21636}
 \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:org5cf5157}
+\label{sec:org56fbb7d}
 

### 2019-08-16 paper/paper.tex
Reworked the "three complementary filters" part

@@
-% Created 2019-08-16 ven. 22:07
+% Created 2019-08-16 ven. 23:34
 % Intended LaTeX compiler: pdflatex
@@
 \section{Introduction}
-\label{sec:org1592c87}
+\label{sec:org1a92e6d}
   \label{sec:introduction}
@@
 \section{Requirements on the Design of Complementary Filters}
-\label{sec:org045537e}
+\label{sec:org8c17952}
 \label{sec:requirements}
@@
 \subsection{Sensor Fusion}
-\label{sec:org68eba14}
+\label{sec:org77e3eba}
+\label{sec:sensor_fusion}
 
@@
 \subsection{Noise Sensor Filtering}
-\label{sec:orgce86efa}
+\label{sec:org61f1e42}
+\label{sec:noise_filtering}
 
 \subsection{Robustness of the Fusion}
-\label{sec:orgc52988d}
+\label{sec:org88c9440}
+\label{sec:fusion_robustness}
 
 \subsection{Upper bounds as a mathematical translation of the requirements}
-\label{sec:org4ab877a}
-\begin{quote}
-The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity
-\end{quote}
+\label{sec:org2e8321f}
+\label{sec:requirements_upper_bounds}
+
+\textbf{The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity}
 
 \section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:org4728e0e}
+\label{sec:orgd9ea119}
 \label{sec:hinf_method}
-First order complementary filters are easy to synthesize. For instance, one can use the following filters
-\begin{equation}
-H_H(s) = \frac{s/\w_0}{1 + s/\w_0}; \quad H_L(s) = \frac{1}{1 + s/\w_0}
-\end{equation}
-with \(\w_0\) is the tuning parameter corresponding to the crossover frequency of the filters.
-
-However, the manual design of higher order complementary filters is far more complex and we have to use an automatic synthesis technique.
-
 As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
+As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
 
@@
 \subsection{\(\mathcal{H}_\infty\) problem formulation}
-\label{sec:orgdd7b8f5}
-   \label{sec:hinf_conf}
+\label{sec:orgecc21d9}
+\label{sec:hinf_synthesis}
+
 In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.
@@
 
-\subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
-\label{sec:org8724b71}
-As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
-However, robust performance condition \eqref{eq:robust_perf_a} is not.
+\subsection{Choice of the weighting functions}
+\label{sec:org6167188}
+\label{sec:hinf_weighting_func}
 
-With the \(\mathcal{H}_\infty\) synthesis the condition \eqref{eq:hinf_problem} only ensure
-\begin{align*}
-  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} \le 1 &\Leftrightarrow \max_\omega \sqrt{|w_L H_L|^2 + |w_H H_H|^2} \le 1\\
-                                                             &\Rightarrow |w_L H_L| + |w_H H_H| \le \sqrt{2} \quad \forall\omega
-\end{align*}
+We here give some advice on the design of the weighting functions used for the synthesis of the complementary filters using the \(\mathcal{H}_\infty\) method.
 
-And thus we have almost robust stability.
-
-\subsection{Choice of the weighting functions}
-\label{sec:org04e66eb}
-   \label{sec:hinf_weighting_func}
-We here give some advice on the choice of the weighting functions used for the synthesis of the complementary filters.
-
-The shape should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.
+The weighting functions should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.
 
@@
 
-One should not forget the fundamental limitations of feedback control such that \(S + T = 1\).
-Similarly, we here have that \(H_L + H_H = 1\) which implies that \(H_L\) and \(H_H\) cannot be made small at the same time.
+Moreover, the order of the complementary filters will be equal to the sum of the order of the weighting functions used.
+
+One should not forget the fundamental limitations imposed by the synthesis: \(H_L(s) + H_H(s) = 1\).
+This implies that \(H_L\) and \(H_H\) cannot be made small at the same time.
+
+We here propose a formula for the design of the weighting function \eqref{eq:weight_formula}.
 
 \begin{equation}
-  W(s) = G_c * \left(\frac{\frac{1}{\omega_0}\sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}}{\frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{\left(\frac{G_\infty}{G_c}\right)^{\frac{2}{n}} - 1}} s + 1}\right)^n
+\label{eq:weight_formula}
+  W(s) = \left(\frac{
+           \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
+         }{
+           \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
+         }}\right)^n
 \end{equation}
+with:
+\begin{itemize}
+\item \(G_0\) is the absolute gain at low frequency
+\item \(G_\infty\) is the absolute gain at high frequency
+\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
+\item \(n\) is the absolute slope of the filter, it is also equal to the order of the filter
+\end{itemize}
+
+The constrains are that \(G_0 < 1 < G_\infty\) and \(G_0 < G_c < G_\infty\) or that \(G_\infty < 1 < G_0\) and \(G_\infty < G_c < G_0\).
+
+The shape of the weight generated using the formula is shown on figure \ref{fig:weight_formula}.
 
@@
 \caption{\label{fig:weight_formula}
-Amplitude of the proposed formula for the weighting functions}
+Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
 \end{figure}
@@
 \subsection{Example}
-\label{sec:orgf8bbd7b}
+\label{sec:orgb30ba62}
+\label{sec:hinf_example}
+
+We are now using the proposed \(\mathcal{H}_\infty\) complementary filters synthesis method for a simple example.
+
+The goal is to design
+
+We use the formula \eqref{eq:weight_formula} for both \(w_L(s)\) and \(w_H(s)\).
+The parameters used are summarized on table \ref{tab:weights_params}. And the magnitude of the weighting functions are shown on figure \ref{fig:weights_wl_wh}.
+
+\begin{table}[!htpb]
+\caption{\label{tab:weights_params}
+Parameters used for the weighting functions}
+\centering
+\begin{tabular}{|l|X|X|}
+\hline
+Parameters & \(w_L\) & \(w_H\)\\
+\hline
+\(G_0\) & \(0.1\) & \(1000\)\\
+\hline
+\(G_\infty\) & \(1000\) & \(0.1\)\\
+\hline
+\(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
+\hline
+\(G_c\) & \(2\) & \(2\)\\
+\hline
+\(n\) & \(2\) & \(3\)\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \end{figure}
+
+After synthesis, the obtain filters are:
+\begin{align}
+  H_L(s) &= \frac{10^{-8} (s+6.6e^9) (s+3450)^2 (s^2 + 49s + 895)}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}\\
+  H_H(s) &= \frac{(s+6.6e^4) (s+160) (s+4)^3}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}
+\end{align}
+
+Their bode plot is shown on figure \ref{fig:hinf_synthesis_results}.
 
@@
 \subsection{Synthesis of Three Complementary Filters}
-\label{sec:org916d6f2}
+\label{sec:org415d7ce}
+\label{sec:hinf_three_comp_filters}
+
+We want:
+\begin{align*}
+  & |H_1 w_1| < 1, \quad \forall\omega\\
+  & |H_2 w_2| < 1, \quad \forall\omega\\
+  & |H_3 w_3| < 1, \quad \forall\omega\\
+  & H_1 + H_2 + H_3 = 1
+\end{align*}
+
+The \(\mathcal{H}_\infty\) objective is:
+\begin{align*}
+  & |H_1 w_1| < 1, \quad \forall\omega\\
+  & |H_2 w_2| < 1, \quad \forall\omega\\
+  & |(1 - H_1 - H_2) w_3| < 1, \quad \forall\omega\\
+\end{align*}
+
+And thus if we choose \(H_3 = 1 - H_1 - H_2\) we have solved the problem.
 
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/hinf_three_synthesis_results.pdf}
+\caption{\label{fig:hinf_three_synthesis_results}
+Figure caption}
+\end{figure}
+
 \section{Application to the design of}
-\label{sec:org7e3fe3e}
-\label{sec:application}
+\label{sec:org57876bd}
+\label{sec:application_ligo}
 
 \subsection{Specifications}
-\label{sec:org7f6a128}
+\label{sec:orgc79cee4}
+\label{sec:ligo_specifications}
 
@@
 \subsection{Weighting functions design}
-\label{sec:orgdd7b46d}
+\label{sec:org6e51da2}
+\label{sec:ligo_weights}
 
@@
 \subsection{Comparison}
-\label{sec:orge13017e}
+\label{sec:org06ff1a1}
+\label{sec:ligo_results}
 
@@
 \section{Conclusion}
-\label{sec:org7a21636}
+\label{sec:orga86d375}
 \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:org56fbb7d}
+\label{sec:org8d338b6}
 

### 2019-08-19 paper/paper.tex
Update few figures
Worked on the LIGO example

--- 2019-08-12 paper/paper.tex
@@
-% Created 2019-08-12 lun. 16:02
+% Created 2019-08-19 lun. 13:52
 % Intended LaTeX compiler: pdflatex
-\documentclass[9pt, technote, a4paper]{ieeeconf}
+\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amsmath,amssymb,amsfonts, cases}
+\usepackage[noadjust,space,compress]{cite}
+\usepackage{tabularx,siunitx,booktabs}
 \usepackage{algorithmic, graphicx, textcomp}
@@
 \setcounter{footnote}{1}
-\input{config.tex}
-\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
-\date{2019-08-12}
-\title{On the Design of Complementary Filters for Control}
+\renewcommand{\citedash}{--}
+\IEEEoverridecommandlockouts
+\author{Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} Unversité Libre de Bruxelles, BEAMS Department, Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}}
+\date{2019-08-19}
+\title{Design of Complementary Filters Using the \(\mathcal{H}_\infty\) Synthesis}
 \hypersetup{
- pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*} and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
- pdftitle={On the Design of Complementary Filters for Control},
+ pdfauthor={Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} Unversité Libre de Bruxelles, BEAMS Department, Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}},
+ pdftitle={Design of Complementary Filters Using the \(\mathcal{H}_\infty\) Synthesis},
  pdfkeywords={},
@@
 
-\begin{IEEEkeywords}
-complementary filters, h-infinity, feedback control
-\end{IEEEkeywords}
+\section{Introduction}
+\label{sec:org1868519}
+\label{sec:introduction}
+A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies.
+These filters are used when two or more sensors are measuring the same physical quantity with different noise characteristics.
+Unreliable frequencies of each sensors are filtered out by the complementary filters and combined to form a "super sensor" giving a better estimate of the physical quantity over a wider bandwidth.
+This technique is called sensor blending or sensor fusion and used for many applications.\par
+In \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}, such technique is used for the attitude estimation of Unmanned Aerial Vehicles (UAV) using various sensors (accelerometers, gyroscopes, vision sensors, \ldots{}).
+In \cite{collette15_sensor_fusion_method_high_perfor}, several sensor fusion configurations using different types of sensors (inertial, relative motion and force) have been discussed in order to increase the control bandwidth of active vibration isolation systems.
+Furthermore, sensor fusion is used for the low frequency isolation at the Laser Interferometer Gravitational-Wave Observator (LIGO), where inertial sensors are merged with relative sensors
+\cite{matichard15_seism_isolat_advan_ligo,hua04_polyp_fir_compl_filter_contr_system}. \par
+As the super sensor noise characteristics depends largely on the complementary filter norms, their proper design is of primary importance for sensor fusion performance.
+Different design methods have been developed.
+In \cite{corke04_inert_visual_sensin_system_small_auton_helic,jensen13_basic_uas,min15_compl_filter_desig_angle_estim}, analytical formulas for complementary filter transfer functions of first and second order have been proposed.
+Higher order complementary filters have been used in
+\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel,zimmermann92_high_bandw_orien_measur_contr,collette15_sensor_fusion_method_high_perfor}.
+In \cite{jensen13_basic_uas}, the sensitivity and complementary sensitivity transfer functions of a feedback architecture have been proposed to be used for complementary filters.
+The design of such filters can then benefits from the developments of classical control theory.
+Linear Matrix Inequalities (LMIs) are used in \cite{pascoal99_navig_system_desig_using_time} for the synthesis of complementary filters satisfying some frequency-like performance.
+A design method using linear least squares to optimize the coefficients of complementary filters is proposed in \cite{min15_compl_filter_desig_angle_estim}.
+Finally, high order Finite Impulse Response (FIR) complementary filters are used to merge sensors at LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system,matichard15_seism_isolat_advan_ligo}.
+The synthesis of such filter using convex optimization is presented in \cite{hua05_low_ligo}.
+\par
+Although many design methods of complementary filters have been proposed, we believe that it lacks a simple method of designing complementary filters [\ldots{}] specifying upper bounds.\par
+In this paper, we propose a synthesis method for the shaping of complementary filters using the \(\mathcal{H}_\infty\) norm.\par
+The section \ref{sec:requirements} gives a brief overview of sensor fusion using complementary filters and the associated requirements on their norms.
+In section \ref{sec:hinf_method}, a new method for designing complementary filters using the \(\mathcal{H}_\infty\) synthesis is proposed.
+In section \ref{sec:application_ligo}, two high order complementary filters are designed using the proposed method and compared with FIR filters used for sensor fusion at the LIGO.
+Our conclusions are drawn in the final section.
 
-\section{Introduction}
-\label{sec:orgb15ebed}
-  \label{sec:introduction}
-The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
-To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
-A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.
+\section{Complementary Filters Requirements}
+\label{sec:org8f2a1a9}
+\label{sec:requirements}
+\subsection{Sensor Fusion Architecture}
+\label{sec:org202d271}
+\label{sec:sensor_fusion}
 
-The proper design of this particular kind of filter is of primary importance in a wide range of applications.
-Often, multiple sensors with different noise or dynamical properties are used to measure the same physical quantity.
-In such case, complementary filters can be used to merge the sensors and forms a "super sensor" that has gives a better estimate of the physical quantity over a wider bandwidth.
-This is called sensor blending or sensor fusion.
+Let's consider two sensors measuring the same physical quantity \(x\) but with different dynamics (\(G_1(s)\) and \(G_2(s)\)) and noise characteristics (\(n_1\) and \(n_2\)).
 
-This is widely used for the attitude estimation of unmanned aerial vehicles using various kind of sensors (accelerometers, gyroscopes, vision sensors, inclinometer) \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}.
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel} Fast position measurement of flexible structure
-
-\cite{matichard15_seism_isolat_advan_ligo} (relative displacement measurement at low frequencies with inertial at high frequencies)
-
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-
-\cite{collette15_sensor_fusion_method_high_perfor}
-The design methods for such filters goes from simple analytical formulas
-
-\cite{corke04_inert_visual_sensin_system_small_auton_helic}
-
-\cite{min15_compl_filter_desig_angle_estim}
-\cite{jensen13_basic_uas}
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel}
-\cite{zimmermann92_high_bandw_orien_measur_contr}
-\cite{matichard15_seism_isolat_advan_ligo}
-\cite{collette15_sensor_fusion_method_high_perfor}
-
-\cite{hua05_low_ligo}
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-\cite{matichard15_seism_isolat_advan_ligo}
-
-\cite{mahony08_nonlin_compl_filter_special_orthog_group}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{jensen13_basic_uas} (feedback system, P, PI, classical control theory for filter design)
-\cite{brown72_integ_navig_system_kalman_filter}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{min15_compl_filter_desig_angle_estim}
-Although
-In this paper, we propose
-The body of the paper consists of five parts followed by a conclusion.
-
-\section{H-Infinity synthesis of complementary filters}
-\label{sec:org303afb5}
-  \label{sec:hinf_filters}
-First order complementary filters are easy to synthesize. For instance, one can use the following filters
+The signals from both sensors are fed into two complementary filters \(H_1(s)\) and \(H_2(s)\) and then combined to yield an estimate \(\hat{x}\) of \(x\) as shown on Fig.
+\ref{fig:fusion_super_sensor}.
 \begin{equation}
-H_H(s) = \frac{s/\w_0}{1 + s/\w_0}; \quad H_L(s) = \frac{1}{1 + s/\w_0}
-\end{equation}
-with \(\w_0\) is the tuning parameter corresponding to the crossover frequency of the filters.
-
-However, the manual design of higher order complementary filters is far more complex and we have to use an automatic synthesis technique.
-
-As shown in Sec. \ref{sec:trans_perf}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
-
-Thus, the \(\mathcal{H}_\infty\) framework seems adapted and we here propose a technique to synthesis complementary filters while specifying uppers bounds on their magnitudes.
-
-\subsection{\(\hinf\) problem formulation}
-\label{sec:org9dcb2b1}
-   \label{sec:hinf_conf}
-In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.
-
-The synthesis objective is to shape an high pass filter \(H_H\) and a low pass filter \(H_L\) while ensuring their complementary property (\(H_H + H_L = 1\)).
-
-To do so, we define two weighting functions \(w_L\) and \(w_H\) that will respectively used to shape \(H_L\) and \(H_H\).
-
-The synthesis problem is then
-\begin{subnumcases}{\text{Find } H_L, H_H \text{ such that}}
-  H_L \text{ and } H_H \text{ are stable} \label{eq:hinf_cond_stability}\\
-  H_L + H_H = 1 \label{eq:hinf_cond_complementarity} \\
-  |w_L H_L| \le 1 \quad \forall\omega \label{eq:hinf_cond_hl} \\
-  |w_H H_H| \le 1 \quad \forall\omega \label{eq:hinf_cond_hh}
-\end{subnumcases}
-
-To express this synthesis problem into an \(\hinf\) synthesis problem, we define the following generalized plant \(P\) (also shown on Fig. \ref{fig:sf_hinf_filters_plant_b}):
-\begin{equation}
-\label{eq:generalized_plant}
-  \colvec{w\\u} = P \colvec{z_H \\ z_L \\ v}; \quad P = \begin{bmatrix} w_H & -w_H \\ 0 & w_L \\ 1 & 0 \end{bmatrix}
+\label{eq:comp_filter_estimate}
+  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
 \end{equation}
@@
 \centering
-\includegraphics[scale=1]{./figs/sf_hinf_filters_plant_b.pdf}
-\caption{\label{fig:sf_hinf_filters_plant_b}
-Generalized plant for the synthesis of the complementary filters}
+\includegraphics[scale=1]{figs/fusion_super_sensor.pdf}
+\caption{\label{fig:fusion_super_sensor}
+Sensor Fusion Architecture}
 \end{figure}
 
-The \(\hinf\) synthesis objective is then to design a stable filter \(H_L\) (Fig.
-\ref{fig:sf_hinf_filters_b}) such that the \(\mathcal{H}_\infty\) norm of the transfer function from \(w\) to \([z_H, \ z_L]\) is less than \(1\):
+The complementary property of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies \eqref{eq:comp_filter}.
 \begin{equation}
-  \hnorm{\begin{matrix} (1 - H_L) w_H \\ H_L w_L \end{matrix}} \le 1
+\label{eq:comp_filter}
+  H_1(s) + H_2(s) = 1
 \end{equation}
-Which is equivalent to
+
+\subsection{Noise Sensor Filtering}
+\label{sec:org0ee5b17}
+\label{sec:noise_filtering}
+
+Let's first consider sensors with perfect dynamics
 \begin{equation}
-\label{eq:hinf_problem}
-  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} < 1 \text{ by choosing } H_H = 1 - H_L
+\label{eq:perfect_dynamics}
+  G_1(s) = G_2(s) = 1
+\end{equation}
+
+The estimate \(\hat{x}\) is then described by
+\begin{equation}
+\label{eq:estimate_perfect_dyn}
+  \hat{x} = x + H_1 n_1 + H_2 n_2
+\end{equation}
+
+The complementary filters \(H_1(s)\) and \(H_2(s)\) only operates on the noise of the sensors.
+Thus, this sensor fusion architecture permits to filter the noise of both sensors without introducing any distortion in the physical quantity to measure.
+
+The estimation error \(\delta x\) is defined by \eqref{eq:estimate_error}.
+\begin{equation}
+\label{eq:estimate_error}
+  \delta x \triangleq \hat{x} - x = H_1 n_1 + H_2 n_2
+\end{equation}
+
+As shown in \eqref{eq:noise_filtering_psd}, the Power Spectral Density (PSD) of the estimation error \(\Phi_{\delta x}\) depends both on the norms of the complementary filters and on the PSD of the noise sources \(\Phi_{n_1}\) and \(\Phi_{n_2}\).
+\begin{equation}
+\label{eq:noise_filtering_psd}
+  \Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2}
+\end{equation}
+
+Usually, the two sensors have higher noise levels over distinct yet complementary frequency regions.
+In order to lower the noise present in the estimation \(\hat{x}\), the norm \(|H_1|\) has to be made small when \(\Phi_{n_1}\) is larger than \(\Phi_{n_2}\) and \(|H_2|\) small when \(\Phi_{n_2}\) is larger than \(\Phi_{n_1}\).
+
+\subsection{Robustness of the Fusion}
+\label{sec:orgb942694}
+\label{sec:fusion_robustness}
+
+In practical systems, the sensors dynamics has always some level of uncertainty and cannot be inverted perfectly such that \(G_i(s) = 1\).
+
+This uncertainty can be represented as input multiplicative uncertainty as shown on Fig.
+\ref{fig:fusion_gain_mismatch_bis} where \(\Delta_i\) is any transfer function satisfying \(\|\Delta_i(j\omega)\|_\infty \le 1,\ \forall\omega\) and where \(|W_i(s)|\) represents the frequency dependent uncertainty level.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/fusion_gain_mismatch_bis.pdf}
+\caption{\label{fig:fusion_gain_mismatch_bis}
+Sensor Fusion Architecture with Sensor Dynamical Uncertainty}
+\end{figure}
+
+The super sensor dynamics \eqref{eq:super_sensor_dyn_uncertainty} is not longer equal to \(1\) and now depends on the sensor dynamic uncertainties \(W_i(s)\) as well as on the complementary filters \(H_i(s)\).
+\begin{equation}
+\label{eq:super_sensor_dyn_uncertainty}
+  \frac{\hat{x}}{x} = 1 + W_1(s) H_1(s) \Delta_1(s) + W_2(s) H_2(s) \Delta_2(s)
+\end{equation}
+
+In order to limit the phase and gain uncertainty of the super sensor, one may want to design the complementary filters to such that \eqref{eq:max_uncertainty_super_sensor} is satisfied.
+\begin{equation}
+\label{eq:max_uncertainty_super_sensor}
+  \begin{aligned}
+    & \left|W_1 H_1 \Delta_1\right| + \left|W_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_i\\
+    \Leftrightarrow & \left|W_1 H_1\right| + \left|W_2 H_2\right| \le \epsilon \quad \forall\omega
+  \end{aligned}
+\end{equation}
+
+Condition \eqref{eq:max_uncertainty_super_sensor} is equivalent as to bound the uncertainty set of the super sensor dynamics in the complex plane by a circle centered on \(1\) with a radius equal to \(\epsilon\) (Fig.
+\ref{fig:uncertainty_gain_phase_variation_bis}).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/uncertainty_gain_phase_variation_bis.pdf}
+\caption{\label{fig:uncertainty_gain_phase_variation_bis}
+Uncertainty set of the super sensor dynamics}
+\end{figure}
+
+The maximum phase added by the super sensor uncertainty \(\Delta\phi\) is then equal to \eqref{eq:max_phase_uncertainty}.
+\begin{equation}
+\label{eq:max_phase_uncertainty}
+    \Delta \phi = \arcsin\left( \epsilon \right)
+\end{equation}
+
+Limiting the phase added by the super sensor to \(\Delta \phi = \SI{30}{\degree}\) requires that \(H_1(s)\) and \(H_2(s)\) are designed such that \eqref{eq:max_uncertainty_super_sensor} is satisfied with \(\epsilon = \sin(\Delta\phi = \SI{30}{\degree}) = 0.5\).
+Thus the norm of the complementary filter \(|H_i|\) for sensor \(i\) should be made small at frequencies where its dynamic uncertainty \(|W_i|\) is large.\par
+
+As stated above, the requirements in terms of noise attenuation and robustness of the sensor fusion architecture can be termed as upper bounds on the norm of the complementary filters.
+
+\section{Complementary Filters Shaping using the \(\mathcal{H}_\infty\) Synthesis}
+\label{sec:orgb8fb6f7}
+\label{sec:hinf_method}
+As shown in Sec. \ref{sec:requirements}, most of the performance requirements for the design of the complementary filters can be expressed as upper bounds on the magnitude of the filters.
+
+Therefore, the \(\mathcal{H}_\infty\) Loop Shaping framework seems adapted for the synthesis of complementary filters.
+In this section, a technique for the synthesis complementary filters while specifying uppers bounds on their magnitudes using the \(\mathcal{H}_\infty\) synthesis is presented.
+\subsection{Synthesis of Complementary Filters as a \(\mathcal{H}_\infty\) problem}
+\label{sec:org3375829}
+\label{sec:hinf_synthesis}
+
+The synthesis objective is to shape the norm of two filters \(H_1(s)\) and \(H_2(s)\) while ensuring their complementary property \eqref{eq:comp_filter}.
+
+The synthesis problem is then to find stable transfer functions \(H_1(s)\) and \(H_2(s)\) such that conditions \eqref{eq:comp_filter_problem_form} are satisfied.
+\begin{subequations}
+\label{eq:comp_filter_problem_form}
+  \begin{align}
+  & H_1(s) + H_2(s) = 1 \label{eq:hinf_cond_complementarity} \\
+  & |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h1} \\
+  & |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h2}
+  \end{align}
+\end{subequations}
+where \(W_1(s)\) and \(W_2(s)\) are two weighting transfer functions chosen to shape the corresponding filters.
+
+In order to express this synthesis problem into a standard \(\mathcal{H}_\infty\) problem, we use the standard architecture shown on Fig.
+\ref{fig:h_infinity_robust_fusion} where the generalized plant \(P\) is described by \eqref{eq:generalized_plant}.
+\begin{equation}
+\label{eq:generalized_plant}
+  \begin{bmatrix} z_1 \\ z_2 \\ v \end{bmatrix} = P(s) \begin{bmatrix} w\\u \end{bmatrix}; \quad P(s) = \begin{bmatrix}W_1(s) & -W_1(s) \\ 0 & W_2(s) \\  1 & 0 \end{bmatrix}
 \end{equation}
@@
 \centering
-\includegraphics[scale=1]{./figs/sf_hinf_filters_b.pdf}
-\caption{\label{fig:sf_hinf_filters_b}
-\(\hinf\text{-synthesis}\) of complementary filters}
+\includegraphics[scale=1]{figs/h_infinity_robust_fusion.pdf}
+\caption{\label{fig:h_infinity_robust_fusion}
+Architecture used for the \(\mathcal{H}_\infty\) synthesis of complementary filters}
 \end{figure}
 
-Performance conditions \eqref{eq:hinf_cond_hl} and \eqref{eq:hinf_cond_hl} are satisfied by \eqref{eq:hinf_problem}.
-Complementary condition \eqref{eq:hinf_cond_complementarity} is satisfied by design: \(H_H = 1 - H_L\) and thus \(H_L + H_H = 1\).
-The stability condition \eqref{eq:hinf_cond_stability} is guaranteed by the \(H_\infty\) synthesis (\textbf{reference}).
+The \(\mathcal{H}_\infty\) filter design problem is then to find a stable filter \(H_1(s)\) which based on \(v\), generates a signal \(u\) such that the \(\mathcal{H}_\infty\) norm from \(w\) to \([z_1, \ z_2]\) is less than one \eqref{eq:hinf_syn_obj}.
+\begin{equation}
+\label{eq:hinf_syn_obj}
+  \left\|\begin{matrix} \left[1 - H_2(s)\right] W_1(s) \\ H_2(s) W_2(s) \end{matrix}\right\|_\infty \le 1
+\end{equation}
 
-Using this synthesis method, we are then able to shape at the same time the high pass and low pass filters while ensuring their complementary.
+Which is equivalent to \eqref{eq:hinf_problem} by defining \(H_1(s) \triangleq 1 - H_2(s)\).
+\begin{equation}
+\label{eq:hinf_problem}
+  \left\|\begin{matrix} H_1(s) W_1(s) \\ H_2(s) W_2(s) \end{matrix}\right\|_\infty \le 1
+\end{equation}
 
-\subsection{Control requirements as \(\mathcal{H}_\infty\) norm of complementary filters}
-\label{sec:orgb7d25ea}
-As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
-However, robust performance condition \eqref{eq:robust_perf_a} is not.
+The complementary condition \eqref{eq:hinf_cond_complementarity} is ensured by the definition of \(H_1(s)\).
+The conditions \eqref{eq:hinf_cond_h1} and \eqref{eq:hinf_cond_h2} on the shape of the filters are satisfied by \eqref{eq:hinf_problem}.
 
-With the \(\mathcal{H}_\infty\) synthesis the condition \eqref{eq:hinf_problem} only ensure
+Using this \(\mathcal{H}_\infty\) synthesis method, we are then able to shape complementary filters.
+
+\subsection{Choice of the weighting functions}
+\label{sec:orgd7d262d}
+\label{sec:hinf_weighting_func}
+
+The choice of the weighting functions is of primary importance for the success of the presented \(\mathcal{H}_\infty\) synthesis of complementary filters.
+
+First, only proper, stable and minimum phase transfer functions should be used.
+Second, the order of the weights should stay reasonably small as this will increase both the complexity of the optimization problem and the order of the synthesized complementary filters, the latter begin equal to the sum of the weighting functions orders.
+Third, one should not forget the fundamental limitations imposed by the complementary property: \(H_1(s) + H_2(s) = 1\).
+This implies for instance that \(|H_1(j\omega)|\) and \(|H_2(j\omega)|\) cannot be made small at the same time.
+
+When designing complementary filters, it is usually desired to specify the slope of the filter, its crossover frequency and its low and high frequency gains.
+To help with the design of the weighting functions such that the above specification are easily expressed, the formula \eqref{eq:weight_formula} is proposed.
+\begin{equation}
+\label{eq:weight_formula}
+  W(s) = \left( \frac{
+           \hfill{} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
+         }{
+           \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
+         }\right)^n
+\end{equation}
+where:
+\begin{itemize}
+\item \(G_0\) is the absolute gain at low frequency
+\item \(G_\infty\) is the absolute gain at high frequency
+\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
+\item \(n\) is the order of the weighting function as well as its slope between high and low frequency
+\end{itemize}
+
+The parameters \(G_0\), \(G_c\) and \(G_\infty\) should either satisfy condition \eqref{eq:cond_formula_1} or \eqref{eq:cond_formula_2}.
+\begin{subequations}
+\label{eq:condition_params_formula}
+  \begin{align}
+    G_0 < 1 < G_\infty \text{ and } G_0 < G_c < G_\infty \label{eq:cond_formula_1}\\
+    G_\infty < 1 < G_0 \text{ and } G_\infty < G_c < G_0 \label{eq:cond_formula_2}
+  \end{align}
+\end{subequations}
+
+The shape of the weighting function generated using \eqref{eq:weight_formula} is shown on Fig. \ref{fig:weight_formula}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/weight_formula.pdf}
+\caption{\label{fig:weight_formula}
+Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
+\end{figure}
+
+\subsection{Example}
+\label{sec:org018b699}
+\label{sec:hinf_example}
+
+Let's validate the proposed design method of complementary filters using the \(\mathcal{H}_\infty\) synthesis with a simple example.
+
+Both weighting functions \(W_1(s)\) and \(W_2(s)\) are designed using \eqref{eq:weight_formula}.
+The parameters used are summarized on table \ref{tab:weights_params} and the magnitude of the weighting functions are shown on Fig. \ref{fig:hinf_synthesis_results}.
+
+The blending frequency is chosen to be around \(\SI{10}{Hz}\).
+The slope of \(|H_1(j\omega)|\) is chosen to be \(-2\) above \(\SI{10}{Hz}\) by choosing \(n=2\) for \(W_1(s)\).
+The slope of \(|H_2(j\omega)|\) is chosen to be \(+3\) below \(\SI{10}{Hz}\) by choosing \(n=3\) for \(W_2(s)\).
+The order of the obtained complementary filters will thus be of order \(5\).
+
+\begin{table}[htbp]
+\caption{\label{tab:weights_params}
+Parameters used for \(W_1(s)\) and \(W_2(s)\)}
+\centering
+\begin{tabularx}{0.5\linewidth}{Xcc}
+\toprule
+Parameter & \(W_1(s)\) & \(W_2(s)\)\\
+\midrule
+\(G_0\) & \(0.1\) & \(1000\)\\
+\(G_\infty\) & \(1000\) & \(0.1\)\\
+\(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
+\(G_c\) & \(2\) & \(2\)\\
+\(n\) & \(2\) & \(3\)\\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+The bode plot of the obtained complementary filters is shown on Fig. \ref{fig:hinf_synthesis_results} and their transfer functions in the Laplace domain are shown below.
 \begin{align*}
-  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} \le 1 &\Leftrightarrow \max_\omega \sqrt{|w_L H_L|^2 + |w_H H_H|^2} \le 1\\
-                                                             &\Rightarrow |w_L H_L| + |w_H H_H| \le \sqrt{2} \quad \forall\omega
+  H_1(s) &= \frac{10^{-8} (s+6.6e^9) (s+3450)^2 (s^2 + 49s + 895)}{(s+6.6e^4) (s^2 + 106 s + 3e^3) (s^2 + 72s + 3580)}\\
+  H_2(s) &= \frac{(s+6.6e^4) (s+160) (s+4)^3}{(s+6.6e^4) (s^2 + 106 s + 3e^3) (s^2 + 72s + 3580)}
 \end{align*}
 
-And thus we have almost robust stability.
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
+\caption{\label{fig:hinf_synthesis_results}
+Weighting functions and Obtain Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
+\end{figure}
 
-\subsection{Choice of the weighting functions}
-\label{sec:org2d7aa5b}
-   \label{sec:hinf_weighting_func}
-We here give some advice on the choice of the weighting functions used for the synthesis of the complementary filters.
+\subsection{Generalization to the synthesis of Three Complementary Filters}
+\label{sec:orgcb75a24}
+\label{sec:hinf_three_comp_filters}
+In some applications, it may be needed to merge more than two sensors.
+In such case, it is necessary to design as many complementary filters \(H_i(s)\) as the number of sensors used.
+The synthesis problem is then to compute \(n\) stable transfer functions \(H_i(s)\) such that \eqref{eq:hinf_problem_gen} is satisfied.
+\begin{subequations}
+\label{eq:hinf_problem_gen}
+  \begin{align}
+  & \sum_{i=0}^n H_i(s) = 1 \label{eq:hinf_cond_compl_gen} \\
+  & \left| H_i(j\omega) \right| < \frac{1}{\left| W_i(j\omega) \right|}, \quad \forall \omega,\ i = 1 \dots n \label{eq:hinf_cond_perf_gen}
+  \end{align}
+\end{subequations}
+The synthesis architecture on Fig. \ref{fig:h_infinity_robust_fusion} can be generalized for the synthesis of a set of \(n\) complementary filters.
+For the synthesis of three complementary filters, the architecture used is shown on Fig. \ref{fig:comp_filter_three_hinf}.
 
-The shape should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.
+The \(\mathcal{H}_\infty\) synthesis objective applied on \(P(s)\) is to design two stable filters \(H_2(s)\) and \(H_3(s)\) such that the \(\mathcal{H}_\infty\) norm of the transfer function from \(w\) to \([z_1,\ z_2, \ z_3]\) is less than one \eqref{eq:hinf_syn_obj_three}.
+\begin{equation}
+\label{eq:hinf_syn_obj_three}
+  \left\| \begin{matrix} \left[1 - H_2(s) - H_3(s)\right] W_1(s) \\ H_2(s) W_2(s) \\ H_3(s) W_3(s) \end{matrix} \right\|_\infty \le 1
+\end{equation}
 
-However, one should be careful when designing the complementary filters, and should only use stable and minimum phase transfer functions.
-The order of the weights should stay reasonably small as this will increase the complexity of the optimization problem.
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_filter_three_hinf.pdf}
+\caption{\label{fig:comp_filter_three_hinf}
+Architecture for the \(\mathcal{H}_\infty\) synthesis of three complementary filters}
+\end{figure}
 
-One should not forget the fundamental limitations of feedback control such that \(S + T = 1\).
-Similarly, we here have that \(H_L + H_H = 1\) which implies that \(H_L\) and \(H_H\) cannot be made small at the same time.
+By choosing \(H_1(s) \triangleq 1 - H_2(s) - H_3(s)\), the proposed \(\mathcal{H}_\infty\) synthesis solves the design problem \eqref{eq:hinf_problem_gen}. \par
+An example is given to validate the method where three sensors are used in different frequency bands (up to \(\SI{1}{Hz}\), from \(1\) to \(\SI{10}{Hz}\) and above \(\SI{10}{Hz}\) respectively).
+Three weighting functions are designed using \eqref{eq:weight_formula} and shown by dashed curves on Fig. \ref{fig:hinf_three_synthesis_results}.
+The obtained complementary filters after synthesis are shown on Fig. \ref{fig:hinf_three_synthesis_results}.
 
-\subsection{Trade-off between performance and robustness}
-\label{sec:org7af3efe}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/hinf_three_synthesis_results.pdf}
+\caption{\label{fig:hinf_three_synthesis_results}
+Obtained three complementary filters}
+\end{figure}
 
-\subsection{Analytical formula of complementary filters}
-\label{sec:org477b4a4}
-  \label{sec:analytical_complementary_filters}
-To simplify the synthesis, one can use already synthesized filters
+\section{Application: Design of Complementary Filters used for the Active Vibration Isolation System at the LIGO}
+\label{sec:org8dbdcd2}
+\label{sec:application_ligo}
+Several complementary filters are used for the active isolation system at the LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
+The requirements on those filters are very tight and thus their design is complex.
+The approach taken in \cite{hua05_low_ligo} for the design of those filters is to use high order FIR filters and write the synthesis objective as a convex optimization problem.
+The obtained FIR filters are compliant with the requirements, however their implementation is complex as it requires a lot of computation power.
 
-\begin{align}
-  H_L(s) = \frac{1}{1 + \frac{s}{\omega_0}}\\
-  H_H(s) = \frac{\frac{s}{\omega_0}}{1 + \frac{s}{\omega_0}}
-\end{align}
+In order to demonstrate the effectiveness of the synthesis method presented in section \ref{sec:hinf_method}, complementary filters subject to the same requirements are synthesize.
+\subsection{Specifications}
+\label{sec:org684e797}
+\label{sec:ligo_specifications}
 
-\begin{align}
-  H_L(s) &= \frac{(1+\alpha) (\frac{s}{\omega_0})+1}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}\\
-  H_H(s) &= \frac{(\frac{s}{\omega_0})^2 \left((\frac{s}{\omega_0})+1+\alpha\right)}{\left((\frac{s}{\omega_0})+1\right) \left((\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1\right)}
-\end{align}
+As explained in section \ref{sec:requirements}, typical specifications for the complementary filters are on their magnitude.
 
-\begin{align}
-  H_L(s) &= \frac{\left(1+(\alpha+1)(\beta+1)\right) (\frac{s}{\omega_0})^2 + (1+\alpha+\beta)(\frac{s}{\omega_0}) + 1}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}\\
-  H_H(s) &= \frac{(\frac{s}{\omega_0})^3 \left( (\frac{s}{\omega_0})^2 + (1+\alpha+\beta) (\frac{s}{\omega_0}) + (1+(\alpha+1)(\beta+1)) \right)}{\left(\frac{s}{\omega_0} + 1\right) \left( (\frac{s}{\omega_0})^2 + \alpha (\frac{s}{\omega_0}) + 1 \right) \left( (\frac{s}{\omega_0})^2 + \beta (\frac{s}{\omega_0}) + 1 \right)}
-\end{align}
+The specifications are summarized below and explained in details in \cite{hua04_polyp_fir_compl_filter_contr_system}:
+\begin{itemize}
+\item From \(0\) to \(\SI{0.008}{Hz}\), the magnitude of the filter's transfer function should be less or equal to \(8 \times 10^{-4}\)
+\item Between \(\SI{0.008}{Hz}\) to \(\SI{0.04}{Hz}\), the filter should attenuate the input signal proportional to frequency cubed
+\item Between \(\SI{0.04}{Hz}\) to \(\SI{0.1}{Hz}\), the magnitude of the transfer function should be less than \(3\)
+\item Above \(\SI{0.1}{Hz}\), the magnitude of the complementary filter should be less than \(0.045\)
+\end{itemize}
 
-\section{Discussion}
-\label{sec:org4fb9d01}
+The specifications are represented by the dashed black curves on the bode plot in Fig. \ref{fig:ligo_weights}.
+
+\subsection{Weighting functions design}
+\label{sec:orgac7c8d0}
+\label{sec:ligo_weights}
+The weighting functions should be designed so that their inverse amplitude is as close as possible to the specifications in order to not over-constrain the synthesis problem.
+However, their order should not be too high as to limit both the complexity of the optimization problem and the order of the synthesize complementary filters.
+
+For the weight function corresponding to the low pass filter \(w_L(s)\), a Type I Chebyshev filter of order \(20\) is used.
+For the one corresponding to the high pass filter \(w_H(s)\), a \(7^{\text{th}}\) order transfer function gives satisfactory results.
+The magnitudes of the inverse of the weighting functions are shown on Fig. \ref{fig:ligo_weights}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/ligo_weights.pdf}
+\caption{\label{fig:ligo_weights}
+Specification and Weighting Functions used for the \(\mathcal{H}_\infty\) synthesis}
+\end{figure}
+
+\subsection{\(\mathcal{H}_\infty\) Synthesis}
+\label{sec:org9dfd8e0}
+\label{sec:ligo_results}
+
+The \(\mathcal{H}_\infty\) synthesis is performed using the architecture of Fig. \ref{eq:generalized_plant}.
+The complementary filters obtained are of order \(27\).
+Their bode plot is compared on Fig. \ref{fig:comp_fir_ligo_hinf} with the FIR filters of order 512 obtained in \cite{hua05_low_ligo}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
+\caption{\label{fig:comp_fir_ligo_hinf}
+Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with the \(\mathcal{H}_\infty\) synthesis (dashed)}
+\end{figure}
+
 \section{Conclusion}
-\label{sec:orgecd9d50}
+\label{sec:org30078db}
 \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:org5cf5157}
+\label{sec:orgf4d440c}
+This research benefited from a FRIA grant from the French Community of Belgium.
 

### 2019-08-20 matlab/matlab/comp_filter_analytical.m
Re-run all the matlab computation. Change some variable and figure names.

@@ -1,391 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-freqs = logspace(-1, 3, 1000);
-
-% Result
-% Their bode plot is shown Fig. ref:fig:comp_filter_1st_order.
-
-
-w0 = 2*pi; % [rad/s]
-
-Hh1 = (s/w0)/((s/w0)+1);
-Hl1 = 1/((s/w0)+1);
-
-freqs = logspace(-2, 2, 1000);
-
-figure;
-% Magnitude
-ax1 = subaxis(2,1,1);
-hold on;
-set(gca,'ColorOrderIndex',1); plot(freqs, abs(squeeze(freqresp(Hh1, freqs, 'Hz'))));
-set(gca,'ColorOrderIndex',1); plot(freqs, abs(squeeze(freqresp(Hl1, freqs, 'Hz'))));
-set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
-set(gca, 'XTickLabel',[]);
-ylabel('Magnitude');
-hold off;
-% Phase
-ax2 = subaxis(2,1,2);
-hold on;
-set(gca,'ColorOrderIndex',1); plot(freqs, 180/pi*angle(squeeze(freqresp(Hh1, freqs, 'Hz'))));
-set(gca,'ColorOrderIndex',1); plot(freqs, 180/pi*angle(squeeze(freqresp(Hl1, freqs, 'Hz'))));
-set(gca,'xscale','log');
-yticks(-180:90:180);
-ylim([-180 180]);
-xlabel('Relative Frequency $\frac{\omega}{\omega_0}$'); ylabel('Phase [deg]');
-hold off;
-linkaxes([ax1,ax2],'x');
-xlim([freqs(1), freqs(end)]);
-
-
-
-% #+NAME: fig:comp_filter_1st_order
-% #+CAPTION: Bode plot of first order complementary filter ([[./figs/comp_filter_1st_order.png][png]], [[./figs/comp_filter_1st_order.pdf][pdf]])
-% [[file:figs/comp_filter_1st_order.png]]
-
-
[…]

### 2019-08-20 matlab/matlab/comp_filters_analytical.m

@@ -1,142 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-freqs = logspace(-1, 3, 1000);
-
-% Analytical 1st order complementary filters
-% First order complementary filters are defined with following equations:
-% \begin{align}
-%   H_L(s) = \frac{1}{1 + \frac{s}{\omega_0}}\\
-%   H_H(s) = \frac{\frac{s}{\omega_0}}{1 + \frac{s}{\omega_0}}
-% \end{align}
-
-% Their bode plot is shown figure [[fig:comp_filter_1st_order]].
-
-
-w0 = 2*pi; % [rad/s]
-
-Hh1 = (s/w0)/((s/w0)+1);
-Hl1 = 1/((s/w0)+1);
-
-freqs = logspace(-2, 2, 1000);
-
-figure;
-% Magnitude
-ax1 = subaxis(2,1,1);
-hold on;
-set(gca,'ColorOrderIndex',1); plot(freqs, abs(squeeze(freqresp(Hh1, freqs, 'Hz'))));
-set(gca,'ColorOrderIndex',1); plot(freqs, abs(squeeze(freqresp(Hl1, freqs, 'Hz'))));
-set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
-set(gca, 'XTickLabel',[]);
-ylabel('Magnitude');
-hold off;
-% Phase
-ax2 = subaxis(2,1,2);
-hold on;
-set(gca,'ColorOrderIndex',1); plot(freqs, 180/pi*angle(squeeze(freqresp(Hh1, freqs, 'Hz'))));
-set(gca,'ColorOrderIndex',1); plot(freqs, 180/pi*angle(squeeze(freqresp(Hl1, freqs, 'Hz'))));
-set(gca,'xscale','log');
-yticks(-180:90:180);
-ylim([-180 180]);
-xlabel('Relative Frequency $\frac{\omega}{\omega_0}$'); ylabel('Phase [deg]');
-hold off;
-linkaxes([ax1,ax2],'x');
-xlim([freqs(1), freqs(end)]);
-
-% Second Order Complementary Filters
-% We here use analytical formula for the complementary filters $H_L$ and $H_H$.
-
[…]

### 2019-08-20 matlab/matlab/comp_filters_ligo.m

@@ -4,65 +4,272 @@ clear; close all; clc;
 %% Intialize Laplace variable
 s = zpk('s');
 
-freqs = logspace(-3, 1, 1000);
+freqs = logspace(-3, 0, 1000);
 
 % Specifications
-% The specifications are:
-% 1. From $0$ to $0.008\text{ Hz}$,the magnitude of the filter’s transfer function should be less than or equal to $8 \times 10^{-3}$.
+% The specifications for the filters are:
+% 1. From $0$ to $0.008\text{ Hz}$,the magnitude of the filter’s transfer function should be less than or equal to $8 \times 10^{-3}$
 % 2. From $0.008\text{ Hz}$ to $0.04\text{ Hz}$, it attenuates the input signal proportional to frequency cubed
-% 3. Between $0.04\text{ Hz}$ and $0.1\text{ Hz}$, the magnitude of the transfer function should be less than 3.
-% 4. Above $0.1\text{ Hz}$, the maximum of the magnitude of the complement filter should be as close to zero as possible. In our system ,we would like to have the magnitude of the complementary filter to be less than $0.1$.
+% 3. Between $0.04\text{ Hz}$ and $0.1\text{ Hz}$, the magnitude of the transfer function should be less than 3
+% 4. Above $0.1\text{ Hz}$, the maximum of the magnitude of the complement filter should be as close to zero as possible. In our system, we would like to have the magnitude of the complementary filter to be less than $0.1$. As the filters obtained in cite:hua05_low_ligo have a magnitude of $0.045$, we will set that as our requirement
+
+% The specifications are translated in upper bounds of the complementary filters are shown on figure [[fig:ligo_specifications]].
 
 
[…]

### 2019-08-20 matlab/matlab/feedback_generate_comp_filters.m

@@ -1,58 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-freqs = logspace(-2, 2, 1000);
-
-% Loop Gain Design
-% Let's first define the loop gain $L$.
-
-wc = 2*pi*1;
-alpha = 2;
-
-L = (wc/s)^2 * (s/(wc/alpha) + 1)/(s/wc + alpha);
-
-figure;
-
-ax1 = subplot(2,1,1);
-plot(freqs, abs(squeeze(freqresp(L, freqs, 'Hz'))), '-');
-ylabel('Magnitude');
-set(gca, 'XScale', 'log');
-set(gca, 'YScale', 'log');
-
-ax2 = subplot(2,1,2);
-plot(freqs, 180/pi*phase(squeeze(freqresp(L, freqs, 'Hz'))), '--');
-xlabel('Frequency [Hz]'); ylabel('Phase [deg]');
-set(gca, 'XScale', 'log');
-ylim([-180, 0]);
-yticks([-360:90:360]);
-
-linkaxes([ax1,ax2],'x');
-xlim([freqs(1), freqs(end)]);
-xticks([0.1, 1, 10, 100, 1000]);
-
-% Complementary Filters Obtained
-% We then compute the resulting low pass and high pass filters.
-
-Hl = L/(L + 1);
-Hh = 1/(L + 1);
-
-alphas = [1, 2, 10];
-
-figure;
-hold on;
-for i = 1:length(alphas)
-  alpha = alphas(i);
-  L = (wc/s)^2 * (s/(wc/alpha) + 1)/(s/wc + alpha);
-  Hl = L/(L + 1);
-  Hh = 1/(L + 1);
-  set(gca,'ColorOrderIndex',i)
-  plot(freqs, abs(squeeze(freqresp(Hl, freqs, 'Hz'))), 'DisplayName', sprintf('$\\alpha = %.0f$', alpha));
-  set(gca,'ColorOrderIndex',i)
-  plot(freqs, abs(squeeze(freqresp(Hh, freqs, 'Hz'))), 'HandleVisibility', 'off');
-end
-set(gca, 'xscale', 'log'); set(gca, 'yscale', 'log');
-xlabel('Frequency [Hz]'); ylabel('Amplitude')
-legend('location', 'northeast');

### 2019-08-20 matlab/matlab/h_inf_synthesis_complementary_filters.m

@@ -6,89 +6,155 @@ s = zpk('s');
 
 freqs = logspace(-1, 3, 1000);
 
-% Weights
+% Design of Weighting Function
+
+% A formula is proposed to help the design of the weighting functions.
+
+% \begin{equation}
+%   W(s) = \left(\frac{
+%            \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
+%          }{
+%            \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
+%          }}\right)^n
+% \end{equation}
+
+% The parameters permits to specify:
+% - the low frequency gain: $G_0 = lim_{\omega \to 0} |W(j\omega)|$
+% - the high frequency gain: $G_\infty = lim_{\omega \to \infty} |W(j\omega)|$
+% - the absolute gain at $\omega_0$: $G_c = |W(j\omega_0)|$
+% - the absolute slope between high and low frequency: $n$
+
+% The general shape of a weighting function generated using the formula is shown in figure [[fig:weight_formula]].
+
+% #+name: fig:weight_formula
+% #+caption: Amplitude of the proposed formula for the weighting functions
+% [[file:figs-tikz/weight_formula.png]]
 
 
-omegab = 2*pi*9;
-wH = (omegab)^2/(s + omegab*sqrt(1e-5))^2;
-omegab = 2*pi*28;
-wL = (s + omegab/(4.5)^(1/3))^3/(s*(1e-4)^(1/3) + omegab)^3;
+n = 2; w0 = 2*pi*11; G0 = 1/10; G1 = 1000; Gc = 1/2;
[…]

### 2019-08-20 matlab/matlab/optimal_comp_filters.m

@@ -1,102 +1,0 @@
-%% Clear Workspace and Close figures
-clear; close all; clc;
-
-%% Intialize Laplace variable
-s = zpk('s');
-
-freqs = logspace(-1, 3, 1000);
-
-% Noise of the sensors
-% Let's define the noise characteristics of the two sensors by choosing $W_1$ and $W_2$:
-% - Sensor 1 characterized by $W_1$ has low noise at low frequency (for instance a geophone)
-% - Sensor 2 characterized by $W_2$ has low noise at high frequency (for instance an accelerometer)
-
-
-omegac = 2*pi; G0 = 1e-2; Ginf = 1e-6;
-W1 = ((sqrt(G0))/(s/omegac + 1))^2;
-
-omegac = 100*2*pi; G0 = 1e-6; Ginf = 1e-2;
-W2 = ((sqrt(Ginf)*s/omegac + sqrt(G0))/(s/omegac + 1))^2/(1 + s/2/pi/4000)^2;
-
-omegac = 100*2*pi; G0 = 1e-5; Ginf = 1e-4;
-W1 = (Ginf*s/omegac + G0)/(s/omegac + 1)/(1 + s/2/pi/4000);
-
-omegac = 1*2*pi; G0 = 1e-3; Ginf = 1e-8;
-W2 = ((sqrt(Ginf)*s/omegac + sqrt(G0))/(s/omegac + 1))^2/(1 + s/2/pi/4000)^2;
-
-figure;
-hold on;
-plot(freqs, abs(squeeze(freqresp(W1, freqs, 'Hz'))), '-', 'DisplayName', '$W_1$');
-plot(freqs, abs(squeeze(freqresp(W2, freqs, 'Hz'))), '-', 'DisplayName', '$W_2$');
-set(gca, 'XScale', 'log'); set(gca, 'YScale', 'log');
-xlabel('Frequency [Hz]'); ylabel('Magnitude');
-hold off;
-xlim([freqs(1), freqs(end)]);
-legend('location', 'northeast');
-
-% H-Two Synthesis
-% We use the generalized plant architecture shown on figure [[fig:h_infinity_optimal_comp_filters]].
-
-% #+name: fig:h_infinity_optimal_comp_filters
-% #+caption: $\mathcal{H}_2$ Synthesis - Generalized plant used for the optimal generation of complementary filters
-% [[file:figs/h_infinity_optimal_comp_filters.png]]
-
[…]

### 2019-08-20 matlab/matlab/three_comp_filters.m

@@ -9,18 +9,22 @@ freqs = logspace(-2, 4, 1000);
 % Weights
 % First we define the weights.
 
-w1 = 0.35*(1 + s/2/pi/1)^2/(1 + s/2/pi/100)^2;
-w2 = 0.35*(1 + s/2/pi/1)^2/(sqrt(1e-4) + s/2/pi/1)^2*(1 + s/2/pi/100)^2/(1 + s/2/pi/10000)^2;
-w3 = 0.35*(1 + s/2/pi/100)^2/(sqrt(1e-4) + s/2/pi/100)^2;
+n = 2; w0 = 2*pi*1; G0 = 1/10; G1 = 1000; Gc = 1/2;
+W1 = (((1/w0)*sqrt((1-(G0/Gc)^(2/n))/(1-(Gc/G1)^(2/n)))*s + (G0/Gc)^(1/n))/((1/G1)^(1/n)*(1/w0)*sqrt((1-(G0/Gc)^(2/n))/(1-(Gc/G1)^(2/n)))*s + (1/Gc)^(1/n)))^n;
+
+W2 = 0.22*(1 + s/2/pi/1)^2/(sqrt(1e-4) + s/2/pi/1)^2*(1 + s/2/pi/10)^2/(1 + s/2/pi/1000)^2;
+
+n = 3; w0 = 2*pi*10; G0 = 1000; G1 = 0.1; Gc = 1/2;
+W3 = (((1/w0)*sqrt((1-(G0/Gc)^(2/n))/(1-(Gc/G1)^(2/n)))*s + (G0/Gc)^(1/n))/((1/G1)^(1/n)*(1/w0)*sqrt((1-(G0/Gc)^(2/n))/(1-(Gc/G1)^(2/n)))*s + (1/Gc)^(1/n)))^n;
 
 figure;
 hold on;
 set(gca,'ColorOrderIndex',1)
-plot(freqs, 1./abs(squeeze(freqresp(w1, freqs, 'Hz'))), '--', 'DisplayName', '$w_1$');
+plot(freqs, 1./abs(squeeze(freqresp(W1, freqs, 'Hz'))), '--', 'DisplayName', '$|W_1|^{-1}$');
 set(gca,'ColorOrderIndex',2)
-plot(freqs, 1./abs(squeeze(freqresp(w2, freqs, 'Hz'))), '--', 'DisplayName', '$w_2$');
[…]

### 2019-08-20 paper/paper.tex
Paper submission

@@
-% Created 2019-08-19 lun. 13:52
+% Created 2019-08-20 mar. 16:57
 % Intended LaTeX compiler: pdflatex
@@
 \IEEEoverridecommandlockouts
-\author{Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} Unversité Libre de Bruxelles, BEAMS Department, Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}}
-\date{2019-08-19}
-\title{Design of Complementary Filters Using the \(\mathcal{H}_\infty\) Synthesis}
+\author{Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} BEAMS Department, Free University of Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Corresponding Author.
+Email: {\tt\small thomas.dehaeze@esrf.fr}}}
+\date{2019-08-20}
+\title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis}
 \hypersetup{
- pdfauthor={Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} Unversité Libre de Bruxelles, BEAMS Department, Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}},
- pdftitle={Design of Complementary Filters Using the \(\mathcal{H}_\infty\) Synthesis},
+ pdfauthor={Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} BEAMS Department, Free University of Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Corresponding Author.
+Email: {\tt\small thomas.dehaeze@esrf.fr}}},
+ pdftitle={Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis},
  pdfkeywords={},
@@
 \begin{abstract}
-Abstract text to be done
+For many applications, large bandwidth and dynamic ranges are requiring to use several sensors, whose signals are combined using complementary filters.
+This paper presents a method for designing these complementary filters using \(\mathcal{H}_\infty\) synthesis that allows to shape the filter norms.
+This method is shown to be easily applicable for the synthesis of complex complementary filters.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:org1868519}
+\label{sec:orgf075900}
 \label{sec:introduction}
@@
 These filters are used when two or more sensors are measuring the same physical quantity with different noise characteristics.
-Unreliable frequencies of each sensors are filtered out by the complementary filters and combined to form a "super sensor" giving a better estimate of the physical quantity over a wider bandwidth.
-This technique is called sensor blending or sensor fusion and used for many applications.\par
-In \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}, such technique is used for the attitude estimation of Unmanned Aerial Vehicles (UAV) using various sensors (accelerometers, gyroscopes, vision sensors, \ldots{}).
-In \cite{collette15_sensor_fusion_method_high_perfor}, several sensor fusion configurations using different types of sensors (inertial, relative motion and force) have been discussed in order to increase the control bandwidth of active vibration isolation systems.
-Furthermore, sensor fusion is used for the low frequency isolation at the Laser Interferometer Gravitational-Wave Observator (LIGO), where inertial sensors are merged with relative sensors
+Unreliable frequencies of each sensor are filtered out by the complementary filters and then combined to form a super sensor giving a better estimate of the physical quantity over a wider bandwidth.
+This technique is called sensor fusion and is used in many applications.\par
+In \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}, various sensors (accelerometers, gyroscopes, vision sensors, etc.) are merged using complementary filters for the attitude estimation of Unmanned Aerial Vehicles (UAV).
+In \cite{collette15_sensor_fusion_method_high_perfor}, several sensor fusion configurations using different types of sensors are discussed in order to increase the control bandwidth of active vibration isolation systems.
+Furthermore, sensor fusion is used in the isolation systems of the Laser Interferometer Gravitational-Wave Observator (LIGO) to merge inertial sensors with relative sensors
 \cite{matichard15_seism_isolat_advan_ligo,hua04_polyp_fir_compl_filter_contr_system}. \par
-As the super sensor noise characteristics depends largely on the complementary filter norms, their proper design is of primary importance for sensor fusion performance.
-Different design methods have been developed.
-In \cite{corke04_inert_visual_sensin_system_small_auton_helic,jensen13_basic_uas,min15_compl_filter_desig_angle_estim}, analytical formulas for complementary filter transfer functions of first and second order have been proposed.
+As the super sensor noise characteristics largely depend on the complementary filter norms, their proper design is of primary importance for sensor fusion.
+In \cite{corke04_inert_visual_sensin_system_small_auton_helic,jensen13_basic_uas,min15_compl_filter_desig_angle_estim}, first and second order analytical formulas of complementary filters have been presented.
 Higher order complementary filters have been used in
 \cite{shaw90_bandw_enhan_posit_measur_using_measur_accel,zimmermann92_high_bandw_orien_measur_contr,collette15_sensor_fusion_method_high_perfor}.
-In \cite{jensen13_basic_uas}, the sensitivity and complementary sensitivity transfer functions of a feedback architecture have been proposed to be used for complementary filters.
-The design of such filters can then benefits from the developments of classical control theory.
+In \cite{jensen13_basic_uas}, the sensitivity and complementary sensitivity transfer functions of a feedback architecture have been proposed to be used as complementary filters.
+The design of such filters can then benefit from the classical control theory developments.
 Linear Matrix Inequalities (LMIs) are used in \cite{pascoal99_navig_system_desig_using_time} for the synthesis of complementary filters satisfying some frequency-like performance.
-A design method using linear least squares to optimize the coefficients of complementary filters is proposed in \cite{min15_compl_filter_desig_angle_estim}.
-Finally, high order Finite Impulse Response (FIR) complementary filters are used to merge sensors at LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system,matichard15_seism_isolat_advan_ligo}.
-The synthesis of such filter using convex optimization is presented in \cite{hua05_low_ligo}.
+Finally, a synthesis method of high order Finite Impulse Response (FIR) complementary filters using convex optimization has been developed in \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
 \par
-Although many design methods of complementary filters have been proposed, we believe that it lacks a simple method of designing complementary filters [\ldots{}] specifying upper bounds.\par
-In this paper, we propose a synthesis method for the shaping of complementary filters using the \(\mathcal{H}_\infty\) norm.\par
-The section \ref{sec:requirements} gives a brief overview of sensor fusion using complementary filters and the associated requirements on their norms.
-In section \ref{sec:hinf_method}, a new method for designing complementary filters using the \(\mathcal{H}_\infty\) synthesis is proposed.
-In section \ref{sec:application_ligo}, two high order complementary filters are designed using the proposed method and compared with FIR filters used for sensor fusion at the LIGO.
+Although many design methods of complementary filters have been proposed in the literature, no simple method that allows to shape the norm of the complementary filters is available.
+This paper presents a new design method of complementary filters based on \(\mathcal{H}_\infty\) synthesis.
+This design method permits to easily shape the norms of the generated filters.\par
+The section \ref{sec:requirements} gives a brief overview of sensor fusion using complementary filters and explains how the typical requirements for such fusion can be expressed as upper bounds on the filters norms.
+In section \ref{sec:hinf_method}, a new design method for the shaping of complementary filters using \(\mathcal{H}_\infty\) synthesis is proposed.
+In section \ref{sec:application_ligo}, the method is used to design complex complementary filters that are used for sensor fusion at the LIGO.
 Our conclusions are drawn in the final section.
@@
 \section{Complementary Filters Requirements}
-\label{sec:org8f2a1a9}
+\label{sec:orgcfd59fa}
 \label{sec:requirements}
 \subsection{Sensor Fusion Architecture}
-\label{sec:org202d271}
+\label{sec:orgc84edaa}
 \label{sec:sensor_fusion}
 
-Let's consider two sensors measuring the same physical quantity \(x\) but with different dynamics (\(G_1(s)\) and \(G_2(s)\)) and noise characteristics (\(n_1\) and \(n_2\)).
+Let's consider two sensors measuring the same physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\), and with noise characteristics \(n_1\) and \(n_2\).
 
-The signals from both sensors are fed into two complementary filters \(H_1(s)\) and \(H_2(s)\) and then combined to yield an estimate \(\hat{x}\) of \(x\) as shown on Fig.
+The signals from both sensors are fed into two complementary filters \(H_1(s)\) and \(H_2(s)\) and then combined to yield an estimate \(\hat{x}\) of \(x\) as shown in Fig.
 \ref{fig:fusion_super_sensor}.
@@
 \caption{\label{fig:fusion_super_sensor}
-Sensor Fusion Architecture}
+Sensor fusion architecture}
 \end{figure}
@@
 \subsection{Noise Sensor Filtering}
-\label{sec:org0ee5b17}
+\label{sec:org3904fad}
 \label{sec:noise_filtering}
@@
 
-The complementary filters \(H_1(s)\) and \(H_2(s)\) only operates on the noise of the sensors.
-Thus, this sensor fusion architecture permits to filter the noise of both sensors without introducing any distortion in the physical quantity to measure.
+From \eqref{eq:estimate_perfect_dyn}, the complementary filters \(H_1(s)\) and \(H_2(s)\) are shown to only operate on the sensor's noise.
+Thus, this sensor fusion architecture permits to filter the noise of both sensors without introducing any distortion in the physical quantity to be measured.
 
@@
 
-As shown in \eqref{eq:noise_filtering_psd}, the Power Spectral Density (PSD) of the estimation error \(\Phi_{\delta x}\) depends both on the norms of the complementary filters and on the PSD of the noise sources \(\Phi_{n_1}\) and \(\Phi_{n_2}\).
+As shown in \eqref{eq:noise_filtering_psd}, the Power Spectral Density (PSD) of the estimation error \(\Phi_{\delta x}\) depends both on the norm of the two complementary filters and on the PSD of the noise sources \(\Phi_{n_1}\) and \(\Phi_{n_2}\).
 \begin{equation}
@@
 
-Usually, the two sensors have higher noise levels over distinct yet complementary frequency regions.
-In order to lower the noise present in the estimation \(\hat{x}\), the norm \(|H_1|\) has to be made small when \(\Phi_{n_1}\) is larger than \(\Phi_{n_2}\) and \(|H_2|\) small when \(\Phi_{n_2}\) is larger than \(\Phi_{n_1}\).
+Usually, the two sensors have high noise levels over distinct frequency regions.
+In order to lower the noise of the super sensor, the value of the norm \(|H_1|\) has to be lowered when \(\Phi_{n_1}\) is larger than \(\Phi_{n_2}\) and that of \(|H_2|\) lowered when \(\Phi_{n_2}\) is larger than \(\Phi_{n_1}\).
 
 \subsection{Robustness of the Fusion}
-\label{sec:orgb942694}
+\label{sec:org1955823}
 \label{sec:fusion_robustness}
 
-In practical systems, the sensors dynamics has always some level of uncertainty and cannot be inverted perfectly such that \(G_i(s) = 1\).
+In practical systems, the sensor dynamics always have some level of uncertainty and cannot be inverted perfectly such that \(G_i(s) = 1\).
 
-This uncertainty can be represented as input multiplicative uncertainty as shown on Fig.
-\ref{fig:fusion_gain_mismatch_bis} where \(\Delta_i\) is any transfer function satisfying \(\|\Delta_i(j\omega)\|_\infty \le 1,\ \forall\omega\) and where \(|W_i(s)|\) represents the frequency dependent uncertainty level.
+This can be represented as an input multiplicative uncertainty as shown in Fig.
+\ref{fig:sensor_fusion_dynamic_uncertainty} where \(\Delta_i\) is any stable transfer function satisfying \(|\Delta_i(j\omega)| \le 1,\ \forall\omega\), and \(|w_i(s)|\) is a weight representing the magnitude of the uncertainty.
 
@@
 \centering
-\includegraphics[scale=1]{figs/fusion_gain_mismatch_bis.pdf}
-\caption{\label{fig:fusion_gain_mismatch_bis}
-Sensor Fusion Architecture with Sensor Dynamical Uncertainty}
+\includegraphics[scale=1]{figs/sensor_fusion_dynamic_uncertainty.pdf}
+\caption{\label{fig:sensor_fusion_dynamic_uncertainty}
+Sensor fusion architecture with sensor dynamics uncertainty}
 \end{figure}
 
-The super sensor dynamics \eqref{eq:super_sensor_dyn_uncertainty} is not longer equal to \(1\) and now depends on the sensor dynamic uncertainties \(W_i(s)\) as well as on the complementary filters \(H_i(s)\).
+The super sensor dynamics \eqref{eq:super_sensor_dyn_uncertainty} is no longer equal to \(1\) and is now dependent on the sensor dynamics uncertainty weights \(w_i(s)\) as well as on the complementary filters \(H_i(s)\).
 \begin{equation}
 \label{eq:super_sensor_dyn_uncertainty}
-  \frac{\hat{x}}{x} = 1 + W_1(s) H_1(s) \Delta_1(s) + W_2(s) H_2(s) \Delta_2(s)
+  \frac{\hat{x}}{x} = 1 + w_1(s) H_1(s) \Delta_1(s) + w_2(s) H_2(s) \Delta_2(s)
 \end{equation}
 
-In order to limit the phase and gain uncertainty of the super sensor, one may want to design the complementary filters to such that \eqref{eq:max_uncertainty_super_sensor} is satisfied.
+In order to limit the phase and gain uncertainty of the super sensor, one may want to design the complementary filters such that \eqref{eq:max_uncertainty_super_sensor} is satisfied.
 \begin{equation}
@@
   \begin{aligned}
-    & \left|W_1 H_1 \Delta_1\right| + \left|W_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_i\\
-    \Leftrightarrow & \left|W_1 H_1\right| + \left|W_2 H_2\right| \le \epsilon \quad \forall\omega
+    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
+    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega
   \end{aligned}
@@
 
-Condition \eqref{eq:max_uncertainty_super_sensor} is equivalent as to bound the uncertainty set of the super sensor dynamics in the complex plane by a circle centered on \(1\) with a radius equal to \(\epsilon\) (Fig.
-\ref{fig:uncertainty_gain_phase_variation_bis}).
+Condition \eqref{eq:max_uncertainty_super_sensor} is equivalent to bounding the uncertainty set of the super sensor dynamics in the complex plane by a circle centered at \(1\) with a radius equal to \(\epsilon\) (Fig.
+\ref{fig:uncertainty_set_super_sensor}).
 
@@
 \centering
-\includegraphics[scale=1]{figs/uncertainty_gain_phase_variation_bis.pdf}
-\caption{\label{fig:uncertainty_gain_phase_variation_bis}
+\includegraphics[scale=1]{figs/uncertainty_set_super_sensor.pdf}
+\caption{\label{fig:uncertainty_set_super_sensor}
 Uncertainty set of the super sensor dynamics}
@@
 
-The maximum phase added by the super sensor uncertainty \(\Delta\phi\) is then equal to \eqref{eq:max_phase_uncertainty}.
+The maximum phase added by the super sensor uncertainty \(\Delta\phi\) is then
 \begin{equation}
@@
 Limiting the phase added by the super sensor to \(\Delta \phi = \SI{30}{\degree}\) requires that \(H_1(s)\) and \(H_2(s)\) are designed such that \eqref{eq:max_uncertainty_super_sensor} is satisfied with \(\epsilon = \sin(\Delta\phi = \SI{30}{\degree}) = 0.5\).
-Thus the norm of the complementary filter \(|H_i|\) for sensor \(i\) should be made small at frequencies where its dynamic uncertainty \(|W_i|\) is large.\par
+Thus the norm of the complementary filter \(|H_i|\) should be made small at frequencies where the dynamic uncertainty \(|w_i|\) of sensor \(i\) is large.
 
-As stated above, the requirements in terms of noise attenuation and robustness of the sensor fusion architecture can be termed as upper bounds on the norm of the complementary filters.
-
-\section{Complementary Filters Shaping using the \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:orgb8fb6f7}
+\section{Complementary Filters Shaping using \(\mathcal{H}_\infty\) Synthesis}
+\label{sec:org8eb875c}
 \label{sec:hinf_method}
-As shown in Sec. \ref{sec:requirements}, most of the performance requirements for the design of the complementary filters can be expressed as upper bounds on the magnitude of the filters.
-
-Therefore, the \(\mathcal{H}_\infty\) Loop Shaping framework seems adapted for the synthesis of complementary filters.
-In this section, a technique for the synthesis complementary filters while specifying uppers bounds on their magnitudes using the \(\mathcal{H}_\infty\) synthesis is presented.
-\subsection{Synthesis of Complementary Filters as a \(\mathcal{H}_\infty\) problem}
-\label{sec:org3375829}
+As shown in Sec. \ref{sec:requirements}, the performance and robustness of the sensor fusion architecture depends on the complementary filters norms.
+Therefore, the development of a synthesis method of complementary filters that allows the shaping of their norm is necessary.
+\subsection{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\label{sec:orga1b497a}
 \label{sec:hinf_synthesis}
-
 The synthesis objective is to shape the norm of two filters \(H_1(s)\) and \(H_2(s)\) while ensuring their complementary property \eqref{eq:comp_filter}.
-
-The synthesis problem is then to find stable transfer functions \(H_1(s)\) and \(H_2(s)\) such that conditions \eqref{eq:comp_filter_problem_form} are satisfied.
+This is equivalent as to finding stable transfer functions \(H_1(s)\) and \(H_2(s)\) such that conditions \eqref{eq:comp_filter_problem_form} are satisfied.
 \begin{subequations}
@@
 \end{subequations}
-where \(W_1(s)\) and \(W_2(s)\) are two weighting transfer functions chosen to shape the corresponding filters.
+where \(W_1(s)\) and \(W_2(s)\) are two weighting transfer functions that are chosen to shape the norms of the corresponding filters.
 
-In order to express this synthesis problem into a standard \(\mathcal{H}_\infty\) problem, we use the standard architecture shown on Fig.
-\ref{fig:h_infinity_robust_fusion} where the generalized plant \(P\) is described by \eqref{eq:generalized_plant}.
+In order to express this optimization problem as a standard \(\mathcal{H}_\infty\) problem, the architecture shown in Fig.
+\ref{fig:h_infinity_robust_fusion} is used where the generalized plant \(P\) is described by \eqref{eq:generalized_plant}.
 \begin{equation}
@@
 \caption{\label{fig:h_infinity_robust_fusion}
-Architecture used for the \(\mathcal{H}_\infty\) synthesis of complementary filters}
+Architecture used for \(\mathcal{H}_\infty\) synthesis of complementary filters}
 \end{figure}
 
-The \(\mathcal{H}_\infty\) filter design problem is then to find a stable filter \(H_1(s)\) which based on \(v\), generates a signal \(u\) such that the \(\mathcal{H}_\infty\) norm from \(w\) to \([z_1, \ z_2]\) is less than one \eqref{eq:hinf_syn_obj}.
+The \(\mathcal{H}_\infty\) filter design problem is then to find a stable filter \(H_2(s)\) which based on \(v\), generates a signal \(u\) such that the \(\mathcal{H}_\infty\) norm from \(w\) to \([z_1, \ z_2]\) is less than one \eqref{eq:hinf_syn_obj}.
 \begin{equation}
@@
 
-Which is equivalent to \eqref{eq:hinf_problem} by defining \(H_1(s) \triangleq 1 - H_2(s)\).
+This is equivalent to having \eqref{eq:hinf_problem} by defining \(H_1(s)\) as the complementary filter of \(H_2(s)\) \eqref{eq:definition_H1}.
 \begin{equation}
@@
 
-The complementary condition \eqref{eq:hinf_cond_complementarity} is ensured by the definition of \(H_1(s)\).
-The conditions \eqref{eq:hinf_cond_h1} and \eqref{eq:hinf_cond_h2} on the shape of the filters are satisfied by \eqref{eq:hinf_problem}.
+\begin{equation}
+\label{eq:definition_H1}
+  H_1(s) \triangleq 1 - H_2(s)
+\end{equation}
 
-Using this \(\mathcal{H}_\infty\) synthesis method, we are then able to shape complementary filters.
+The complementary condition \eqref{eq:hinf_cond_complementarity} is ensured by \eqref{eq:definition_H1}.
+The conditions \eqref{eq:hinf_cond_h1} and \eqref{eq:hinf_cond_h2} on the filters shapes are satisfied by \eqref{eq:hinf_problem}.
+Therefore, all the conditions \eqref{eq:comp_filter_problem_form} are satisfied using this synthesis method based on \(\mathcal{H}_\infty\) synthesis, and thus it permits to shape complementary filters as desired.
 
-\subsection{Choice of the weighting functions}
-\label{sec:orgd7d262d}
+\subsection{Weighting Functions Design}
+\label{sec:orgdf5910c}
 \label{sec:hinf_weighting_func}
-
-The choice of the weighting functions is of primary importance for the success of the presented \(\mathcal{H}_\infty\) synthesis of complementary filters.
+The proper design of the weighting functions is of primary importance for the success of the presented complementary filters \(\mathcal{H}_\infty\) synthesis.
 
 First, only proper, stable and minimum phase transfer functions should be used.
-Second, the order of the weights should stay reasonably small as this will increase both the complexity of the optimization problem and the order of the synthesized complementary filters, the latter begin equal to the sum of the weighting functions orders.
-Third, one should not forget the fundamental limitations imposed by the complementary property: \(H_1(s) + H_2(s) = 1\).
+Second, the order of the weights should stay reasonably small in order to reduce the computational costs associated with the solving of the optimization problem and for the physical implementation of the filters (the order of the synthesized filters being equal to the sum of the weighting functions order).
+Third, one should not forget the fundamental limitations imposed by the complementary property \eqref{eq:comp_filter}.
 This implies for instance that \(|H_1(j\omega)|\) and \(|H_2(j\omega)|\) cannot be made small at the same time.
 
-When designing complementary filters, it is usually desired to specify the slope of the filter, its crossover frequency and its low and high frequency gains.
-To help with the design of the weighting functions such that the above specification are easily expressed, the formula \eqref{eq:weight_formula} is proposed.
+When designing complementary filters, it is usually desired to specify the slope of the filter, its crossover frequency and its gain at low and high frequency.
+To help with the design of the weighting functions such that the above specification can be easily expressed, the following formula is proposed.
 \begin{equation}
@@
 \end{equation}
-where:
+The parameters permit to specify:
 \begin{itemize}
-\item \(G_0\) is the absolute gain at low frequency
-\item \(G_\infty\) is the absolute gain at high frequency
-\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
-\item \(n\) is the order of the weighting function as well as its slope between high and low frequency
+\item the low frequency gain: \(G_0 = lim_{\omega \to 0} |W(j\omega)|\)
+\item the high frequency gain: \(G_\infty = lim_{\omega \to \infty} |W(j\omega)|\)
+\item the absolute gain at \(\omega_0\): \(G_c = |W(j\omega_0)|\)
+\item the absolute slope between high and low frequency: \(n\)
 \end{itemize}
@@
 
-The shape of the weighting function generated using \eqref{eq:weight_formula} is shown on Fig. \ref{fig:weight_formula}.
+The general shape of a weighting function generated using \eqref{eq:weight_formula} is shown in Fig. \ref{fig:weight_formula}.
 
@@
 \caption{\label{fig:weight_formula}
-Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
+Magnitude of a weighting function generated using the proposed formula \eqref{eq:weight_formula}, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
 \end{figure}
 
-\subsection{Example}
-\label{sec:org018b699}
+\subsection{Validation of the proposed synthesis method}
+\label{sec:org32ec287}
 \label{sec:hinf_example}
+Let's validate the proposed design method of complementary filters with a simple example where two complementary filters \(H_1(s)\) and \(H_2(s)\) have to be designed such that:
+\begin{itemize}
+\item the merging frequency is around \(\SI{10}{Hz}\)
+\item the slope of \(|H_1(j\omega)|\) is \(-2\) above \(\SI{10}{Hz}\)
+\item the slope of \(|H_2(j\omega)|\) is \(+3\) below \(\SI{10}{Hz}\)
+\item the gain of both filters is equal to \(10^{-3}\) away from the merging frequency
+\end{itemize}
 
-Let's validate the proposed design method of complementary filters using the \(\mathcal{H}_\infty\) synthesis with a simple example.
-
-Both weighting functions \(W_1(s)\) and \(W_2(s)\) are designed using \eqref{eq:weight_formula}.
-The parameters used are summarized on table \ref{tab:weights_params} and the magnitude of the weighting functions are shown on Fig. \ref{fig:hinf_synthesis_results}.
-
-The blending frequency is chosen to be around \(\SI{10}{Hz}\).
-The slope of \(|H_1(j\omega)|\) is chosen to be \(-2\) above \(\SI{10}{Hz}\) by choosing \(n=2\) for \(W_1(s)\).
-The slope of \(|H_2(j\omega)|\) is chosen to be \(+3\) below \(\SI{10}{Hz}\) by choosing \(n=3\) for \(W_2(s)\).
-The order of the obtained complementary filters will thus be of order \(5\).
+The weighting functions \(W_1(s)\) and \(W_2(s)\) are designed using \eqref{eq:weight_formula}.
+The parameters used are summarized in table \ref{tab:weights_params} and the magnitude of the weighting functions is shown in Fig. \ref{fig:hinf_synthesis_results}.
 
@@
 \(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
-\(G_c\) & \(2\) & \(2\)\\
+\(G_c\) & \(0.5\) & \(0.5\)\\
 \(n\) & \(2\) & \(3\)\\
@@
 
-The bode plot of the obtained complementary filters is shown on Fig. \ref{fig:hinf_synthesis_results} and their transfer functions in the Laplace domain are shown below.
+The bode plots of the obtained complementary filters are shown in Fig. \ref{fig:hinf_synthesis_results} and their transfer functions in the Laplace domain are given below.
 \begin{align*}
@@
 \caption{\label{fig:hinf_synthesis_results}
-Weighting functions and Obtain Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
+Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
 
-\subsection{Generalization to the synthesis of Three Complementary Filters}
-\label{sec:orgcb75a24}
+\subsection{Synthesis of Three Complementary Filters}
+\label{sec:orgdfc880e}
 \label{sec:hinf_three_comp_filters}
-In some applications, it may be needed to merge more than two sensors.
-In such case, it is necessary to design as many complementary filters \(H_i(s)\) as the number of sensors used.
+Some applications may require to merge more than two sensors.
+In such a case, it is necessary to design as many complementary filters as the number of sensors used.
 The synthesis problem is then to compute \(n\) stable transfer functions \(H_i(s)\) such that \eqref{eq:hinf_problem_gen} is satisfied.
@@
 \end{subequations}
-The synthesis architecture on Fig. \ref{fig:h_infinity_robust_fusion} can be generalized for the synthesis of a set of \(n\) complementary filters.
-For the synthesis of three complementary filters, the architecture used is shown on Fig. \ref{fig:comp_filter_three_hinf}.
+The synthesis method is generalized here for the synthesis of three complementary filters using the architecture shown in Fig. \ref{fig:comp_filter_three_hinf}.
 
@@
 \caption{\label{fig:comp_filter_three_hinf}
-Architecture for the \(\mathcal{H}_\infty\) synthesis of three complementary filters}
+Architecture for \(\mathcal{H}_\infty\) synthesis of three complementary filters}
 \end{figure}
@@
 An example is given to validate the method where three sensors are used in different frequency bands (up to \(\SI{1}{Hz}\), from \(1\) to \(\SI{10}{Hz}\) and above \(\SI{10}{Hz}\) respectively).
-Three weighting functions are designed using \eqref{eq:weight_formula} and shown by dashed curves on Fig. \ref{fig:hinf_three_synthesis_results}.
-The obtained complementary filters after synthesis are shown on Fig. \ref{fig:hinf_three_synthesis_results}.
+Three weighting functions are designed using \eqref{eq:weight_formula} and shown by dashed curves in Fig. \ref{fig:hinf_three_synthesis_results}.
+The bode plots of the obtained complementary filters are shown in Fig. \ref{fig:hinf_three_synthesis_results}.
 
@@
 \caption{\label{fig:hinf_three_synthesis_results}
-Obtained three complementary filters}
+Frequency response of the weighting functions and three complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
 
-\section{Application: Design of Complementary Filters used for the Active Vibration Isolation System at the LIGO}
-\label{sec:org8dbdcd2}
+\section{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}
+\label{sec:org58b0928}
 \label{sec:application_ligo}
-Several complementary filters are used for the active isolation system at the LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
+Several complementary filters are used in the active isolation system at the LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
 The requirements on those filters are very tight and thus their design is complex.
-The approach taken in \cite{hua05_low_ligo} for the design of those filters is to use high order FIR filters and write the synthesis objective as a convex optimization problem.
-The obtained FIR filters are compliant with the requirements, however their implementation is complex as it requires a lot of computation power.
+The approach used in \cite{hua05_low_ligo} for their design is to write the synthesis of complementary FIR filters as a convex optimization problem.
+The obtained FIR filters are compliant with the requirements. However they are of very high order so their implementation is quite complex.
 
-In order to demonstrate the effectiveness of the synthesis method presented in section \ref{sec:hinf_method}, complementary filters subject to the same requirements are synthesize.
-\subsection{Specifications}
-\label{sec:org684e797}
+The effectiveness of the proposed method is demonstrated by designing complementary filters with the same requirements as the one described in \cite{hua05_low_ligo}.
+\subsection{Complementary Filters Specifications}
+\label{sec:org0bf5de3}
 \label{sec:ligo_specifications}
-
-As explained in section \ref{sec:requirements}, typical specifications for the complementary filters are on their magnitude.
-
-The specifications are summarized below and explained in details in \cite{hua04_polyp_fir_compl_filter_contr_system}:
+The specifications for one pair of complementary filters used at the LIGO are summarized below (for further details, refer to \cite{hua04_polyp_fir_compl_filter_contr_system}):
 \begin{itemize}
@@
 
-The specifications are represented by the dashed black curves on the bode plot in Fig. \ref{fig:ligo_weights}.
+The specifications are represented by the dashed lines in Fig. \ref{fig:ligo_weights}.
 
-\subsection{Weighting functions design}
-\label{sec:orgac7c8d0}
+\subsection{Weighting Functions Design}
+\label{sec:org0a19352}
 \label{sec:ligo_weights}
-The weighting functions should be designed so that their inverse amplitude is as close as possible to the specifications in order to not over-constrain the synthesis problem.
-However, their order should not be too high as to limit both the complexity of the optimization problem and the order of the synthesize complementary filters.
+The weighting functions should be designed such that their inverse magnitude is as close as possible to the specifications in order to not over-constrain the synthesis problem.
+However, the order of each weight should stay reasonably small in order to reduce the computational costs of the optimization problem as well as for the physical implementation of the filters.
 
-For the weight function corresponding to the low pass filter \(w_L(s)\), a Type I Chebyshev filter of order \(20\) is used.
-For the one corresponding to the high pass filter \(w_H(s)\), a \(7^{\text{th}}\) order transfer function gives satisfactory results.
-The magnitudes of the inverse of the weighting functions are shown on Fig. \ref{fig:ligo_weights}.
+A Type I Chebyshev filter of order \(20\) is used as the weighting transfer function \(w_L(s)\) corresponding to the low pass filter.
+For the one corresponding to the high pass filter \(w_H(s)\), a \(7^{\text{th}}\) order transfer function is designed.
+The magnitudes of the weighting functions inverse are shown in Fig. \ref{fig:ligo_weights}.
 
@@
 \caption{\label{fig:ligo_weights}
-Specification and Weighting Functions used for the \(\mathcal{H}_\infty\) synthesis}
+Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
@@
 \subsection{\(\mathcal{H}_\infty\) Synthesis}
-\label{sec:org9dfd8e0}
+\label{sec:orgf481d28}
 \label{sec:ligo_results}
-
-The \(\mathcal{H}_\infty\) synthesis is performed using the architecture of Fig. \ref{eq:generalized_plant}.
+\(\mathcal{H}_\infty\) synthesis is performed using the architecture shown in Fig. \ref{eq:generalized_plant}.
 The complementary filters obtained are of order \(27\).
-Their bode plot is compared on Fig. \ref{fig:comp_fir_ligo_hinf} with the FIR filters of order 512 obtained in \cite{hua05_low_ligo}.
+In Fig. \ref{fig:comp_fir_ligo_hinf}, their bode plot is compared with the FIR filters of order 512 obtained in \cite{hua05_low_ligo}.
+They are found to be very close to each other and this shows the effectiveness of the proposed synthesis method.
 
@@
 \caption{\label{fig:comp_fir_ligo_hinf}
-Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with the \(\mathcal{H}_\infty\) synthesis (dashed)}
+Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with \(\mathcal{H}_\infty\) synthesis (dashed)}
 \end{figure}
@@
 \section{Conclusion}
-\label{sec:org30078db}
+\label{sec:orgc26b54f}
   \label{sec:conclusion}
+This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
+Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
+Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
+Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.
 
 \section{Acknowledgment}
-\label{sec:orgf4d440c}
+\label{sec:org698db58}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2019-08-22 poster/conclusion.tex
Add poster files

--- 2019-08-16 paper/paper.tex
@@
-% Created 2019-08-16 ven. 23:34
-% Intended LaTeX compiler: pdflatex
-\documentclass[9pt, technote, a4paper]{ieeeconf}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{grffile}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage[most]{tcolorbox}
-\usepackage{siunitx}
-\usepackage{amsmath,amssymb,amsfonts, cases}
-\usepackage{algorithmic, graphicx, textcomp}
-\usepackage{xcolor, import, hyperref}
-\usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
-\input{config.tex}
-\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
-\date{2019-08-16}
-\title{On the Design of Complementary Filters for Control}
-\hypersetup{
- pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
- pdftitle={On the Design of Complementary Filters for Control},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
- pdflang={English}}
-\begin{document}
-
-\maketitle
-\bibliographystyle{IEEEtran}
-
-\begin{abstract}
-Abstract text to be done
-\end{abstract}
-
-\begin{IEEEkeywords}
-complementary filters, h-infinity, feedback control
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:org1a92e6d}
-  \label{sec:introduction}
-The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
-To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
-A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.
-
-The proper design of this particular kind of filter is of primary importance in a wide range of applications.
-Often, multiple sensors with different noise or dynamical properties are used to measure the same physical quantity.
-In such case, complementary filters can be used to merge the sensors and forms a "super sensor" that has gives a better estimate of the physical quantity over a wider bandwidth.
-This is called sensor blending or sensor fusion.
-
-This is widely used for the attitude estimation of unmanned aerial vehicles using various kind of sensors (accelerometers, gyroscopes, vision sensors, inclinometer) \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}.
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel} Fast position measurement of flexible structure
-
-\cite{matichard15_seism_isolat_advan_ligo} (relative displacement measurement at low frequencies with inertial at high frequencies)
-
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-
-\cite{collette15_sensor_fusion_method_high_perfor}
-The design methods for such filters goes from simple analytical formulas
-
-\cite{corke04_inert_visual_sensin_system_small_auton_helic}
-
-\cite{min15_compl_filter_desig_angle_estim}
-\cite{jensen13_basic_uas}
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel}
-\cite{zimmermann92_high_bandw_orien_measur_contr}
-\cite{matichard15_seism_isolat_advan_ligo}
-\cite{collette15_sensor_fusion_method_high_perfor}
-
-\cite{hua05_low_ligo}
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-\cite{matichard15_seism_isolat_advan_ligo}
-
-\cite{mahony08_nonlin_compl_filter_special_orthog_group}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{jensen13_basic_uas} (feedback system, P, PI, classical control theory for filter design)
-\cite{brown72_integ_navig_system_kalman_filter}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{min15_compl_filter_desig_angle_estim}
-Although
-In this paper, we propose
-The body of the paper consists of five parts followed by a conclusion.
-
-\section{Requirements on the Design of Complementary Filters}
-\label{sec:org8c17952}
-\label{sec:requirements}
-
-\subsection{Sensor Fusion}
-\label{sec:org77e3eba}
-\label{sec:sensor_fusion}
-
-Let's consider two sensors measuring the physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\) and with noise \(n_1\) and \(n_2\) respectively.
-
-\(H_1(s)\) and \(H_2(s)\) are complementary filters:
-\begin{equation}
-  H_1(s) + H_2(s) = 1
-\end{equation}
-
-\begin{equation}
-  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
-\end{equation}
-
-If we now consider sensors with perfect dynamics (\(G_1(s) = G_2(s) = 1\)), we have that the estimate of \(x\) using the two sensors are shown on figure \ref{fig:fusion_two_noisy_sensors_with_dyn_ter} is:
-
-\begin{equation}
-  \hat{x} = x + H_1 n_1 + H_2 n_2
-\end{equation}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/fusion_two_noisy_sensors_with_dyn_ter.pdf}
-\caption{\label{fig:fusion_two_noisy_sensors_with_dyn_ter}
-Sensor Fusion Architecture}
-\end{figure}
-
-We see that the complementary filters \(H_1(s)\) and \(H_2(s)\) operates only on the noise of the sensors.
-
-Thus, this architecture permits to filter each of the sensors without introducing any distortion in the physical quantity to measure.
-
-\begin{equation}
-  \delta x = \hat{x} - x = H_1 n_1 + H_2 n_2
-\end{equation}
-
-Usually, the two sensors have higher noise levels over distinct yet complementary frequency regions.
-The two complementary filters are used to combine the filtered noise and yield to a better estimate \(\hat{x}\) over a larger bandwidth.
-
-The noise of the super sensor is determine by the norm of the complementary filters.
-
-\subsection{Noise Sensor Filtering}
-\label{sec:org61f1e42}
-\label{sec:noise_filtering}
-
-\subsection{Robustness of the Fusion}
-\label{sec:org88c9440}
-\label{sec:fusion_robustness}
-
-\subsection{Upper bounds as a mathematical translation of the requirements}
-\label{sec:org2e8321f}
-\label{sec:requirements_upper_bounds}
-
-\textbf{The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity}
-
-\section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:orgd9ea119}
-\label{sec:hinf_method}
-As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
-As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
-
-Thus, the \(\mathcal{H}_\infty\) framework seems adapted and we here propose a technique to synthesis complementary filters while specifying uppers bounds on their magnitudes.
-
-\subsection{\(\mathcal{H}_\infty\) problem formulation}
-\label{sec:orgecc21d9}
-\label{sec:hinf_synthesis}
-
-In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.
-
-The synthesis objective is to shape an high pass filter \(H_H\) and a low pass filter \(H_L\) while ensuring their complementary property (\(H_H + H_L = 1\)).
-
-To do so, we define two weighting functions \(w_L\) and \(w_H\) that will respectively used to shape \(H_L\) and \(H_H\).
-
-The synthesis problem is then
-\begin{subnumcases}{\text{Find } H_L, H_H \text{ such that}}
-  H_L \text{ and } H_H \text{ are stable} \label{eq:hinf_cond_stability}\\
-  H_L + H_H = 1 \label{eq:hinf_cond_complementarity} \\
-  |w_L H_L| \le 1 \quad \forall\omega \label{eq:hinf_cond_hl} \\
-  |w_H H_H| \le 1 \quad \forall\omega \label{eq:hinf_cond_hh}
-\end{subnumcases}
-
-To express this synthesis problem into an \(\hinf\) synthesis problem, we define the following generalized plant \(P\) (also shown on Fig. \ref{fig:sf_hinf_filters_plant_b}):
-\begin{equation}
-\label{eq:generalized_plant}
-  \colvec{w\\u} = P \colvec{z_H \\ z_L \\ v}; \quad P = \begin{bmatrix} w_H & -w_H \\ 0 & w_L \\ 1 & 0 \end{bmatrix}
-\end{equation}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/h_infinity_robust_fusion.pdf}
-\caption{\label{fig:h_infinity_robust_fusion}
-Architecture used for the \(\mathcal{H}_\infty\) synthesis of complementary filters}
-\end{figure}
-
-The \(\hinf\) synthesis objective is then to design a stable filter \(H_L\) (Fig.
-\ref{fig:sf_hinf_filters_b}) such that the \(\mathcal{H}_\infty\) norm of the transfer function from \(w\) to \([z_H, \ z_L]\) is less than \(1\):
-\begin{equation}
-  \hnorm{\begin{matrix} (1 - H_L) w_H \\ H_L w_L \end{matrix}} \le 1
-\end{equation}
-Which is equivalent to
-\begin{equation}
-\label{eq:hinf_problem}
-  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} < 1 \text{ by choosing } H_H = 1 - H_L
-\end{equation}
-
-Performance conditions \eqref{eq:hinf_cond_hl} and \eqref{eq:hinf_cond_hl} are satisfied by \eqref{eq:hinf_problem}.
-Complementary condition \eqref{eq:hinf_cond_complementarity} is satisfied by design: \(H_H = 1 - H_L\) and thus \(H_L + H_H = 1\).
-The stability condition \eqref{eq:hinf_cond_stability} is guaranteed by the \(H_\infty\) synthesis (\textbf{reference}).
-
-Using this synthesis method, we are then able to shape at the same time the high pass and low pass filters while ensuring their complementary.
-
-\subsection{Choice of the weighting functions}
-\label{sec:org6167188}
-\label{sec:hinf_weighting_func}
-
-We here give some advice on the design of the weighting functions used for the synthesis of the complementary filters using the \(\mathcal{H}_\infty\) method.
-
-The weighting functions should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.
-
-However, one should be careful when designing the complementary filters, and should only use stable and minimum phase transfer functions.
-The order of the weights should stay reasonably small as this will increase the complexity of the optimization problem.
-
-Moreover, the order of the complementary filters will be equal to the sum of the order of the weighting functions used.
-
-One should not forget the fundamental limitations imposed by the synthesis: \(H_L(s) + H_H(s) = 1\).
-This implies that \(H_L\) and \(H_H\) cannot be made small at the same time.
-
-We here propose a formula for the design of the weighting function \eqref{eq:weight_formula}.
-
-\begin{equation}
-\label{eq:weight_formula}
-  W(s) = \left(\frac{
-           \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
-         }{
-           \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
-         }}\right)^n
-\end{equation}
-with:
-\begin{itemize}
-\item \(G_0\) is the absolute gain at low frequency
-\item \(G_\infty\) is the absolute gain at high frequency
-\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
-\item \(n\) is the absolute slope of the filter, it is also equal to the order of the filter
-\end{itemize}
-
-The constrains are that \(G_0 < 1 < G_\infty\) and \(G_0 < G_c < G_\infty\) or that \(G_\infty < 1 < G_0\) and \(G_\infty < G_c < G_0\).
-
-The shape of the weight generated using the formula is shown on figure \ref{fig:weight_formula}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/weight_formula.pdf}
-\caption{\label{fig:weight_formula}
-Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
-\end{figure}
-
-\subsection{Example}
-\label{sec:orgb30ba62}
-\label{sec:hinf_example}
-
-We are now using the proposed \(\mathcal{H}_\infty\) complementary filters synthesis method for a simple example.
-
-The goal is to design
-
-We use the formula \eqref{eq:weight_formula} for both \(w_L(s)\) and \(w_H(s)\).
-The parameters used are summarized on table \ref{tab:weights_params}. And the magnitude of the weighting functions are shown on figure \ref{fig:weights_wl_wh}.
-
-\begin{table}[!htpb]
-\caption{\label{tab:weights_params}
-Parameters used for the weighting functions}
-\centering
-\begin{tabular}{|l|X|X|}
-\hline
-Parameters & \(w_L\) & \(w_H\)\\
-\hline
-\(G_0\) & \(0.1\) & \(1000\)\\
-\hline
-\(G_\infty\) & \(1000\) & \(0.1\)\\
-\hline
-\(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
-\hline
-\(G_c\) & \(2\) & \(2\)\\
-\hline
-\(n\) & \(2\) & \(3\)\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/weights_wl_wh.pdf}
-\caption{\label{fig:weights_wl_wh}
-Weighting Functions used for the \(\mathcal{H}_\infty\) Synthesis}
-\end{figure}
-
-After synthesis, the obtain filters are:
-\begin{align}
-  H_L(s) &= \frac{10^{-8} (s+6.6e^9) (s+3450)^2 (s^2 + 49s + 895)}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}\\
-  H_H(s) &= \frac{(s+6.6e^4) (s+160) (s+4)^3}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}
-\end{align}
-
-Their bode plot is shown on figure \ref{fig:hinf_synthesis_results}.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
-\caption{\label{fig:hinf_synthesis_results}
-Obtain Complementary Filters}
-\end{figure}
-
-\subsection{Synthesis of Three Complementary Filters}
-\label{sec:org415d7ce}
-\label{sec:hinf_three_comp_filters}
-
-We want:
-\begin{align*}
-  & |H_1 w_1| < 1, \quad \forall\omega\\
-  & |H_2 w_2| < 1, \quad \forall\omega\\
-  & |H_3 w_3| < 1, \quad \forall\omega\\
-  & H_1 + H_2 + H_3 = 1
-\end{align*}
-
-The \(\mathcal{H}_\infty\) objective is:
-\begin{align*}
-  & |H_1 w_1| < 1, \quad \forall\omega\\
-  & |H_2 w_2| < 1, \quad \forall\omega\\
-  & |(1 - H_1 - H_2) w_3| < 1, \quad \forall\omega\\
-\end{align*}
-
-And thus if we choose \(H_3 = 1 - H_1 - H_2\) we have solved the problem.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_filter_three_hinf.pdf}
-\caption{\label{fig:comp_filter_three_hinf}
-Architecture for the \(\mathcal{H}_\infty\) synthesis of three complementary filters}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/hinf_three_synthesis_results.pdf}
-\caption{\label{fig:hinf_three_synthesis_results}
-Figure caption}
-\end{figure}
-
-\section{Application to the design of}
-\label{sec:org57876bd}
-\label{sec:application_ligo}
-
-\subsection{Specifications}
-\label{sec:orgc79cee4}
-\label{sec:ligo_specifications}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/ligo_specifications.pdf}
-\caption{\label{fig:ligo_specifications}
-Specifications on the norms of the complementary filters}
-\end{figure}
-
-\subsection{Weighting functions design}
-\label{sec:org6e51da2}
-\label{sec:ligo_weights}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/ligo_weights.pdf}
-\caption{\label{fig:ligo_weights}
-Weighting Functions used for the \(\mathcal{H}_\infty\) synthesis}
-\end{figure}
-
-\subsection{Comparison}
-\label{sec:org06ff1a1}
-\label{sec:ligo_results}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
-\caption{\label{fig:comp_fir_ligo_hinf}
-Comparison of the filters obtain with the \(\mathcal{H}_\infty\) synthesis and the FIR filters designed in \cite{hua05_low_ligo}}
-\end{figure}
-
-\section{Conclusion}
-\label{sec:orga86d375}
-\label{sec:conclusion}
-
-\section{Acknowledgment}
-\label{sec:org8d338b6}
-
-\bibliography{ref}
-\end{document}
+This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
+Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
+Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
+Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.

### 2019-08-22 poster/ligo.tex
Add poster files

\textbf{Control Configuration}

\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Specifications and weighting functions magnitude used for $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[scale=1.8]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with $\mathcal{H}_\infty$ synthesis (dashed)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[scale=1.8]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}

### 2019-08-22 poster/poster.tex
Add poster files

\documentclass[%
    a0paper,%
    20pt,%
    portait,%
    margin=0mm,%
    innermargin=10mm,%
    blockverticalspace=10mm,%
    colspace=10mm,%
    subcolspace=5mm%
]{tikzposter}

\input{config.tex}

\addbibresource{ref.bib}

\author{Dehaeze Thomas, Verma Mohit and Collette Christophe}
\date{2019-11-06}
\title{Complementary Filters Shaping Using \scalebox{2}{$\mathcal{H}_\infty$} Synthesis}
\institute{}

\useblockstyle{customstyle}

\begin{document}

\maketitle[%
    roundedcorners=2,
    linewidth=2mm,
    innersep=10mm,
    titletotopverticalspace=10mm,
    titletoblockverticalspace=10mm]

\block[]{}{\input{abstract.tex}}

\begin{columns}
\column{0.5}
\block[]{Introduction}{\input{introduction.tex}}
\block[]{Complementary Filters Requirements}{\input{requirements.tex}}

\column{0.5}
\block[]{Complementary Filters Shaping using $\mathcal{H}_\infty$ Synthesis}{\input{hinfinity.tex}}
\block[]{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}{\input{ligo.tex}}
\block[]{Conclusion}{\input{conclusion.tex}}
\end{columns}

\block[]{}{\input{reference.tex}}

\end{document}

### 2019-08-22 poster/requirements.tex
Add poster files

\begin{tikzfigure}[Sensor fusion architecture]
  \label{fig:fusion_super_sensor}
  \centering
  \includegraphics[scale=1.8]{figs/fusion_super_sensor.pdf}
\end{tikzfigure}

\begin{tikzfigure}[Sensor fusion architecture with sensor dynamics uncertainty]
  \label{fig:sensor_fusion_dynamic_uncertainty}
  \centering
  \includegraphics[scale=1.8]{figs/sensor_fusion_dynamic_uncertainty.pdf}
\end{tikzfigure}

\begin{tikzfigure}[Uncertainty set of the super sensor dynamics]
  \label{fig:uncertainty_set_super_sensor}
  \centering
  \includegraphics[scale=1.8]{figs/uncertainty_set_super_sensor.pdf}
\end{tikzfigure}

### 2019-08-22 presentation/presentation.tex
Add Presentation files

--- 2019-08-16 paper/paper.tex
@@
-% Created 2019-08-16 ven. 23:34
+% Created 2019-08-22 jeu. 11:06
 % Intended LaTeX compiler: pdflatex
-\documentclass[9pt, technote, a4paper]{ieeeconf}
+\documentclass[t]{clean-beamer}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{siunitx}
-\usepackage{amsmath,amssymb,amsfonts, cases}
-\usepackage{algorithmic, graphicx, textcomp}
-\usepackage{xcolor, import, hyperref}
-\usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
-\input{config.tex}
-\author{\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}}
-\date{2019-08-16}
-\title{On the Design of Complementary Filters for Control}
+\AtBeginSection[]{
+\begin{frame}<beamer>{Table of Contents}
+\tableofcontents[currentsection, hideothersubsections, sectionstyle=show/shaded]
+\end{frame}
+}
+\usetheme{default}
+\author{Dehaeze Thomas}
+\date{07-11-2019}
+\title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
+\subtitle{ICCMA 2019}
 \hypersetup{
- pdfauthor={\IEEEauthorblockN{Dehaeze Thomas\IEEEauthorrefmark{*}, Vermat Mohit and Collette Christophe} \\ \IEEEauthorblockA{Precision Mechatronics Laboratory, ULB\\ Brussels, Belgium\\ Email: \IEEEauthorrefmark{*}dehaeze.thomas@gmail.com}},
- pdftitle={On the Design of Complementary Filters for Control},
- pdfkeywords={},
- pdfsubject={},
+ pdfauthor={Dehaeze Thomas},
+ pdftitle={Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis},
+ pdfkeywords={complementary filters, h-infinity, sensor fusion},
+ pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation at ICCMA 2019.},
  pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
@@
 \maketitle
-\bibliographystyle{IEEEtran}
-
-\begin{abstract}
-Abstract text to be done
-\end{abstract}
-
-\begin{IEEEkeywords}
-complementary filters, h-infinity, feedback control
-\end{IEEEkeywords}
+\begin{frame}{Outline}
+\tableofcontents
+\end{frame}
 
 \section{Introduction}
-\label{sec:org1a92e6d}
+\label{sec:org4eff5bb}
 \label{sec:introduction}
-The basic idea of a complementary filter involves taking two or more sensors, filtering out unreliable frequencies for each sensor and combining the filtered outputs to get a better estimate throughout the entire bandwidth of the system.
-To achieve this, the sensors included in the filter should complement one another by performing better over specific parts of the system bandwidth.
-A set of filters is said to be complementary if the sum of their transfer functions is equal to one at all frequencies, (i.e.) its magnitude is one and its phase is zero.
 
-The proper design of this particular kind of filter is of primary importance in a wide range of applications.
-Often, multiple sensors with different noise or dynamical properties are used to measure the same physical quantity.
-In such case, complementary filters can be used to merge the sensors and forms a "super sensor" that has gives a better estimate of the physical quantity over a wider bandwidth.
-This is called sensor blending or sensor fusion.
+\begin{frame}[label={sec:org6dbc4f9}]{Introduction}
+High bandwidth
+\begin{itemize}
+\item need of Sensor at low frequency + sensor at high frequency
+\item need of merging the two
+\item complementary filters
+\item design of those filters using \(\mathcal{H}_\infty\)
+\end{itemize}
+\end{frame}
 
-This is widely used for the attitude estimation of unmanned aerial vehicles using various kind of sensors (accelerometers, gyroscopes, vision sensors, inclinometer) \cite{zimmermann92_high_bandw_orien_measur_contr,corke04_inert_visual_sensin_system_small_auton_helic,min15_compl_filter_desig_angle_estim}.
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel} Fast position measurement of flexible structure
-
-\cite{matichard15_seism_isolat_advan_ligo} (relative displacement measurement at low frequencies with inertial at high frequencies)
-
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-
-\cite{collette15_sensor_fusion_method_high_perfor}
-The design methods for such filters goes from simple analytical formulas
-
-\cite{corke04_inert_visual_sensin_system_small_auton_helic}
-
-\cite{min15_compl_filter_desig_angle_estim}
-\cite{jensen13_basic_uas}
-
-\cite{shaw90_bandw_enhan_posit_measur_using_measur_accel}
-\cite{zimmermann92_high_bandw_orien_measur_contr}
-\cite{matichard15_seism_isolat_advan_ligo}
-\cite{collette15_sensor_fusion_method_high_perfor}
-
-\cite{hua05_low_ligo}
-\cite{hua04_polyp_fir_compl_filter_contr_system}
-\cite{matichard15_seism_isolat_advan_ligo}
-
-\cite{mahony08_nonlin_compl_filter_special_orthog_group}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{jensen13_basic_uas} (feedback system, P, PI, classical control theory for filter design)
-\cite{brown72_integ_navig_system_kalman_filter}
-
-\cite{pascoal99_navig_system_desig_using_time}
-
-\cite{min15_compl_filter_desig_angle_estim}
-Although
-In this paper, we propose
-The body of the paper consists of five parts followed by a conclusion.
-
-\section{Requirements on the Design of Complementary Filters}
-\label{sec:org8c17952}
+\section{Complementary Filters Requirements}
+\label{sec:org49f4bb1}
 \label{sec:requirements}
-
-\subsection{Sensor Fusion}
-\label{sec:org77e3eba}
+\begin{frame}[label={sec:orgd4e76ba}]{Sensor Fusion Architecture}
 \label{sec:sensor_fusion}
 
-Let's consider two sensors measuring the physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\) and with noise \(n_1\) and \(n_2\) respectively.
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/fusion_super_sensor.pdf}
+\caption{\label{fig:fusion_super_sensor}
+Sensor fusion architecture}
+\end{figure}
 
-\(H_1(s)\) and \(H_2(s)\) are complementary filters:
 \begin{equation}
-  H_1(s) + H_2(s) = 1
+\label{eq:comp_filter_estimate}
+  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
 \end{equation}
@@
 \begin{equation}
-  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
+\label{eq:comp_filter}
+  H_1(s) + H_2(s) = 1
+\end{equation}
+\end{frame}
+
+\begin{frame}[label={sec:org1234068}]{Noise Sensor Filtering}
+\label{sec:noise_filtering}
+
+Perfect Sensor Dynamics:
+\begin{equation}
+\label{eq:perfect_dynamics}
+  G_1(s) = G_2(s) = 1
 \end{equation}
 
-If we now consider sensors with perfect dynamics (\(G_1(s) = G_2(s) = 1\)), we have that the estimate of \(x\) using the two sensors are shown on figure \ref{fig:fusion_two_noisy_sensors_with_dyn_ter} is:
-
+Super Sensor Estimation:
 \begin{equation}
+\label{eq:estimate_perfect_dyn}
   \hat{x} = x + H_1 n_1 + H_2 n_2
@@
 
+Noise in the Super Sensor:
+\begin{equation}
+\label{eq:noise_filtering_psd}
+  \Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2}
+\end{equation}
+
+Usually, the two sensors have high noise levels over distinct frequency regions.
+In order to lower the noise of the super sensor, the value of the norm \(|H_1|\) has to be lowered when \(\Phi_{n_1}\) is larger than \(\Phi_{n_2}\) and that of \(|H_2|\) lowered when \(\Phi_{n_2}\) is larger than \(\Phi_{n_1}\).
+\end{frame}
+
+\begin{frame}[label={sec:org9e26d3e}]{Robustness of the Fusion}
+\label{sec:fusion_robustness}
+
 \begin{figure}[htbp]
 \centering
-\includegraphics[scale=1]{figs/fusion_two_noisy_sensors_with_dyn_ter.pdf}
-\caption{\label{fig:fusion_two_noisy_sensors_with_dyn_ter}
-Sensor Fusion Architecture}
+\includegraphics[scale=1]{figs/sensor_fusion_dynamic_uncertainty.pdf}
+\caption{\label{fig:sensor_fusion_dynamic_uncertainty}
+Sensor fusion architecture with sensor dynamics uncertainty}
 \end{figure}
 
-We see that the complementary filters \(H_1(s)\) and \(H_2(s)\) operates only on the noise of the sensors.
-
-Thus, this architecture permits to filter each of the sensors without introducing any distortion in the physical quantity to measure.
+\begin{equation}
+\label{eq:super_sensor_dyn_uncertainty}
+  \frac{\hat{x}}{x} = 1 + w_1(s) H_1(s) \Delta_1(s) + w_2(s) H_2(s) \Delta_2(s)
+\end{equation}
 
 \begin{equation}
-  \delta x = \hat{x} - x = H_1 n_1 + H_2 n_2
+\label{eq:max_uncertainty_super_sensor}
+  \begin{aligned}
+    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
+    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega
+  \end{aligned}
 \end{equation}
+\end{frame}
 
-Usually, the two sensors have higher noise levels over distinct yet complementary frequency regions.
-The two complementary filters are used to combine the filtered noise and yield to a better estimate \(\hat{x}\) over a larger bandwidth.
-
-The noise of the super sensor is determine by the norm of the complementary filters.
-
-\subsection{Noise Sensor Filtering}
-\label{sec:org61f1e42}
-\label{sec:noise_filtering}
-
-\subsection{Robustness of the Fusion}
-\label{sec:org88c9440}
-\label{sec:fusion_robustness}
-
-\subsection{Upper bounds as a mathematical translation of the requirements}
-\label{sec:org2e8321f}
-\label{sec:requirements_upper_bounds}
-
-\textbf{The conclusion of the section should be that it is the norm of the complementary filter that is important and that is why we propose a method of synthesis based on H-infinity}
-
-\section{Shaping of Complementary Filters using the \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:orgd9ea119}
+\section{Complementary Filters Shaping using \(\mathcal{H}_\infty\) Synthesis}
+\label{sec:org727d73b}
 \label{sec:hinf_method}
-As shown in Sec. \ldots{}, most of the performance requirements can be expressed as upper bounds on the magnitude of the complementary filters.
-As presented in Sec. \ref{sec:trans_perf}, almost all the requirements can be specified with upper bounds on the complementary filters.
-
-Thus, the \(\mathcal{H}_\infty\) framework seems adapted and we here propose a technique to synthesis complementary filters while specifying uppers bounds on their magnitudes.
-
-\subsection{\(\mathcal{H}_\infty\) problem formulation}
-\label{sec:orgecc21d9}
+\begin{frame}[label={sec:org3adefc5}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \label{sec:hinf_synthesis}
 
-In this section, we formulate the \(\hinf\) problem for the synthesis of complementary filters.
-
-The synthesis objective is to shape an high pass filter \(H_H\) and a low pass filter \(H_L\) while ensuring their complementary property (\(H_H + H_L = 1\)).
-
-To do so, we define two weighting functions \(w_L\) and \(w_H\) that will respectively used to shape \(H_L\) and \(H_H\).
-
-The synthesis problem is then
-\begin{subnumcases}{\text{Find } H_L, H_H \text{ such that}}
-  H_L \text{ and } H_H \text{ are stable} \label{eq:hinf_cond_stability}\\
-  H_L + H_H = 1 \label{eq:hinf_cond_complementarity} \\
-  |w_L H_L| \le 1 \quad \forall\omega \label{eq:hinf_cond_hl} \\
-  |w_H H_H| \le 1 \quad \forall\omega \label{eq:hinf_cond_hh}
-\end{subnumcases}
-
-To express this synthesis problem into an \(\hinf\) synthesis problem, we define the following generalized plant \(P\) (also shown on Fig. \ref{fig:sf_hinf_filters_plant_b}):
-\begin{equation}
-\label{eq:generalized_plant}
-  \colvec{w\\u} = P \colvec{z_H \\ z_L \\ v}; \quad P = \begin{bmatrix} w_H & -w_H \\ 0 & w_L \\ 1 & 0 \end{bmatrix}
-\end{equation}
+Synthesis Objective:
+\begin{subequations}
+\label{eq:comp_filter_problem_form}
+  \begin{align}
+  & H_1(s) + H_2(s) = 1 \label{eq:hinf_cond_complementarity} \\
+  & |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h1} \\
+  & |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h2}
+  \end{align}
+\end{subequations}
 
@@
 \caption{\label{fig:h_infinity_robust_fusion}
-Architecture used for the \(\mathcal{H}_\infty\) synthesis of complementary filters}
+Architecture used for \(\mathcal{H}_\infty\) synthesis of complementary filters}
 \end{figure}
 
-The \(\hinf\) synthesis objective is then to design a stable filter \(H_L\) (Fig.
-\ref{fig:sf_hinf_filters_b}) such that the \(\mathcal{H}_\infty\) norm of the transfer function from \(w\) to \([z_H, \ z_L]\) is less than \(1\):
 \begin{equation}
-  \hnorm{\begin{matrix} (1 - H_L) w_H \\ H_L w_L \end{matrix}} \le 1
-\end{equation}
-Which is equivalent to
-\begin{equation}
-\label{eq:hinf_problem}
-  \hnorm{\begin{matrix} H_H w_H \\ H_L w_L \end{matrix}} < 1 \text{ by choosing } H_H = 1 - H_L
+\label{eq:hinf_syn_obj}
+  \left\|\begin{matrix} \left[1 - H_2(s)\right] W_1(s) \\ H_2(s) W_2(s) \end{matrix}\right\|_\infty \le 1
 \end{equation}
 
-Performance conditions \eqref{eq:hinf_cond_hl} and \eqref{eq:hinf_cond_hl} are satisfied by \eqref{eq:hinf_problem}.
-Complementary condition \eqref{eq:hinf_cond_complementarity} is satisfied by design: \(H_H = 1 - H_L\) and thus \(H_L + H_H = 1\).
-The stability condition \eqref{eq:hinf_cond_stability} is guaranteed by the \(H_\infty\) synthesis (\textbf{reference}).
+\begin{equation}
+\label{eq:definition_H1}
+  H_1(s) \triangleq 1 - H_2(s)
+\end{equation}
+\end{frame}
 
-Using this synthesis method, we are then able to shape at the same time the high pass and low pass filters while ensuring their complementary.
-
-\subsection{Choice of the weighting functions}
-\label{sec:org6167188}
+\begin{frame}[label={sec:org90726d8}]{Weighting Functions Design}
 \label{sec:hinf_weighting_func}
-
-We here give some advice on the design of the weighting functions used for the synthesis of the complementary filters using the \(\mathcal{H}_\infty\) method.
-
-The weighting functions should be such that the performance requirements are met as explain in Sec. \ref{sec:trans_perf}.
-
-However, one should be careful when designing the complementary filters, and should only use stable and minimum phase transfer functions.
-The order of the weights should stay reasonably small as this will increase the complexity of the optimization problem.
-
-Moreover, the order of the complementary filters will be equal to the sum of the order of the weighting functions used.
-
-One should not forget the fundamental limitations imposed by the synthesis: \(H_L(s) + H_H(s) = 1\).
-This implies that \(H_L\) and \(H_H\) cannot be made small at the same time.
-
-We here propose a formula for the design of the weighting function \eqref{eq:weight_formula}.
-
 \begin{equation}
 \label{eq:weight_formula}
-  W(s) = \left(\frac{
-           \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
+  W(s) = \left( \frac{
+           \hfill{} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
          }{
            \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
-         }}\right)^n
+         }\right)^n
 \end{equation}
-with:
-\begin{itemize}
-\item \(G_0\) is the absolute gain at low frequency
-\item \(G_\infty\) is the absolute gain at high frequency
-\item \(\omega_0\) and \(G_c\) define the absolute value of the filter at \(\omega = \omega_0\): \(|W(j\omega_0)| = G_c\)
-\item \(n\) is the absolute slope of the filter, it is also equal to the order of the filter
-\end{itemize}
-
-The constrains are that \(G_0 < 1 < G_\infty\) and \(G_0 < G_c < G_\infty\) or that \(G_\infty < 1 < G_0\) and \(G_\infty < G_c < G_0\).
-
-The shape of the weight generated using the formula is shown on figure \ref{fig:weight_formula}.
 
@@
 \caption{\label{fig:weight_formula}
-Amplitude of the proposed formula for the weighting functions, \(G_0 = 1e^{-3}\), \(G_\infty = 10\), \(\omega_c = \SI{10}{Hz}\), \(G_c = 2\), \(n = 3\)}
+Magnitude of a weighting function generated using the formula}
 \end{figure}
+\end{frame}
 
-\subsection{Example}
-\label{sec:orgb30ba62}
+\begin{frame}[label={sec:orgbb615dc}]{Validation of the proposed synthesis method}
 \label{sec:hinf_example}
-
-We are now using the proposed \(\mathcal{H}_\infty\) complementary filters synthesis method for a simple example.
-
-The goal is to design
-
-We use the formula \eqref{eq:weight_formula} for both \(w_L(s)\) and \(w_H(s)\).
-The parameters used are summarized on table \ref{tab:weights_params}. And the magnitude of the weighting functions are shown on figure \ref{fig:weights_wl_wh}.
-
-\begin{table}[!htpb]
-\caption{\label{tab:weights_params}
-Parameters used for the weighting functions}
-\centering
-\begin{tabular}{|l|X|X|}
-\hline
-Parameters & \(w_L\) & \(w_H\)\\
-\hline
-\(G_0\) & \(0.1\) & \(1000\)\\
-\hline
-\(G_\infty\) & \(1000\) & \(0.1\)\\
-\hline
-\(\omega_c\) [\(\si{Hz}\)] & \(11\) & \(10\)\\
-\hline
-\(G_c\) & \(2\) & \(2\)\\
-\hline
-\(n\) & \(2\) & \(3\)\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/weights_wl_wh.pdf}
-\caption{\label{fig:weights_wl_wh}
-Weighting Functions used for the \(\mathcal{H}_\infty\) Synthesis}
-\end{figure}
-
-After synthesis, the obtain filters are:
-\begin{align}
-  H_L(s) &= \frac{10^{-8} (s+6.6e^9) (s+3450)^2 (s^2 + 49s + 895)}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}\\
-  H_H(s) &= \frac{(s+6.6e^4) (s+160) (s+4)^3}{(s+6.6e^4) (s^2 + 106 s + 3000) (s^2 + 72s + 3580)}
-\end{align}
-
-Their bode plot is shown on figure \ref{fig:hinf_synthesis_results}.
-
 \begin{figure}[htbp]
@@
 \caption{\label{fig:hinf_synthesis_results}
-Obtain Complementary Filters}
+Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
+\end{frame}
 
-\subsection{Synthesis of Three Complementary Filters}
-\label{sec:org415d7ce}
+\begin{frame}[label={sec:org1e9511a}]{Synthesis of Three Complementary Filters}
 \label{sec:hinf_three_comp_filters}
-
-We want:
-\begin{align*}
-  & |H_1 w_1| < 1, \quad \forall\omega\\
-  & |H_2 w_2| < 1, \quad \forall\omega\\
-  & |H_3 w_3| < 1, \quad \forall\omega\\
-  & H_1 + H_2 + H_3 = 1
-\end{align*}
-
-The \(\mathcal{H}_\infty\) objective is:
-\begin{align*}
-  & |H_1 w_1| < 1, \quad \forall\omega\\
-  & |H_2 w_2| < 1, \quad \forall\omega\\
-  & |(1 - H_1 - H_2) w_3| < 1, \quad \forall\omega\\
-\end{align*}
-
-And thus if we choose \(H_3 = 1 - H_1 - H_2\) we have solved the problem.
-
 \begin{figure}[htbp]
@@
 \caption{\label{fig:hinf_three_synthesis_results}
-Figure caption}
+Frequency response of the weighting functions and three complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
+\end{frame}
 
-\section{Application to the design of}
-\label{sec:org57876bd}
+\section{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}
+\label{sec:org282c8fb}
 \label{sec:application_ligo}
+\begin{frame}[label={sec:org17c24af}]{Application}
+Several complementary filters are used in the active isolation system at the LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
+The requirements on those filters are very tight and thus their design is complex.
+The approach used in \cite{hua05_low_ligo} for their design is to write the synthesis of complementary FIR filters as a convex optimization problem.
+The obtained FIR filters are compliant with the requirements. However they are of very high order so their implementation is quite complex.
 
-\subsection{Specifications}
-\label{sec:orgc79cee4}
+The effectiveness of the proposed method is demonstrated by designing complementary filters with the same requirements as the one described in \cite{hua05_low_ligo}.
+\end{frame}
+
+\begin{frame}[label={sec:org1f8bc6e}]{Complementary Filters Specifications}
 \label{sec:ligo_specifications}
+\begin{itemize}
+\item From \(0\) to \(\SI{0.008}{Hz}\), the magnitude of the filter's transfer function should be less or equal to \(8 \times 10^{-4}\)
+\item Between \(\SI{0.008}{Hz}\) to \(\SI{0.04}{Hz}\), the filter should attenuate the input signal proportional to frequency cubed
+\item Between \(\SI{0.04}{Hz}\) to \(\SI{0.1}{Hz}\), the magnitude of the transfer function should be less than \(3\)
+\item Above \(\SI{0.1}{Hz}\), the magnitude of the complementary filter should be less than \(0.045\)
+\end{itemize}
 
@@
 \centering
-\includegraphics[scale=1]{figs/ligo_specifications.pdf}
-\caption{\label{fig:ligo_specifications}
-Specifications on the norms of the complementary filters}
+\includegraphics[scale=1]{figs/ligo_weights.pdf}
+\caption{\label{fig:ligo_weights}
+Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
+\end{frame}
 
-\subsection{Weighting functions design}
-\label{sec:org6e51da2}
+\begin{frame}[label={sec:org305a6e1}]{Weighting Functions Design}
 \label{sec:ligo_weights}
@@
 \caption{\label{fig:ligo_weights}
-Weighting Functions used for the \(\mathcal{H}_\infty\) synthesis}
+Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
+\end{frame}
 
-\subsection{Comparison}
-\label{sec:org06ff1a1}
+\begin{frame}[label={sec:org1aa43d2}]{\(\mathcal{H}_\infty\) Synthesis}
 \label{sec:ligo_results}
@@
 \caption{\label{fig:comp_fir_ligo_hinf}
-Comparison of the filters obtain with the \(\mathcal{H}_\infty\) synthesis and the FIR filters designed in \cite{hua05_low_ligo}}
+Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with \(\mathcal{H}_\infty\) synthesis (dashed)}
 \end{figure}
+\end{frame}
 
 \section{Conclusion}
-\label{sec:orga86d375}
+\label{sec:org425430e}
 \label{sec:conclusion}
-
-\section{Acknowledgment}
-\label{sec:org8d338b6}
-
+\begin{frame}[label={sec:org3cfbc70}]{Conclusion}
+This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
+Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
+Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
+Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.
+\end{frame}
+\section{Bibliography}
+\label{sec:org404b871}
+\begin{frame}[label={sec:org03eccb0}]{Bibliography}
+\bibliographystyle{unsrt}
 \bibliography{ref}
+\end{frame}
 \end{document}

### 2019-08-28 presentation/presentation.tex
Worked on the presentation for LIGO meeting

@@
-% Created 2019-08-22 jeu. 11:06
+% Created 2019-08-28 mer. 11:49
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{siunitx}
-\AtBeginSection[]{
-\begin{frame}<beamer>{Table of Contents}
-\tableofcontents[currentsection, hideothersubsections, sectionstyle=show/shaded]
-\end{frame}
+\beamertemplatenavigationsymbolsempty
+\addtobeamertemplate{navigation symbols}{}{%
+\usebeamerfont{footline}%
+\usebeamercolor[fg]{footline}%
+\hspace{1em}%
+\insertframenumber/\inserttotalframenumber
 }
+\setbeamertemplate{itemize items}[circle]
+\usefonttheme[onlymath]{serif}
+\definecolor{mycolor1}{RGB}{79,115,193}
+\definecolor{mycolor2}{RGB}{213,91,53}
 \usetheme{default}
 \author{Dehaeze Thomas}
-\date{07-11-2019}
+\date{2019-08-28}
 \title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
-\subtitle{ICCMA 2019}
+\subtitle{Control System Working Group meeting}
 \hypersetup{
@@
  pdfkeywords={complementary filters, h-infinity, sensor fusion},
- pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation at ICCMA 2019.},
+ pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
  pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
@@
 \maketitle
-\begin{frame}{Outline}
-\tableofcontents
+
+\section{Complementary Filters Shaping}
+\label{sec:org40f8eb6}
+\begin{frame}[label={sec:org0a9a28a}]{Sensor Fusion Architecture - Noise Filtering}
+\vspace{-1em}
+\begin{columns}
+\begin{column}{0.45\columnwidth}
+\vspace{-1em}
+\begin{center}
+\includegraphics[scale=1,width=1.1\linewidth]{figs/fusion_super_sensor.pdf}
+\end{center}
+\end{column}
+
+\begin{column}{0.55\columnwidth}
+\begin{equation*}
+  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
+\end{equation*}
+
+\onslide{\begin{cbox}[Complementary Property]{blue}{}
+\begin{equation*}
+  H_1(s) + H_2(s) = 1
+\end{equation*}
+\end{cbox}}\vspace{0.5em}
+\end{column}
+\end{columns}
+
+\vspace{0.5em}
+Let's first consider \textbf{Perfectly Known Sensor Dynamics}:
+\begin{equation*}
+  G_1(s) = G_2(s) = 1 \Longrightarrow \hat{x} = x + H_1 n_1 + H_2 n_2
+\end{equation*}
+
+\onslide{\begin{cbox}[PSD of the Super Sensor's noise]{blue}{ams nodisplayskip}
+\begin{equation*}
+  \Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
+\end{equation*}
+\end{cbox}}\vspace{0.5em}
 \end{frame}
 
-\section{Introduction}
-\label{sec:org4eff5bb}
-\label{sec:introduction}
+\begin{frame}[label={sec:orgbe85fff}]{Sensor Fusion Architecture - Robustness}
+\begin{columns}
+\begin{column}{0.5\columnwidth}
+\vspace{-2em}
+\begin{center}
+\includegraphics[scale=1,width=1.1\linewidth]{figs/sensor_fusion_dynamic_uncertainty.pdf}
+\end{center}
+\end{column}
 
-\begin{frame}[label={sec:org6dbc4f9}]{Introduction}
-High bandwidth
-\begin{itemize}
-\item need of Sensor at low frequency + sensor at high frequency
-\item need of merging the two
-\item complementary filters
-\item design of those filters using \(\mathcal{H}_\infty\)
-\end{itemize}
+\begin{column}{0.5\columnwidth}
+\textbf{Dynamic Uncertainty}:
+\begin{gather*}
+  G_i^\prime(s) = G_i(s) [1 + w_i(s)\Delta_i(s)],\\
+  \quad \forall\Delta_i, \|\Delta_i\|_\infty < 1
+\end{gather*}
+
+\textbf{Super Sensor Dynamics}:
+\begin{equation*}
+  \frac{\hat{x}}{x} = 1 + w_1 H_1 \Delta_1 + w_2 H_2 \Delta_2
+\end{equation*}
+\end{column}
+\end{columns}
+
+\vspace{0.5em}
+\onslide{\begin{cbox}[Limit the Super Sensor Dynamic uncertainty]{blue}{}
+Design \(H_1(s)\) and \(H_2(s)\) such that:
+\begin{equation*}
+  \begin{aligned}
+                    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
+    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega \\
+    \Longrightarrow & \text{ depends on the filters' norm} \\
+  \end{aligned}
+\end{equation*}
+\end{cbox}}\vspace{0.5em}
 \end{frame}
 
-\section{Complementary Filters Requirements}
-\label{sec:org49f4bb1}
-\label{sec:requirements}
-\begin{frame}[label={sec:orgd4e76ba}]{Sensor Fusion Architecture}
-\label{sec:sensor_fusion}
+\begin{frame}[label={sec:org44eb698}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\vspace{-1em}
+\begin{columns}
+\begin{column}{0.5\columnwidth}
+\onslide{\begin{cbox}[Design Objective]{blue}{ams nodisplayskip}
+\begin{gather*}
+  H_1(s) + H_2(s) = 1 \\
+  |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \\
+  |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega
+\end{gather*}
+\end{cbox}}\vspace{0.5em}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/fusion_super_sensor.pdf}
-\caption{\label{fig:fusion_super_sensor}
-Sensor fusion architecture}
-\end{figure}
+\onslide{\begin{cbox}[]{blue}{}
+\(W_1(s)\) and \(W_2(s)\) are proper, stable and minimum phase transfer functions
+\end{cbox}}\vspace{0.5em}
+\end{column}
 
-\begin{equation}
-\label{eq:comp_filter_estimate}
-  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
-\end{equation}
+\begin{column}{0.5\columnwidth}
+\vspace{-3em}
+\begin{center}
+\includegraphics[scale=1,width=\linewidth]{figs/h_infinity_robust_fusion.pdf}
+\end{center}
 
-\begin{equation}
-\label{eq:comp_filter}
-  H_1(s) + H_2(s) = 1
-\end{equation}
+\onslide{\begin{cbox}[\(\mathcal{H}_\infty\) Synthesis]{blue}{}
+Find \(H_2(s)\) such that:
+\begin{gather*}
+  \left\|\begin{matrix} \left[1 - H_2(s)\right] W_1(s) \\ H_2(s) W_2(s) \end{matrix}\right\|_\infty \le 1 \\
+  H_1(s) \triangleq 1 - H_2(s)
+\end{gather*}
+\end{cbox}}\vspace{0.5em}
+\end{column}
+\end{columns}
 \end{frame}
 
-\begin{frame}[label={sec:org1234068}]{Noise Sensor Filtering}
-\label{sec:noise_filtering}
-
-Perfect Sensor Dynamics:
-\begin{equation}
-\label{eq:perfect_dynamics}
-  G_1(s) = G_2(s) = 1
-\end{equation}
-
-Super Sensor Estimation:
-\begin{equation}
-\label{eq:estimate_perfect_dyn}
-  \hat{x} = x + H_1 n_1 + H_2 n_2
-\end{equation}
-
-Noise in the Super Sensor:
-\begin{equation}
-\label{eq:noise_filtering_psd}
-  \Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2}
-\end{equation}
-
-Usually, the two sensors have high noise levels over distinct frequency regions.
-In order to lower the noise of the super sensor, the value of the norm \(|H_1|\) has to be lowered when \(\Phi_{n_1}\) is larger than \(\Phi_{n_2}\) and that of \(|H_2|\) lowered when \(\Phi_{n_2}\) is larger than \(\Phi_{n_1}\).
+\begin{frame}[label={sec:orgafaab6e}]{Validation of the proposed synthesis method}
+\begin{center}
+\includegraphics[scale=1,width=0.85\linewidth]{figs/hinf_synthesis_results.pdf}
+\end{center}
 \end{frame}
 
-\begin{frame}[label={sec:org9e26d3e}]{Robustness of the Fusion}
-\label{sec:fusion_robustness}
+\begin{frame}[label={sec:org2fc9535}]{Complementary Filters Specifications - Weights}
+\onslide{\begin{cbox}[]{blue}{}
+\begin{center}
+\begin{tabular}{ll}
+\(\tikz[baseline=-0.5ex]{\draw[color=mycolor1, line width=1.5pt](0,0)--(1,0)}\) & Custom Designed \(7^{\text{th}}\) Order Transfer Function\\
+\(\tikz[baseline=-0.5ex]{\draw[color=mycolor2, line width=1.5pt](0,0)--(1,0)}\) & Type I Chebyshev Filter of Order \(20\)\\
+\end{tabular}
+\end{center}
+\end{cbox}}\vspace{0.5em}
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/sensor_fusion_dynamic_uncertainty.pdf}
-\caption{\label{fig:sensor_fusion_dynamic_uncertainty}
-Sensor fusion architecture with sensor dynamics uncertainty}
-\end{figure}
+\begin{center}
+\includegraphics[scale=1,width=0.8\linewidth]{figs/ligo_weights.pdf}
+\end{center}
 
-\begin{equation}
-\label{eq:super_sensor_dyn_uncertainty}
-  \frac{\hat{x}}{x} = 1 + w_1(s) H_1(s) \Delta_1(s) + w_2(s) H_2(s) \Delta_2(s)
-\end{equation}
-
-\begin{equation}
-\label{eq:max_uncertainty_super_sensor}
-  \begin{aligned}
-    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
-    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega
-  \end{aligned}
-\end{equation}
+The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
 \end{frame}
 
-\section{Complementary Filters Shaping using \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:org727d73b}
-\label{sec:hinf_method}
-\begin{frame}[label={sec:org3adefc5}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
-\label{sec:hinf_synthesis}
-
-Synthesis Objective:
-\begin{subequations}
-\label{eq:comp_filter_problem_form}
-  \begin{align}
-  & H_1(s) + H_2(s) = 1 \label{eq:hinf_cond_complementarity} \\
-  & |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h1} \\
-  & |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega \label{eq:hinf_cond_h2}
-  \end{align}
-\end{subequations}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/h_infinity_robust_fusion.pdf}
-\caption{\label{fig:h_infinity_robust_fusion}
-Architecture used for \(\mathcal{H}_\infty\) synthesis of complementary filters}
-\end{figure}
-
-\begin{equation}
-\label{eq:hinf_syn_obj}
-  \left\|\begin{matrix} \left[1 - H_2(s)\right] W_1(s) \\ H_2(s) W_2(s) \end{matrix}\right\|_\infty \le 1
-\end{equation}
-
-\begin{equation}
-\label{eq:definition_H1}
-  H_1(s) \triangleq 1 - H_2(s)
-\end{equation}
-\end{frame}
-
-\begin{frame}[label={sec:org90726d8}]{Weighting Functions Design}
-\label{sec:hinf_weighting_func}
-\begin{equation}
-\label{eq:weight_formula}
-  W(s) = \left( \frac{
-           \hfill{} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
-         }{
-           \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
-         }\right)^n
-\end{equation}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/weight_formula.pdf}
-\caption{\label{fig:weight_formula}
-Magnitude of a weighting function generated using the formula}
-\end{figure}
-\end{frame}
-
-\begin{frame}[label={sec:orgbb615dc}]{Validation of the proposed synthesis method}
-\label{sec:hinf_example}
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
-\caption{\label{fig:hinf_synthesis_results}
-Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
-\end{figure}
-\end{frame}
-
-\begin{frame}[label={sec:org1e9511a}]{Synthesis of Three Complementary Filters}
-\label{sec:hinf_three_comp_filters}
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_filter_three_hinf.pdf}
-\caption{\label{fig:comp_filter_three_hinf}
-Architecture for \(\mathcal{H}_\infty\) synthesis of three complementary filters}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/hinf_three_synthesis_results.pdf}
-\caption{\label{fig:hinf_three_synthesis_results}
-Frequency response of the weighting functions and three complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
-\end{figure}
-\end{frame}
-
-\section{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}
-\label{sec:org282c8fb}
-\label{sec:application_ligo}
-\begin{frame}[label={sec:org17c24af}]{Application}
-Several complementary filters are used in the active isolation system at the LIGO \cite{hua05_low_ligo,hua04_polyp_fir_compl_filter_contr_system}.
-The requirements on those filters are very tight and thus their design is complex.
-The approach used in \cite{hua05_low_ligo} for their design is to write the synthesis of complementary FIR filters as a convex optimization problem.
-The obtained FIR filters are compliant with the requirements. However they are of very high order so their implementation is quite complex.
-
-The effectiveness of the proposed method is demonstrated by designing complementary filters with the same requirements as the one described in \cite{hua05_low_ligo}.
-\end{frame}
-
-\begin{frame}[label={sec:org1f8bc6e}]{Complementary Filters Specifications}
-\label{sec:ligo_specifications}
-\begin{itemize}
-\item From \(0\) to \(\SI{0.008}{Hz}\), the magnitude of the filter's transfer function should be less or equal to \(8 \times 10^{-4}\)
-\item Between \(\SI{0.008}{Hz}\) to \(\SI{0.04}{Hz}\), the filter should attenuate the input signal proportional to frequency cubed
-\item Between \(\SI{0.04}{Hz}\) to \(\SI{0.1}{Hz}\), the magnitude of the transfer function should be less than \(3\)
-\item Above \(\SI{0.1}{Hz}\), the magnitude of the complementary filter should be less than \(0.045\)
-\end{itemize}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/ligo_weights.pdf}
-\caption{\label{fig:ligo_weights}
-Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
-\end{figure}
-\end{frame}
-
-\begin{frame}[label={sec:org305a6e1}]{Weighting Functions Design}
-\label{sec:ligo_weights}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/ligo_weights.pdf}
-\caption{\label{fig:ligo_weights}
-Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
-\end{figure}
-\end{frame}
-
-\begin{frame}[label={sec:org1aa43d2}]{\(\mathcal{H}_\infty\) Synthesis}
-\label{sec:ligo_results}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
-\caption{\label{fig:comp_fir_ligo_hinf}
-Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with \(\mathcal{H}_\infty\) synthesis (dashed)}
-\end{figure}
-\end{frame}
-
-\section{Conclusion}
-\label{sec:org425430e}
-\label{sec:conclusion}
-\begin{frame}[label={sec:org3cfbc70}]{Conclusion}
-This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
-Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
-Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
-Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.
-\end{frame}
-\section{Bibliography}
-\label{sec:org404b871}
-\begin{frame}[label={sec:org03eccb0}]{Bibliography}
-\bibliographystyle{unsrt}
-\bibliography{ref}
+\begin{frame}[label={sec:orgc18d54e}]{\(\mathcal{H}_\infty\) Synthesis}
+\begin{center}
+\includegraphics[scale=1,width=0.8\linewidth]{figs/comp_fir_ligo_hinf.pdf}
+\end{center}
 \end{frame}

### 2019-08-28 presentation/presentation.tex
Change few slides

@@
-% Created 2019-08-28 mer. 11:49
+% Created 2019-08-28 mer. 12:04
 % Intended LaTeX compiler: pdflatex
@@
 \section{Complementary Filters Shaping}
-\label{sec:org40f8eb6}
-\begin{frame}[label={sec:org0a9a28a}]{Sensor Fusion Architecture - Noise Filtering}
+\label{sec:orgdcf129e}
+\begin{frame}[label={sec:orgde41700}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:orgbe85fff}]{Sensor Fusion Architecture - Robustness}
+\begin{frame}[label={sec:orgf3b5e26}]{Sensor Fusion Architecture - Robustness}
 \begin{columns}
@@
 
-\begin{frame}[label={sec:org44eb698}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:orgf0b2054}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:orgafaab6e}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:org2d6cd37}]{Validation of the proposed synthesis method}
 \begin{center}
@@
 
-\begin{frame}[label={sec:org2fc9535}]{Complementary Filters Specifications - Weights}
-\onslide{\begin{cbox}[]{blue}{}
+\begin{frame}[label={sec:org2f1e4c4}]{Complementary Filters Used at LIGO - Specifications}
+The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
+
+\begin{center}
+\includegraphics[scale=1,width=0.8\linewidth]{figs/ligo_weights.pdf}
+\end{center}
+
+\onslide{\begin{cbox}[Weighting Functions used]{blue}{}
 \begin{center}
@@
 \end{cbox}}\vspace{0.5em}
-
-\begin{center}
-\includegraphics[scale=1,width=0.8\linewidth]{figs/ligo_weights.pdf}
-\end{center}
-
-The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
 \end{frame}
 
-\begin{frame}[label={sec:orgc18d54e}]{\(\mathcal{H}_\infty\) Synthesis}
+\begin{frame}[label={sec:orgf57371a}]{\(\mathcal{H}_\infty\) Synthesis - Comparison}
+\vspace{-1em}
+\begin{columns}
+\begin{column}{0.6\columnwidth}
+\vspace{-2em}
 \begin{center}
-\includegraphics[scale=1,width=0.8\linewidth]{figs/comp_fir_ligo_hinf.pdf}
+\includegraphics[scale=1,width=1.1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
 \end{center}
+\end{column}
+
+\begin{column}{0.4\columnwidth}
+\begin{itemize}
+\item FIR Filters: order 512
+\item \(\mathcal{H}_\infty\) Filters: order 27
+\end{itemize}
+\end{column}
+\end{columns}
+
+\onslide{\begin{cbox}[Conclusion]{blue}{}
+Easy to use synthesis method of complementary filters
+\end{cbox}}\vspace{0.5em}
 \end{frame}

### 2019-08-28 presentation/presentation.tex
Update conclusion slide

@@
-% Created 2019-08-28 mer. 12:04
+% Created 2019-08-28 mer. 12:10
 % Intended LaTeX compiler: pdflatex
@@
 \section{Complementary Filters Shaping}
-\label{sec:orgdcf129e}
-\begin{frame}[label={sec:orgde41700}]{Sensor Fusion Architecture - Noise Filtering}
+\label{sec:orga90b74d}
+\begin{frame}[label={sec:orgc30113d}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:orgf3b5e26}]{Sensor Fusion Architecture - Robustness}
+\begin{frame}[label={sec:org78632cf}]{Sensor Fusion Architecture - Robustness}
 \begin{columns}
@@
 
-\begin{frame}[label={sec:orgf0b2054}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:org1c8ad51}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:org2d6cd37}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:orgd10d7f7}]{Validation of the proposed synthesis method}
 \begin{center}
@@
 
-\begin{frame}[label={sec:org2f1e4c4}]{Complementary Filters Used at LIGO - Specifications}
+\begin{frame}[label={sec:org67fb3d7}]{Complementary Filters Used at LIGO - Specifications}
 The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
@@
 
-\begin{frame}[label={sec:orgf57371a}]{\(\mathcal{H}_\infty\) Synthesis - Comparison}
+\begin{frame}[label={sec:orgb4f9c19}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
 \vspace{-1em}
@@
 \onslide{\begin{cbox}[Conclusion]{blue}{}
-Easy to use synthesis method of complementary filters
+Specifications: expressed as upper bounds on the filters' norm\\
+\(\mathcal{H}_\infty\) Synthesis: easily shape complex complementary filters
 \end{cbox}}\vspace{0.5em}

### 2019-08-28 presentation/presentation.tex
Add link to repository, add link colors

@@
-% Created 2019-08-28 mer. 12:10
+% Created 2019-08-28 mer. 13:50
 % Intended LaTeX compiler: pdflatex
@@
 \subtitle{Control System Working Group meeting}
+\hypersetup{colorlinks=true}
 \hypersetup{
@@
 \section{Complementary Filters Shaping}
-\label{sec:orga90b74d}
-\begin{frame}[label={sec:orgc30113d}]{Sensor Fusion Architecture - Noise Filtering}
+\label{sec:orgeac405f}
+\begin{frame}[label={sec:org7acc6c9}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 \begin{equation*}
-  \Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
+  \Phi_{\hat{x}} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
 \end{equation*}
@@
 
-\begin{frame}[label={sec:org78632cf}]{Sensor Fusion Architecture - Robustness}
+\begin{frame}[label={sec:orgc2c6d2b}]{Sensor Fusion Architecture - Robustness}
 \begin{columns}
@@
 
-\begin{frame}[label={sec:org1c8ad51}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:orgf43ebc6}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:orgd10d7f7}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:org65cb237}]{Validation of the proposed synthesis method}
 \begin{center}
@@
 
-\begin{frame}[label={sec:org67fb3d7}]{Complementary Filters Used at LIGO - Specifications}
+\begin{frame}[label={sec:org8b0df25}]{Complementary Filters Used at LIGO - Specifications}
 The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
@@
 
-\begin{frame}[label={sec:orgb4f9c19}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
-\vspace{-1em}
+\begin{frame}[label={sec:org114463e}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
 \begin{columns}
 \begin{column}{0.6\columnwidth}
-\vspace{-2em}
+\vspace{-3em}
 \begin{center}
@@
 \end{itemize}
+
+\vspace{1em}
+
+\onslide{\begin{cbox}[]{blue}{}
+The paper and all the Matlab Scripts used for the paper are accessible \href{https://tdehaeze.github.io/dehaeze19\_desig\_compl\_filte/}{here}.
+\end{cbox}}\vspace{0.5em}
 \end{column}

### 2019-08-28 presentation/presentation.tex
Add notes for the presentation

@@
-% Created 2019-08-28 mer. 13:50
+% Created 2019-08-28 mer. 15:30
 % Intended LaTeX compiler: pdflatex
@@
 \section{Complementary Filters Shaping}
-\label{sec:orgeac405f}
-\begin{frame}[label={sec:org7acc6c9}]{Sensor Fusion Architecture - Noise Filtering}
+\label{sec:orgf40a445}
+\begin{frame}[label={sec:org644c6eb}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 \begin{equation*}
-  \Phi_{\hat{x}} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
+  \Phi_{\text{ss}} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
 \end{equation*}
@@
 
-\begin{frame}[label={sec:orgc2c6d2b}]{Sensor Fusion Architecture - Robustness}
+\begin{frame}[label={sec:orgaee2e4a}]{Sensor Fusion Architecture - Robustness}
 \begin{columns}
@@
 
-\vspace{0.5em}
 \onslide{\begin{cbox}[Limit the Super Sensor Dynamic uncertainty]{blue}{}
@@
                     & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
-    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega \\
+    \Longleftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega \\
     \Longrightarrow & \text{ depends on the filters' norm} \\
@@
 
-\begin{frame}[label={sec:orgf43ebc6}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:org1c42552}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:org65cb237}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:org493a937}]{Validation of the proposed synthesis method}
 \begin{center}
@@
 
-\begin{frame}[label={sec:org8b0df25}]{Complementary Filters Used at LIGO - Specifications}
+\begin{frame}[label={sec:orga95f64f}]{Complementary Filters Used at LIGO - Specifications}
 The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
@@
 
-\begin{frame}[label={sec:org114463e}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
+\begin{frame}[label={sec:org3e0dbb2}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
 \begin{columns}

### 2019-08-28 presentation/notes.tex
Add presentation notes own file

% Created 2019-08-28 mer. 16:01
% Intended LaTeX compiler: pdflatex
\documentclass[hangsection=false, titlepage=false, tocnp=false]{cleanreport}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\newcommand{\authorFirstName}{Thomas}
\newcommand{\authorLastName}{Dehaeze}
\newcommand{\authorEmail}{dehaeze.thomas@gmail.com}
\author{Dehaeze Thomas}
\date{2019-08-28}
\title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis\\\medskip
\large Control System Working Group meeting}
\hypersetup{
 pdfauthor={Dehaeze Thomas},
 pdftitle={Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis},
 pdfkeywords={complementary filters, h-infinity, sensor fusion},
 pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

\maketitle

\section{Title Slide - Introduction}
\label{sec:org2616a5c}
Hi everyone,

Thank you for the invitation.

My name is Thomas Dehaeze and I am a PhD student working in the Precision Mechatronic Laboratory in Belgium.

I will present you recent work that myself, my supervisor Christophe Collette and a post-doc colleague Mohit Verma have done about sensor fusion and the synthesis of complementary filters.

\section{Sensor Fusion Architecture - Noise Filtering}
\label{sec:org3776d94}
A typical sensor fusion architecture is represented here where the signal of two sensors measuring the same quantity \(x\) are filtered out by two filters \(H_1\) and \(H_2\) and then combined to give a estimate \(\hat{x}\) of \(x\).

Each sensor have different noise characteristics \(n_1\) and \(n_2\) and dynamics \(G_1\) and \(G_2\).

We consider that the two filters \(H_1\) and \(H_2\) are complementary, meaning that the sum of their transfer function is equal to one.

If we first consider that the sensor dynamics is perfectly known, we can inverse the sensor dynamics to obtain \(G_1 = G_2 = 1\). And the estimate \(\hat{x}\) is equal to \(x\) plus the noise of the individual sensors filtered out by the associated filter.

The Power Spectral Density of the super sensor noise then depends on both the PSD of \(n_1\) and \(n_2\), but also on the norms of the complementary filters.

Thus, it is usually wanted that the filters are designed such that the norm of \(H_1\) is small when \(n_1\) is larger than \(n_2\) and the norm of \(H_2\) is small when \(n_2\) is large than \(n_1\). We can then obtain a super sensor that has overall less noise than both individual sensors.

\section{Sensor Fusion Architecture - Robustness}
\label{sec:org75a0990}
However, in practical systems, the sensor dynamics is never exactly known and cannot be perfectly inverted.

We can represent this by a multiplicative uncertainty on the dynamics of each sensor where
\begin{itemize}
\item \(w\) is a weight that represents the magnitude of the uncertainty
\item \(\Delta\) can be any stable transfer function with its \(\mathcal{H}_\infty\) norm less than 1
\end{itemize}

The super sensor dynamics uncertainty depends both on the uncertainty weights and on the complementary filters.

This dynamic uncertainty is problematic as it introduces unwanted phase lag and will limit the attainable bandwidth.

In order to limit the super sensor dynamic uncertainty, \(H_1\) and \(H_2\) have to be designed such that:
\begin{itemize}
\item the norm of \(H_1\) is small when the uncertainty on sensor 1 is large
\item the norm of \(H_2\) is small when the uncertainty on sensor 2 is large
\end{itemize}

Doing so, it is possible to obtain a super sensor with less dynamic uncertainty than the individual sensors.
This could allow to increase the control bandwidth.

With these two simple examples, we see that the norm of the complementary filters have a huge impact on both the performance and the robustness of the sensor fusion architecture.

This is why we worked on the development of a synthesis method that permits to shape the norms of the complementary filters.

\section{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
\label{sec:org4d70a51}
The design objective is thus to design two complementary filters \(H_1\) and \(H_2\) such that the norms of \(H_1\) and \(H_2\) are below some defined weights \(W_1\) and \(W_2\).

If apply the \(\mathcal{H}_\infty\) synthesis on the shown generalized plant that includes the two weights \(W_1\) and \(W_2\), the algorithm will find a stable filter \(H_2\) such that the \(\mathcal{H}_\infty\) norm between \(w\) and \([z_1,\ z_2]\) is less than 1.

By then defining \(H_1\) to be the complementary of \(H_2\), we see that this \(\mathcal{H}_\infty\) synthesis problem corresponds to the design objective.

\section{Validation of the proposed synthesis method}
\label{sec:orgd012b55}
We then used this synthesis method to design complementary filters.

We started with relatively simple complementary filters.
Here, the dashed curves are the inverse magnitude of the chosen weights that defines the maximum allowed norm of the complementary filters.
The solid curves represents the synthesized complementary filters using the \(\mathcal{H}_\infty\) synthesis.

\section{Complementary Filters Used at LIGO - Specifications}
\label{sec:orgc32f967}
We then wanted to validate this synthesis method for the design of more complex complementary filters.

We chose one pair of complementary filters that are designed in the PhD thesis of Hua and used at the LIGO.

The specifications on the norms of the filters are shown by the black dashed lines and the solid curves are the inverse magnitude of the designed weighting functions.

The weights are designed to be as close as possible to the specifications in order to not over constrain the synthesis problem.
Also, the order of the weights are kept reasonably small as the synthesized complementary filter will have an order equal to the sum of the weights order.

The weighting functions used are a custom designed 7th order transfer function for the high pass filter and a Type I chebyshev filter of order 20 for the low pass filter.

\section{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
\label{sec:orgdb88b2c}
After synthesis, we obtain the complementary filters shown by the dashed curves which are of order 27.
The FIR filters of order 512 develop in the PhD thesis of Hua are also shown by the solid curves.
The filters are quite similar both in phase and in magnitude.

To summarize:
\begin{itemize}
\item the specifications in terms of super sensor noise and dynamic uncertainty can be expressed as upper bounds on the filter's norm
\item the \(\mathcal{H}_\infty\) synthesis that we developed allows to shape complementary filters quite easily. It works very well for both simple and complex shapes
\item It can be easily generalized to the synthesis of more that two complementary filters. You can check the paper where this is explained
\end{itemize}

If you are interested by this work, the paper and all the Matlab scripts that was used to obtain all these results are accessible in the link.
\end{document}

### 2019-09-26 tikz/figs/comp_fir_ligo_hinf.tex
Review - figures are modified

\setlength\fwidth{6.5cm}
\setlength\fheight{7cm}

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.60\fheight,
    at={(0.0\fwidth, 0.35\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,0.01,0.1,1},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.002,
    ymax=5,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend style={at={(1,0)}, outer sep=2pt, anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}}
    ]
    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addlegendentry{$H_H(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor1, dashed, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addlegendentry{$H_H(s)$ - FIR}
    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addlegendentry{$H_L(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor2, dashed, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addlegendentry{$H_L(s)$ - FIR}
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.3\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,  0.01,   0.1,     1},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-180,
    ymax=180,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addplot [color=mycolor2, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
  \end{axis}
\end{tikzpicture}

### 2019-09-26 tikz/figs/fusion_super_sensor.tex
Review - figures are modified

\begin{tikzpicture}
  \node[branch] (x) at (0, 0);
  \node[block, above right=0.5 and 0.5 of x](G1){$G_1(s)$};
  \node[block, below right=0.5 and 0.5 of x](G2){$G_2(s)$};
  \node[addb, right=0.8 of G1](add1){};
  \node[addb, right=0.8 of G2](add2){};
  \node[block, right=0.8 of add1](H1){$H_1(s)$};
  \node[block, right=0.8 of add2](H2){$H_2(s)$};
  \node[addb, right=5 of x](add){};

  \draw[] ($(x)+(-0.7, 0)$) node[above right]{$x$} -- (x.center);
  \draw[->] (x.center) |- (G1.west);
  \draw[->] (x.center) |- (G2.west);
  \draw[->] (G1.east) -- (add1.west);
  \draw[->] (G2.east) -- (add2.west);
  \draw[<-] (add1.north) -- ++(0, 0.8)node[below right](n1){$n_1$};
  \draw[<-] (add2.north) -- ++(0, 0.8)node[below right](n2){$n_2$};
  \draw[->] (add1.east) -- (H1.west);
  \draw[->] (add2.east) -- (H2.west);
  \draw[->] (H1) -| (add.north);
  \draw[->] (H2) -| (add.south);
  \draw[->] (add.east) -- ++(0.7, 0) node[above left]{$\hat{x}$};

  \begin{scope}[on background layer]
    \node[fit={($(G2.south-|x)+(-0.2, -0.3)$) ($(n1.north east-|add.east)+(0.2, 0.3)$)}, fill=black!10!white, draw, dashed, inner sep=0pt] (supersensor) {};
    \node[below left] at (supersensor.north east) {Super Sensor};

    \node[fit={($(G1.south west)+(-0.3, -0.1)$) ($(n1.north east)+(0.0, 0.1)$)}, fill=black!20!white, draw, dashed, inner sep=0pt] (sensor1) {};
    \node[below right] at (sensor1.north west) {Sensor 1};
    \node[fit={($(G2.south west)+(-0.3, -0.1)$) ($(n2.north east)+(0.0, 0.1)$)}, fill=black!20!white, draw, dashed, inner sep=0pt] (sensor2) {};
    \node[below right] at (sensor2.north west) {Sensor 2};
  \end{scope}
\end{tikzpicture}

### 2019-09-26 tikz/figs/hinf_synthesis_results.tex
Review - figures are modified

\setlength\fwidth{6.5cm}
\setlength\fheight{6cm}

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.5\fheight,
    at={(0.0\fwidth, 0.5\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};

    \addplot [color=mycolor2, line width=1.5pt, forget plot]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};

    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};

    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.45\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-200,
    ymax=200,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    legend style={at={(1,1.1)}, outer sep=2pt , anchor=north east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}},
    ]
    \addlegendimage{color=mycolor1, dashed, line width=1.5pt}
    \addlegendentry{$W_1^{-1}$};
    \addlegendimage{color=mycolor2, dashed, line width=1.5pt}
    \addlegendentry{$W_2^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
    \addlegendentry{$H_1$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
    \addlegendentry{$H_2$};
  \end{axis}
\end{tikzpicture}

### 2019-09-26 tikz/figs/hinf_three_synthesis_results.tex
Review - figures are modified

\setlength\fwidth{6.5cm}
\setlength\fheight{6cm}

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.55\fheight,
    at={(0.0\fwidth, 0.45\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=100,
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend columns=2,
    legend style={
      /tikz/column 2/.style={
        column sep=5pt,
      },
      at={(1,0)}, outer sep=2pt , anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}
    },
    ]
    \addplot [color=mycolor1, dashed, line width=1.5pt]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_1}^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_1$};

    \addplot [color=mycolor2, dashed, line width=1.5pt]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_2}^{-1}$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_2$};

    \addplot [color=mycolor3, dashed, line width=1.5pt]
    table [x=freqs, y=W3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_3}^{-1}$};
    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_3$};
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.4\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=100,
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-240,
    ymax=240,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    ]

    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};

    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};

    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
  \end{axis}
\end{tikzpicture}

### 2019-09-26 tikz/figs/ligo_weights.tex
Review - figures are modified

\setlength\fwidth{6.5cm}
\setlength\fheight{4cm}

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=1.0\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    separate axis lines,
    every outer x axis line/.append style={black},
    every x tick label/.append style={font=\color{black}},
    every x tick/.append style={black},
    xmode=log,
    xmin=0.001,
    xmax=1,
    xminorticks=true,
    xlabel={Frequency [Hz]},
    every outer y axis line/.append style={black},
    every y tick label/.append style={font=\color{black}},
    every y tick/.append style={black},
    ymode=log,
    ymin=0.005,
    ymax=20,
    yminorticks=true,
    ylabel={Magnitude},
    axis background/.style={fill=white},
    xmajorgrids,
    xminorgrids,
    ymajorgrids,
    yminorgrids,
    legend style={at={(0,1)}, outer sep=2pt, anchor=north west, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}}
    ]

    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=wHm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
    \addlegendentry{$|w_H|^{-1}$}

    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=wLm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
    \addlegendentry{$|w_L|^{-1}$}

    \addplot [color=black, dotted, line width=1.5pt]
    table[row sep=crcr]{%
      0.0005	0.008\\
      0.008   0.008\\
    };
    \addlegendentry{Specifications}

    \addplot [color=black, dotted, line width=1.5pt, forget plot]
    table[row sep=crcr]{%
      0.008	0.008\\
      0.04	1\\
    };
    \addplot [color=black, dotted, line width=1.5pt, forget plot]
    table[row sep=crcr]{%
      0.04  3\\
      0.1   3\\
    };
    \addplot [color=black, dotted, line width=1.5pt]
    table[row sep=crcr]{%
      0.1	0.045\\
      2   0.045\\
    };
  \end{axis}
\end{tikzpicture}

### 2019-09-26 tikz/figs/sensor_fusion_dynamic_uncertainty.tex
Review - figures are modified

\begin{tikzpicture}
  \node[branch] (x) at (0, 0);
  \node[addb, above right=0.8 and 4 of x](add1){};
  \node[addb, below right=0.8 and 4 of x](add2){};
  \node[block, above left=0.2 and 0.1 of add1](delta1){$\Delta_1(s)$};
  \node[block, above left=0.2 and 0.1 of add2](delta2){$\Delta_2(s)$};
  \node[block, left=0.5 of delta1](W1){$w_1(s)$};
  \node[block, left=0.5 of delta2](W2){$w_2(s)$};
  \node[block, right=0.5 of add1](H1){$H_1(s)$};
  \node[block, right=0.5 of add2](H2){$H_2(s)$};
  \node[addb, right=6 of x](add){};

  \draw[] ($(x)+(-0.7, 0)$) node[above right]{$x$} -- (x.center);
  \draw[->] (x.center) |- (add1.west);
  \draw[->] (x.center) |- (add2.west);
  \draw[->] ($(add1-|W1.west)+(-0.5, 0)$)node[branch](S1){} |- (W1.west);
  \draw[->] ($(add2-|W2.west)+(-0.5, 0)$)node[branch](S1){} |- (W2.west);
  \draw[->] (W1.east) -- (delta1.west);
  \draw[->] (W2.east) -- (delta2.west);
  \draw[->] (delta1.east) -| (add1.north);
  \draw[->] (delta2.east) -| (add2.north);
  \draw[->] (add1.east) -- (H1.west);
  \draw[->] (add2.east) -- (H2.west);
  \draw[->] (H1.east) -| (add.north);
  \draw[->] (H2.east) -| (add.south);
  \draw[->] (add.east) -- ++(0.7, 0) node[above left]{$\hat{x}$};

  \begin{scope}[on background layer]
    \node[block, fit={($(W1.north-|S1)+(-0.2, 0.2)$) ($(add1.south east)+(0.2, -0.3)$)}, fill=black!20!white, dashed, inner sep=0pt] (sensor1) {};
    \node[above right] at (sensor1.south west) {Sensor 1};
    \node[block, fit={($(W2.north-|S1)+(-0.2, 0.2)$) ($(add2.south east)+(0.2, -0.3)$)}, fill=black!20!white, dashed, inner sep=0pt] (sensor2) {};
    \node[above right] at (sensor2.south west) {Sensor 2};
  \end{scope}
\end{tikzpicture}

### 2019-09-26 tikz/figs/weight_formula.tex
Review - figures are modified

\setlength\fwidth{6.5cm}
\setlength\fheight{3.5cm}

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=1.0\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=100,
    xtick={0.1,1,10, 100},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xlabel={Frequency [Hz]},
    xminorgrids,
    yminorgrids,
    ]

    \addplot [color=black, line width=1.5pt, forget plot]
    table [x=freqs, y=ampl, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/weight_formula.csv};

    \addplot [color=black, dashed, line width=1.5pt]
    table[row sep=crcr]{%
      1     10\\
      100   10\\
    };
    \addplot [color=black, dashed, line width=1.5pt]
    table[row sep=crcr]{%
      0.1  0.001\\
      3    0.001\\
    };

    \addplot [color=black, line width=1.5pt]
    table[row sep=crcr]{%
      0.1  1\\
      100  1\\
    };

    \addplot [color=black, dashed, line width=1.5pt]
    table[row sep=crcr]{%
      10  2\\
      10  1\\
    };

    \node[below] at (2, 10) {$G_\infty$};
    \node[above] at (2, 0.001) {$G_0$};

    \node[branch] at (10, 2){};
    \draw[dashed, line cap=round] (7, 2) -- (20, 2) node[right]{$G_c$};
    \draw[dashed, line cap=round] (10, 2) -- (10, 1) node[below]{$\omega_c$};

    \node[right] at (3, 0.1) {$+n$};

  \end{axis}
\end{tikzpicture}

### 2019-09-26 matlab/matlab/comp_filters_ligo.m

@@ -405,7 +405,7 @@ T = table(freqs', ...
           abs(squeeze(freqresp(Hl, freqs, 'Hz'))), ...
           180/pi*angle(squeeze(freqresp(Hh, freqs, 'Hz'))), ...
           180/pi*angle(squeeze(freqresp(Hl, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'Hlm', 'Hhm', 'Hlp', 'Hhp'});
+          'VariableNames', {'freqs', 'Hhm', 'Hlm', 'Hhp', 'Hlp'});
 writetable(T, 'mat/comp_ligo_fir.csv');
 
 T = table(w', ...
@@ -413,5 +413,5 @@ T = table(w', ...
           abs(1-H), ...
           180/pi*angle(H), ...
           180/pi*angle(1-H), ...
-          'VariableNames', {'freqs', 'Hlm', 'Hhm', 'Hlp', 'Hhp'});
+          'VariableNames', {'freqs', 'Hhm', 'Hlm', 'Hhp', 'Hlp'});
 writetable(T, 'mat/comp_ligo_hinf.csv');

### 2019-09-26 matlab/matlab/h_inf_synthesis_complementary_filters.m

@@ -11,11 +11,11 @@ freqs = logspace(-1, 3, 1000);
 % A formula is proposed to help the design of the weighting functions.
 
 % \begin{equation}
-%   W(s) = \left(\frac{
-%            \hfill \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
+%   W(s) = \left( \frac{
+%            \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{G_0}{G_c}\right)^{\frac{1}{n}}
 %          }{
 %            \left(\frac{1}{G_\infty}\right)^{\frac{1}{n}} \frac{1}{\omega_0} \sqrt{\frac{1 - \left(\frac{G_0}{G_c}\right)^{\frac{2}{n}}}{1 - \left(\frac{G_c}{G_\infty}\right)^{\frac{2}{n}}}} s + \left(\frac{1}{G_c}\right)^{\frac{1}{n}}
-%          }}\right)^n
+%          }\right)^n
 % \end{equation}
 
 % The parameters permits to specify:

### 2019-09-26 matlab/matlab/three_comp_filters.m

@@ -36,7 +36,7 @@ T = table(freqs', ...
           1./abs(squeeze(freqresp(W1, freqs, 'Hz'))), ...
           1./abs(squeeze(freqresp(W2, freqs, 'Hz'))), ...
           1./abs(squeeze(freqresp(W3, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'w1', 'w2', 'w3'});
+          'VariableNames', {'freqs', 'W1', 'W2', 'W3'});
 writetable(T, 'mat/hinf_three_weights.csv');
 
 % H-Infinity Synthesis

### 2019-09-26 paper/paper.tex
One figure was missing the Frequency axis
Review - Change test about robustnesss

@@
-% Created 2019-08-20 mar. 16:57
+% Created 2019-09-26 jeu. 18:26
 % Intended LaTeX compiler: pdflatex
@@
 Email: {\tt\small thomas.dehaeze@esrf.fr}}}
-\date{2019-08-20}
+\date{2019-09-26}
 \title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis}
@@
  pdfsubject={},
- pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
+ pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
  pdflang={English}}
@@
 \section{Introduction}
-\label{sec:orgf075900}
+\label{sec:org239b4b4}
 \label{sec:introduction}
@@
 \section{Complementary Filters Requirements}
-\label{sec:orgcfd59fa}
+\label{sec:org35ebf13}
 \label{sec:requirements}
 \subsection{Sensor Fusion Architecture}
-\label{sec:orgc84edaa}
+\label{sec:org291a5d3}
 \label{sec:sensor_fusion}
 
-Let's consider two sensors measuring the same physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\), and with noise characteristics \(n_1\) and \(n_2\).
+Let's consider two sensors measuring the same physical quantity \(x\) with dynamics \(G_1(s)\) and \(G_2(s)\), and with uncorrelated noise characteristics \(n_1\) and \(n_2\).
 
@@
 \subsection{Noise Sensor Filtering}
-\label{sec:org3904fad}
+\label{sec:org9e972a6}
 \label{sec:noise_filtering}
@@
 
-The estimation error \(\delta x\) is defined by \eqref{eq:estimate_error}.
+Let's define the estimation error \(\delta x\) by \eqref{eq:estimate_error}.
 \begin{equation}
@@
 \subsection{Robustness of the Fusion}
-\label{sec:org1955823}
+\label{sec:org7c81675}
 \label{sec:fusion_robustness}
 
-In practical systems, the sensor dynamics always have some level of uncertainty and cannot be inverted perfectly such that \(G_i(s) = 1\).
+In practical systems the sensor dynamics is not perfect and \eqref{eq:perfect_dynamics} is not verified.
+In such case, one can use an inversion filter \(\hat{G}_i^{-1}(s)\) to normalize the sensor dynamics, where \(\hat{G}_i(s)\) is an estimate of the sensor dynamics \(G_i(s)\).
+However, as there is always some level of uncertainty on the dynamics, it cannot be perfectly inverted and \(\hat{G}_i^{-1}(s) G_i(s) \neq 1\).
 
-This can be represented as an input multiplicative uncertainty as shown in Fig.
+Let's represent the resulting dynamic uncertainty of the inverted sensors by an input multiplicative uncertainty as shown in Fig.
 \ref{fig:sensor_fusion_dynamic_uncertainty} where \(\Delta_i\) is any stable transfer function satisfying \(|\Delta_i(j\omega)| \le 1,\ \forall\omega\), and \(|w_i(s)|\) is a weight representing the magnitude of the uncertainty.
@@
 
-The super sensor dynamics \eqref{eq:super_sensor_dyn_uncertainty} is no longer equal to \(1\) and is now dependent on the sensor dynamics uncertainty weights \(w_i(s)\) as well as on the complementary filters \(H_i(s)\).
+The super sensor dynamics \eqref{eq:super_sensor_dyn_uncertainty} is no longer equal to \(1\) and now depends on the sensor dynamics uncertainty weights \(w_i(s)\) as well as on the complementary filters \(H_i(s)\).
 \begin{equation}
@@
 
-In order to limit the phase and gain uncertainty of the super sensor, one may want to design the complementary filters such that \eqref{eq:max_uncertainty_super_sensor} is satisfied.
-\begin{equation}
-\label{eq:max_uncertainty_super_sensor}
-  \begin{aligned}
-    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
-    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega
-  \end{aligned}
-\end{equation}
-
-Condition \eqref{eq:max_uncertainty_super_sensor} is equivalent to bounding the uncertainty set of the super sensor dynamics in the complex plane by a circle centered at \(1\) with a radius equal to \(\epsilon\) (Fig.
-\ref{fig:uncertainty_set_super_sensor}).
+The uncertainty region of the super sensor can be represented in the complex plane by a circle centered on \(1\) with a radius equal to \(|w_1(j\omega) H_1(j\omega)| + |w_2(j\omega) H_2(j\omega)|\) as shown in Fig.
+\ref{fig:uncertainty_set_super_sensor}.
 
@@
 \caption{\label{fig:uncertainty_set_super_sensor}
-Uncertainty set of the super sensor dynamics}
+Uncertainty region of the super sensor dynamics in the complex plane (solid circle).
+The contribution of both sensors 1 and 2 to the uncertainty are represented respectively by a dotted and a dashed circle}
 \end{figure}
 
-The maximum phase added by the super sensor uncertainty \(\Delta\phi\) is then
+The maximum phase added \(\Delta\phi(\omega)\) by the super sensor dynamics at frequency \(\omega\) is then
 \begin{equation}
 \label{eq:max_phase_uncertainty}
-    \Delta \phi = \arcsin\left( \epsilon \right)
+    \Delta\phi(\omega) = \arcsin\big( |w_1(j\omega) H_1(j\omega)| + |w_2(j\omega) H_2(j\omega)| \big)
 \end{equation}
 
-Limiting the phase added by the super sensor to \(\Delta \phi = \SI{30}{\degree}\) requires that \(H_1(s)\) and \(H_2(s)\) are designed such that \eqref{eq:max_uncertainty_super_sensor} is satisfied with \(\epsilon = \sin(\Delta\phi = \SI{30}{\degree}) = 0.5\).
-Thus the norm of the complementary filter \(|H_i|\) should be made small at frequencies where the dynamic uncertainty \(|w_i|\) of sensor \(i\) is large.
+As it is generally desired to limit the maximum phase added by the super sensor, \(H_1(s)\) and \(H_2(s)\) should be designed such that \eqref{eq:max_uncertainty_super_sensor} is satisfied.
+\begin{equation}
+\label{eq:max_uncertainty_super_sensor}
+   \max_\omega \big( \left|w_1 H_1\right| + \left|w_2 H_2\right|\big) < \sin\left( \Delta \phi_\text{max} \right)
+\end{equation}
+
+Thus the norm of the complementary filter \(|H_i|\) should be made small at frequencies where \(|w_i|\) is large.
 
 \section{Complementary Filters Shaping using \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:org8eb875c}
+\label{sec:org4512d61}
 \label{sec:hinf_method}
@@
 \subsection{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
-\label{sec:orga1b497a}
+\label{sec:org42885ea}
 \label{sec:hinf_synthesis}
@@
 \subsection{Weighting Functions Design}
-\label{sec:orgdf5910c}
+\label{sec:org6492bf4}
 \label{sec:hinf_weighting_func}
@@
 \subsection{Validation of the proposed synthesis method}
-\label{sec:org32ec287}
+\label{sec:org1650523}
 \label{sec:hinf_example}
@@
 \subsection{Synthesis of Three Complementary Filters}
-\label{sec:orgdfc880e}
+\label{sec:orga872169}
 \label{sec:hinf_three_comp_filters}
@@
 \section{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}
-\label{sec:org58b0928}
+\label{sec:org6b43181}
 \label{sec:application_ligo}
@@
 \subsection{Complementary Filters Specifications}
-\label{sec:org0bf5de3}
+\label{sec:orge7d0e23}
 \label{sec:ligo_specifications}
-The specifications for one pair of complementary filters used at the LIGO are summarized below (for further details, refer to \cite{hua04_polyp_fir_compl_filter_contr_system}):
+The specifications for one pair of complementary filters used at the LIGO are summarized below (for further details, refer to \cite{hua04_polyp_fir_compl_filter_contr_system}) and shown in Fig.
+\ref{fig:ligo_weights}:
 \begin{itemize}
@@
 
-The specifications are represented by the dashed lines in Fig. \ref{fig:ligo_weights}.
-
 \subsection{Weighting Functions Design}
-\label{sec:org0a19352}
+\label{sec:org03404b3}
 \label{sec:ligo_weights}
@@
 For the one corresponding to the high pass filter \(w_H(s)\), a \(7^{\text{th}}\) order transfer function is designed.
-The magnitudes of the weighting functions inverse are shown in Fig. \ref{fig:ligo_weights}.
+The magnitudes of the weighting functions are shown in Fig. \ref{fig:ligo_weights}.
 
@@
 \caption{\label{fig:ligo_weights}
-Specifications and weighting functions magnitude used for \(\mathcal{H}_\infty\) synthesis}
+Specifications and weighting functions magnitudes}
 \end{figure}
@@
 \subsection{\(\mathcal{H}_\infty\) Synthesis}
-\label{sec:orgf481d28}
+\label{sec:orgd133413}
 \label{sec:ligo_results}
@@
 \section{Conclusion}
-\label{sec:orgc26b54f}
+\label{sec:orgde38c04}
   \label{sec:conclusion}
@@
 \section{Acknowledgment}
-\label{sec:org698db58}
+\label{sec:org57822f5}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2019-10-01 presentation/notes.tex
Update presentation for LIGO

@@
-% Created 2019-08-28 mer. 16:01
+% Created 2019-10-01 mar. 09:57
 % Intended LaTeX compiler: pdflatex
@@
 \author{Dehaeze Thomas}
-\date{2019-08-28}
+\date{2019-10-01}
 \title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis\\\medskip
@@
  pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
- pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
+ pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
  pdflang={English}}
@@
 \section{Title Slide - Introduction}
-\label{sec:org2616a5c}
-Hi everyone,
+\label{sec:orgda5d0ad}
+Hello everyone,
 
@@
 \section{Sensor Fusion Architecture - Noise Filtering}
-\label{sec:org3776d94}
+\label{sec:org498fb95}
 A typical sensor fusion architecture is represented here where the signal of two sensors measuring the same quantity \(x\) are filtered out by two filters \(H_1\) and \(H_2\) and then combined to give a estimate \(\hat{x}\) of \(x\).
@@
 \section{Sensor Fusion Architecture - Robustness}
-\label{sec:org75a0990}
+\label{sec:org0b2c003}
 However, in practical systems, the sensor dynamics is never exactly known and cannot be perfectly inverted.
@@
 \section{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
-\label{sec:org4d70a51}
+\label{sec:org6d76257}
 The design objective is thus to design two complementary filters \(H_1\) and \(H_2\) such that the norms of \(H_1\) and \(H_2\) are below some defined weights \(W_1\) and \(W_2\).
@@
 \section{Validation of the proposed synthesis method}
-\label{sec:orgd012b55}
+\label{sec:org4885e1d}
 We then used this synthesis method to design complementary filters.
@@
 \section{Complementary Filters Used at LIGO - Specifications}
-\label{sec:orgc32f967}
+\label{sec:org2cb9d01}
 We then wanted to validate this synthesis method for the design of more complex complementary filters.
@@
 \section{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
-\label{sec:orgdb88b2c}
+\label{sec:org5ec32cc}
 After synthesis, we obtain the complementary filters shown by the dashed curves which are of order 27.

### 2019-10-01 presentation/presentation.tex
Update presentation for LIGO

@@
-% Created 2019-08-28 mer. 15:30
+% Created 2019-10-01 mar. 09:50
 % Intended LaTeX compiler: pdflatex
@@
 \usetheme{default}
-\author{Dehaeze Thomas}
-\date{2019-08-28}
+\author{Dehaeze Thomas \\ Collette Christophe \\ Vermat Mohit}
+\date{2019-10-02}
 \title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
@@
 \hypersetup{
- pdfauthor={Dehaeze Thomas},
+ pdfauthor={Dehaeze Thomas \\ Collette Christophe \\ Vermat Mohit},
  pdftitle={Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis},
@@
 \section{Complementary Filters Shaping}
-\label{sec:orgf40a445}
-\begin{frame}[label={sec:org644c6eb}]{Sensor Fusion Architecture - Noise Filtering}
+\label{sec:org15fdac4}
+\begin{frame}[label={sec:org236611f}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:orgaee2e4a}]{Sensor Fusion Architecture - Robustness}
+\begin{frame}[label={sec:orgb822dd6}]{Sensor Fusion Architecture - Robustness}
 \begin{columns}
@@
 
-\begin{frame}[label={sec:org1c42552}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:orge37165c}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:org493a937}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:org1f11fb1}]{Validation of the proposed synthesis method}
 \begin{center}
@@
 
-\begin{frame}[label={sec:orga95f64f}]{Complementary Filters Used at LIGO - Specifications}
+\begin{frame}[label={sec:org75dfd29}]{Complementary Filters Used at LIGO - Specifications}
 The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
@@
 
-\begin{frame}[label={sec:org3e0dbb2}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
+\begin{frame}[label={sec:org53aad0d}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
 \begin{columns}
@@
 \begin{center}
-\includegraphics[scale=1,width=1.1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
+\includegraphics[scale=1,width=1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
 \end{center}

### 2019-10-23 tikz/figs/comp_fir_ligo_hinf.tex
Update path to data

@@
     \addplot [color=mycolor1, line width=1.5pt]
-      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
+      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
     \addlegendentry{$H_H(s)$ - $\mathcal{H}_\infty$}
     \addplot [color=mycolor1, dashed, line width=1.5pt]
-      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
+      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
     \addlegendentry{$H_H(s)$ - FIR}
     \addplot [color=mycolor2, line width=1.5pt]
-      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
+      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
     \addlegendentry{$H_L(s)$ - $\mathcal{H}_\infty$}
     \addplot [color=mycolor2, dashed, line width=1.5pt]
-      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
+      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
     \addlegendentry{$H_L(s)$ - FIR}
@@
     \addplot [color=mycolor1, line width=1.5pt, forget plot]
-      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
+      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
     \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
-      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
+      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
     \addplot [color=mycolor2, line width=1.5pt, forget plot]
-      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
+      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
     \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
-      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
+      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
   \end{axis}

### 2019-10-23 tikz/figs/hinf_synthesis_results.tex
Update path to data

@@
     \addplot [color=mycolor1, line width=1.5pt, forget plot]
-    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
+    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
 
     \addplot [color=mycolor2, line width=1.5pt, forget plot]
-    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
+    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
 
     \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
-    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};
+    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_weights.csv};
 
     \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
-    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};
+    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_weights.csv};
   \end{axis}
@@
     \addplot [color=mycolor1, line width=1.5pt]
-    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
+    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
     \addlegendentry{$H_1$};
     \addplot [color=mycolor2, line width=1.5pt]
-    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
+    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
     \addlegendentry{$H_2$};

### 2019-10-23 tikz/figs/hinf_three_synthesis_results.tex
Update path to data

@@
     \addplot [color=mycolor1, dashed, line width=1.5pt]
-    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
+    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
     \addlegendentry{${W_1}^{-1}$};
     \addplot [color=mycolor1, line width=1.5pt]
-    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
     \addlegendentry{$H_1$};
@@
     \addplot [color=mycolor2, dashed, line width=1.5pt]
-    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
+    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
     \addlegendentry{${W_2}^{-1}$};
     \addplot [color=mycolor2, line width=1.5pt]
-    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
     \addlegendentry{$H_2$};
@@
     \addplot [color=mycolor3, dashed, line width=1.5pt]
-    table [x=freqs, y=W3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
+    table [x=freqs, y=W3, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
     \addlegendentry{${W_3}^{-1}$};
     \addplot [color=mycolor3, line width=1.5pt]
-    table [x=freqs, y=H3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H3, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
     \addlegendentry{$H_3$};
@@
     \addplot [color=mycolor1, line width=1.5pt]
-    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
 
     \addplot [color=mycolor2, line width=1.5pt]
-    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
 
     \addplot [color=mycolor3, line width=1.5pt]
-    table [x=freqs, y=H3p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
+    table [x=freqs, y=H3p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
   \end{axis}

### 2019-10-23 tikz/figs/ligo_weights.tex
Update path to data

@@
     \addplot [color=mycolor1, line width=1.5pt]
-      table [x=freqs, y=wHm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
+      table [x=freqs, y=wHm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matligo_weights.csv};
     \addlegendentry{$|w_H|^{-1}$}
@@
     \addplot [color=mycolor2, line width=1.5pt]
-      table [x=freqs, y=wLm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
+      table [x=freqs, y=wLm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matligo_weights.csv};
     \addlegendentry{$|w_L|^{-1}$}

### 2019-10-23 tikz/figs/weight_formula.tex
Update path to data

@@
     \addplot [color=black, line width=1.5pt, forget plot]
-    table [x=freqs, y=ampl, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/weight_formula.csv};
+    table [x=freqs, y=ampl, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matweight_formula.csv};
 

### 2019-10-29 poster/architecture.tex
Update poster

Let's consider two sensors measuring the same physical quantity \(x\) with
dynamics \(G_1(s)\) and \(G_2(s)\), and with uncorrelated noise characteristics
\(n_1\) and \(n_2\).\newline

The signals from both sensors are fed into two \textbf{complementary filters} \(H_1(s)\)
and \(H_2(s)\) and then combined to yield an estimate \(\hat{x}\) of \(x\) as
shown in Fig.~\ref{fig:fusion_super_sensor}.

\begin{equation*}
  \hat{x} = \left(G_1 H_1 + G_2 H_2\right) x + H_1 n_1 + H_2 n_2
\end{equation*}

The complementary property of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies:
\begin{equation*}
  \tcmbox{H_1(s) + H_2(s) = 1}
\end{equation*}

The combined sensors forms a so called \textbf{super sensor}.
Let's determine the noise property and dynamical uncertainty of such super
sensor.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "poster"
%%% End:

### 2019-10-29 poster/poster.tex
Update poster

@@
 \documentclass[%
-    a0paper,%
-    20pt,%
+    a1paper,%
+    17pt,%
     portait,%
     margin=0mm,%
-    innermargin=10mm,%
-    blockverticalspace=10mm,%
-    colspace=10mm,%
-    subcolspace=5mm%
+    innermargin=5mm,%
+    blockverticalspace=5mm,%
+    colspace=5mm,%
+    subcolspace=2mm%
 ]{tikzposter}
+
+\usetitlestyle[]{Wave}
 
@@
 
-\author{Dehaeze Thomas, Verma Mohit and Collette Christophe}
+\author[1,2]{Dehaeze Thomas}
+\author[1,3]{Verma Mohit}
+\author[1,3]{Collette Christophe}
+\affil[1]{Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium}
+\affil[2]{European Synchrotron Radiation Facility, Grenoble, France}
+\affil[3]{BEAMS Department, Free University of Brussels, Belgium}
+
 \date{2019-11-06}
-\title{Complementary Filters Shaping Using \scalebox{2}{$\mathcal{H}_\infty$} Synthesis}
+\title{Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis}
 \institute{}
@@
     linewidth=2mm,
-    innersep=10mm,
+    innersep=5mm,
     titletotopverticalspace=10mm,
@@
 \column{0.5}
-\block[]{Introduction}{\input{introduction.tex}}
+% \block[]{Introduction}{\input{introduction.tex}}
+\block[]{Sensor Fusion Architecture}{\input{architecture.tex}}
 \block[]{Complementary Filters Requirements}{\input{requirements.tex}}

### 2019-10-29 poster/requirements.tex
Update poster

@@
+%%% Local Variables:
+%%% TeX-master: "poster"
+%%% End:
+
+\begin{minipage}[t]{0.5\linewidth}
+  \begin{center}
+    {\Large \textbf{Noise Property}}
+  \end{center}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.5\linewidth}
+  \begin{center}
+    {\Large \textbf{Dynamical Uncertainty}}
+  \end{center}
+\end{minipage}\hfill
+
+\hspace*{-10pt}\begin{minipage}[t]{0.49\linewidth}
   \begin{tikzfigure}[Sensor fusion architecture]
+    \centering
     \label{fig:fusion_super_sensor}
-  \centering
-  \includegraphics[scale=1.8]{figs/fusion_super_sensor.pdf}
+    \includegraphics[height=6cm]{figs/fusion_super_sensor.pdf}
   \end{tikzfigure}
 
-\begin{tikzfigure}[Sensor fusion architecture with sensor dynamics uncertainty]
+  First suppose \textbf{known sensor dynamics}, such that the dynamics can be
+  inverted:
+  \[ G_1(s) = G_2(s) = 1 \]
+
+  The estimate $\hat{x}$ is then:
+  \[ \tcmbox{\hat{x} = x + H_1 n_1 + H_2 n_2} \]
+
+  The signal $x$ is kept \textbf{undistorted} while the noises $n_1$ and $n_2$ are \textbf{filtered out by the complementary filters}.\newline
+
+  Estimate error $\delta x$:
+  \[ \delta x \triangleq \hat{x} - x = H_1 n_1 + H_2 n_2 \]
+
+  PSD of the super sensor noise:
+  \[ \tcmbox{\Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} +
+      \left|H_2\right|^2 \Phi_{n_2}} \]
+\end{minipage}\hspace{20pt}
+\begin{minipage}[t]{0.49\linewidth}
+  \begin{tikzfigure}[Fusion of sensors with dynamics uncertainty]
+    \centering
     \label{fig:sensor_fusion_dynamic_uncertainty}
-  \centering
-  \includegraphics[scale=1.8]{figs/sensor_fusion_dynamic_uncertainty.pdf}
+    \includegraphics[height=6cm]{figs/sensor_fusion_dynamic_uncertainty.pdf}
   \end{tikzfigure}
+
+  Sensor dynamic uncertainty is represented by \textbf{multiplicative input uncertainty}:
+  \[ \begin{aligned}
+      G_i^\prime(s) = G_i(s) [1 + & w_i(s)\Delta_i(s)], \\
+      &\forall\Delta_i, \|\Delta_i\|_\infty < 1
+    \end{aligned} \]
+
+  The super sensor dynamics is:
+  \[ \tcmbox{\frac{\hat{x}}{x} = 1 + w_1 H_1 \Delta_1 + w_2 H_2 \Delta_2} \]
+
+  The super sensor dynamic uncertainty is represented in the complex plane in
+  Fig.~\ref{fig:uncertainty_set_super_sensor}.
 
@@
     \centering
-  \includegraphics[scale=1.8]{figs/uncertainty_set_super_sensor.pdf}
+    \includegraphics[width=0.8\linewidth]{figs/uncertainty_set_super_sensor.pdf}
   \end{tikzfigure}
+\end{minipage}
+\vspace{1em}
+\sepline
+
+As shown in the analysis above, \textbf{the performance and robustness of the sensor fusion architecture depends on the complementary filters norms}.
+Therefore, the development of a synthesis method of complementary filters that allows the shaping of their norm is necessary.

### 2019-10-30 poster/ligo.tex
Update poster
Reworked the minipage setup
Poster: Update part about H-infinity synthesis

@@
-\textbf{Control Configuration}
+%%% Local Variables:
+%%% TeX-master: "poster"
+%%% End:
+
+The specifications for one pair of complementary filters used at the LIGO are
+detailed in \cite{hua04_polyp_fir_compl_filter_contr_system} and shown in the
+frequency domain in Fig.~\ref{fig:ligo_weights}.
 
@@
     \centering
-    \includegraphics[scale=1.8]{figs/ligo_weights.pdf}
+    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
   \end{tikzfigure}
@@
     \centering
-    \includegraphics[scale=1.8]{figs/comp_fir_ligo_hinf.pdf}
+    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
   \end{tikzfigure}

### 2019-10-30 poster/conclusion.tex
Update poster
Poster: Worked on the ligo part

@@
-This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
-Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
-Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
-Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.
+%%% Local Variables:
+%%% TeX-master: "poster"
+%%% End:
+
+Complementary filters can be used to \textbf{combine multiple sensors} in order
+to obtain a \textbf{super sensor}.
+Specification on the \textbf{super sensor noise} and on the \textbf{robustness
+  of the sensor fusion} are linked to the \textbf{norm of the complementary filters}.
+A synthesis method that permits the \textbf{shaping of the complementary filters
+  norms} has been proposed and has been successfully applied for the design of
+complex filters.

### 2019-10-30 poster/ligo.tex
Poster: Worked on the ligo part

@@
 
-The specifications for one pair of complementary filters used at the LIGO are
-detailed in \cite{hua04_polyp_fir_compl_filter_contr_system} and shown in the
-frequency domain in Fig.~\ref{fig:ligo_weights}.
+The effectiveness of the proposed method is demonstrated by designing a
+complementary filter pair that is used in the active isolation system at the LIGO
+\cite{hua05_low_ligo}.
+The requirements are very tight (shown by dashed upper bounds
+in Fig.~\ref{fig:ligo_weights}) and thus their design is complex.
 
-\begin{minipage}[t]{0.49\linewidth}
-  \begin{tikzfigure}[Specifications and weighting functions magnitude used for $\mathcal{H}_\infty$ synthesis]
+\bigskip
+
+\begin{minipage}[t]{0.48\linewidth}
+  The weights are designed such that their inverse magnitude is as
+  close as possible to the specifications while being of reasonably \textbf{small order}
+  (Fig.~\ref{fig:ligo_weights}).
+  After synthesis, the obtained complementary filters are
+  compared with the FIR filters \cite{hua05_low_ligo} and are found
+  to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).
+  \begin{tikzfigure}[Specifications and weights used for the $\mathcal{H}_\infty$ synthesis]
     \label{fig:ligo_weights}
@@
 \end{minipage}\hfill
-\begin{minipage}[t]{0.49\linewidth}
-  \begin{tikzfigure}[Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with $\mathcal{H}_\infty$ synthesis (dashed)]
+\begin{minipage}[t]{0.5\linewidth}
+  \begin{tikzfigure}[Comparison of the FIR filters designed
+    in \cite{hua05_low_ligo} (order 512) with the filters obtained with $\mathcal{H}_\infty$
+    synthesis (order 28)]
     \label{fig:comp_fir_ligo_hinf}

### 2019-10-30 poster/architecture.tex
Poster: Update part about H-infinity synthesis
Reworked "sensor fusion architecture": makes to section smaller

@@
-Let's consider two sensors measuring the same physical quantity \(x\) with
+Let's consider \textbf{two sensors} measuring the same physical quantity \(x\) with
 dynamics \(G_1(s)\) and \(G_2(s)\), and with uncorrelated noise characteristics
-\(n_1\) and \(n_2\).\newline
+\(n_1\) and \(n_2\).
+
+\bigskip
 
 The signals from both sensors are fed into two \textbf{complementary filters} \(H_1(s)\)
-and \(H_2(s)\) and then combined to yield an estimate \(\hat{x}\) of \(x\) as
-shown in Fig.~\ref{fig:fusion_super_sensor}.
-
+and \(H_2(s)\) and then combined to form a \textbf{super sensor} that yield an estimate \(\hat{x}\) of \(x\) (Fig.~\ref{fig:fusion_super_sensor}).
 \begin{equation*}
@@
 
-The complementary property of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies:
+\begin{minipage}[t]{0.69\linewidth}
+  The \textbf{complementary property} of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies:
+\end{minipage}\hfill
+\begin{minipage}[t]{0.29\linewidth}
+  \vspace{-2em}
   \begin{equation*}
@@
   \end{equation*}
-
-The combined sensors forms a so called \textbf{super sensor}.
-Let's determine the noise property and dynamical uncertainty of such super
-sensor.
+\end{minipage}
 

### 2019-10-30 poster/requirements.tex
Reworked the minipage setup
Poster: Update part about H-infinity synthesis
Poster: Reworked requirement section

@@
 
-\hspace*{-10pt}\begin{minipage}[t]{0.49\linewidth}
+\begin{minipage}[t]{0.47\linewidth}
   \begin{tikzfigure}[Sensor fusion architecture]
@@
 
-  First suppose \textbf{known sensor dynamics}, such that the dynamics can be
+  First suppose \textbf{perfectly known sensor dynamics} such that is can be
   inverted:
@@
 
-  The signal $x$ is kept \textbf{undistorted} while the noises $n_1$ and $n_2$ are \textbf{filtered out by the complementary filters}.\newline
+  The signal $x$ is kept \textbf{undistorted} while the noises $n_1$ and $n_2$
+  are \textbf{filtered out by the complementary filters}.
 
-  Estimate error $\delta x$:
+  \bigskip
+
+  The estimate error $\delta x$ is:
   \[ \delta x \triangleq \hat{x} - x = H_1 n_1 + H_2 n_2 \]
 
-  PSD of the super sensor noise:
+  The PSD of the super sensor noise depends on the \textbf{norm} of the
+  complementary filters:
   \[ \tcmbox{\Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} +
       \left|H_2\right|^2 \Phi_{n_2}} \]
-\end{minipage}\hspace{20pt}
-\begin{minipage}[t]{0.49\linewidth}
+\end{minipage}\hfill
+\begin{minipage}[t]{0.47\linewidth}
   \begin{tikzfigure}[Fusion of sensors with dynamics uncertainty]
@@
 
-  Sensor dynamic uncertainty is represented by \textbf{multiplicative input uncertainty}:
+  Let's represent sensor dynamic uncertainty by \textbf{multiplicative input uncertainty}:
   \[ \begin{aligned}
@@
 
-  The super sensor dynamics is:
+  The dynamics of the super sensor is:
   \[ \tcmbox{\frac{\hat{x}}{x} = 1 + w_1 H_1 \Delta_1 + w_2 H_2 \Delta_2} \]
 
-  The super sensor dynamic uncertainty is represented in the complex plane in
-  Fig.~\ref{fig:uncertainty_set_super_sensor}.
+  The obtained dynamic uncertainty depends on the \textbf{norm} of the filters (Fig.~\ref{fig:uncertainty_set_super_sensor}).
 
@@
 \sepline
+\vspace{1em}
 

### 2019-10-30 poster/conclusion.tex
Everything is aligned

@@
 to obtain a \textbf{super sensor}.
-Specification on the \textbf{super sensor noise} and on the \textbf{robustness
+Specification on the super sensor \textbf{noise} and on the \textbf{robustness
   of the sensor fusion} are linked to the \textbf{norm of the complementary filters}.
@@
 complex filters.
+\vspace{0.5em}

### 2019-10-30 poster/ligo.tex
Everything is aligned

@@
   (Fig.~\ref{fig:ligo_weights}).
-  After synthesis, the obtained complementary filters are
-  compared with the FIR filters \cite{hua05_low_ligo} and are found
-  to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).
-  \begin{tikzfigure}[Specifications and weights used for the $\mathcal{H}_\infty$ synthesis]
+
+  \begin{tikzfigure}[Specifications and weights used for the
+    $\mathcal{H}_\infty$ synthesis]
     \label{fig:ligo_weights}
@@
   \end{tikzfigure}
+  \vspace{-0.8em}
+  \begin{tabular}{ll}
+    \(\tikz[baseline=-0.5ex]{\draw[color=mycolor1, line width=1.5pt](0,0)--(1,0)}\) & {\small Custom designed \(7^{\text{th}}\) Order Transfer Function}\\
+    \(\tikz[baseline=-0.5ex]{\draw[color=mycolor2, line width=1.5pt](0,0)--(1,0)}\) & {\small Type I Chebyshev Filter (Order \(20\))}\\
+  \end{tabular}
 \end{minipage}\hfill
 \begin{minipage}[t]{0.5\linewidth}
+  \vspace{-1.0em}
   \begin{tikzfigure}[Comparison of the FIR filters designed
     in \cite{hua05_low_ligo} (order 512) with the filters obtained with $\mathcal{H}_\infty$
-    synthesis (order 28)]
+    synthesis (order 27)]
     \label{fig:comp_fir_ligo_hinf}
@@
 \end{minipage}
+
+\bigskip
+
+After synthesis, the obtained complementary filters are
+compared with the FIR filters \cite{hua05_low_ligo} and are found
+to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).

### 2019-10-30 poster/architecture.tex
Poster Finished

@@
 \begin{minipage}[t]{0.69\linewidth}
-  The \textbf{complementary property} of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies:
+  The \textbf{complementary property} of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies.
 \end{minipage}\hfill

### 2019-10-30 poster/requirements.tex
Add acknoledgments separate from reference. Work on Introduction
Poster Finished

@@
 
-  First suppose \textbf{perfectly known sensor dynamics} such that is can be
+  First suppose \textbf{perfectly known sensor dynamics} such that it can be
   inverted:
@@
 
-  The PSD of the super sensor noise depends on the \textbf{norm} of the
+  The PSD of the super sensor \textbf{noise} depends on the \textbf{norm} of the
   complementary filters:
@@
 
-  The obtained dynamic uncertainty depends on the \textbf{norm} of the filters (Fig.~\ref{fig:uncertainty_set_super_sensor}).
+  The obtained \textbf{dynamic uncertainty} depends on the \textbf{norm} of the filters (Fig.~\ref{fig:uncertainty_set_super_sensor}).
 
@@
 \end{minipage}
-\vspace{1em}
+
+\bigskip
 \sepline
-\vspace{1em}
+\bigskip
 

### 2019-11-04 paper/paper.tex
Modified the bibtex file
Add one sentence in the paper
Add keywords to paper
[Final Submission] Change the class to IEEEtran / change the authors

@@
-% Created 2019-09-26 jeu. 18:26
+% Created 2019-10-31 jeu. 09:48
 % Intended LaTeX compiler: pdflatex
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
+\documentclass[conference]{IEEEtran}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{siunitx}
-\usepackage{amsmath,amssymb,amsfonts, cases}
-\usepackage[noadjust,space,compress]{cite}
+\IEEEoverridecommandlockouts
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{cases}
 \usepackage{tabularx,siunitx,booktabs}
-\usepackage{algorithmic, graphicx, textcomp}
-\usepackage{xcolor, import, hyperref}
-\usepackage[USenglish, english]{babel}
-\setcounter{footnote}{1}
+\usepackage{algorithmic}
+\usepackage{import, hyperref}
 \renewcommand{\citedash}{--}
-\IEEEoverridecommandlockouts
-\author{Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} BEAMS Department, Free University of Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Corresponding Author.
-Email: {\tt\small thomas.dehaeze@esrf.fr}}}
-\date{2019-09-26}
-\title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis}
-\hypersetup{
- pdfauthor={Dehaeze Thomas\textsuperscript{1,2,$\dagger$}, Verma Mohit\textsuperscript{1,3} and Collette Christophe\textsuperscript{1,3}  \thanks{\textsuperscript{1} Precision Mechatronics Laboratory, A\&M Department, University of Liege, Belgium} \thanks{\textsuperscript{2} European Synchrotron Radiation Facility, Grenoble, France} \thanks{\textsuperscript{3} BEAMS Department, Free University of Brussels, Belgium} \thanks{\textsuperscript{$\dagger$} Corresponding Author.
-Email: {\tt\small thomas.dehaeze@esrf.fr}}},
- pdftitle={Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis},
- pdfkeywords={},
- pdfsubject={},
- pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
- pdflang={English}}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\author{\IEEEauthorblockN{Dehaeze Thomas} \IEEEauthorblockA{\textit{European Synchrotron Radiation Facility} \\ Grenoble, France\\ \textit{Precision Mechatronics Laboratory} \\ \textit{University of Liege}, Belgium \\ thomas.dehaeze@esrf.fr }\and \IEEEauthorblockN{Verma Mohit} \IEEEauthorblockA{\textit{BEAMS Department}\\ \textit{Free University of Brussels}, Belgium\\ \textit{Precision Mechatronics Laboratory} \\ \textit{University of Liege}, Belgium \\ mohit.verma@ulb.ac.be }\and \IEEEauthorblockN{Collette Christophe} \IEEEauthorblockA{\textit{BEAMS Department}\\ \textit{Free University of Brussels}, Belgium\\ \textit{Precision Mechatronics Laboratory} \\ \textit{University of Liege}, Belgium \\ ccollett@ulb.ac.be }}
+\date{2019-10-31}
+\title{Complementary Filters Shaping \\ Using \(\mathcal{H}_\infty\) Synthesis \thanks{This work is funded by the FNRS.}}
 \begin{document}
@@
 \maketitle
+
 \bibliographystyle{IEEEtran}
@@
 
+\begin{IEEEkeywords}
+Complementary Filters, Sensor Fusion, H-Infinity Synthesis
+\end{IEEEkeywords}
+
 \section{Introduction}
-\label{sec:org239b4b4}
+\label{sec:org88c7d86}
 \label{sec:introduction}
@@
 \section{Complementary Filters Requirements}
-\label{sec:org35ebf13}
+\label{sec:org41613b0}
 \label{sec:requirements}
 \subsection{Sensor Fusion Architecture}
-\label{sec:org291a5d3}
+\label{sec:org3da9043}
 \label{sec:sensor_fusion}
@@
 \subsection{Noise Sensor Filtering}
-\label{sec:org9e972a6}
+\label{sec:org76c0d7c}
 \label{sec:noise_filtering}
@@
 \subsection{Robustness of the Fusion}
-\label{sec:org7c81675}
+\label{sec:org60ae644}
 \label{sec:fusion_robustness}
@@
 \end{equation}
+where \(\Delta \phi_\text{max}\) is the maximum allowed added phase.
 
@@
 \section{Complementary Filters Shaping using \(\mathcal{H}_\infty\) Synthesis}
-\label{sec:org4512d61}
+\label{sec:orgcafbd82}
 \label{sec:hinf_method}
@@
 \subsection{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
-\label{sec:org42885ea}
+\label{sec:orga863dd2}
 \label{sec:hinf_synthesis}
@@
 \subsection{Weighting Functions Design}
-\label{sec:org6492bf4}
+\label{sec:orgfe75ec2}
 \label{sec:hinf_weighting_func}
@@
 \subsection{Validation of the proposed synthesis method}
-\label{sec:org1650523}
+\label{sec:org0bf5120}
 \label{sec:hinf_example}
@@
 \subsection{Synthesis of Three Complementary Filters}
-\label{sec:orga872169}
+\label{sec:org9751f7b}
 \label{sec:hinf_three_comp_filters}
@@
 \section{Application: Design of Complementary Filters used in the Active Vibration Isolation System at the LIGO}
-\label{sec:org6b43181}
+\label{sec:orgc2ed648}
 \label{sec:application_ligo}
@@
 \subsection{Complementary Filters Specifications}
-\label{sec:orge7d0e23}
+\label{sec:orgfeebf2a}
 \label{sec:ligo_specifications}
@@
 \subsection{Weighting Functions Design}
-\label{sec:org03404b3}
+\label{sec:orgd9046dc}
 \label{sec:ligo_weights}
@@
 \subsection{\(\mathcal{H}_\infty\) Synthesis}
-\label{sec:orgd133413}
+\label{sec:org58dd9fc}
 \label{sec:ligo_results}
@@
 \section{Conclusion}
-\label{sec:orgde38c04}
+\label{sec:orgf6bb6aa}
 \label{sec:conclusion}
@@
 
-\section{Acknowledgment}
-\label{sec:org57822f5}
+\section*{Acknowledgment}
+\label{sec:org74249bf}
 This research benefited from a FRIA grant from the French Community of Belgium.

### 2019-11-05 tikz/config.tex
Review - figures are modified
Remove Useless Tikz setting

@@
 
-\definecolor{colorblack}{rgb}{0, 0, 0}
-\definecolor{colorblue}{rgb}{0, 0.4470, 0.7410}
-\definecolor{colorred}{rgb}{0.8500, 0.3250, 0.0980}
-\definecolor{coloryellow}{rgb}{0.9290, 0.6940, 0.1250}
-\definecolor{colorpurple}{rgb}{0.4940, 0.1840, 0.5560}
-\definecolor{colorgreen}{rgb}{0.4660, 0.6740, 0.1880}
-\definecolor{colorcyan}{rgb}{0.3010, 0.7450, 0.9330}
-\definecolor{colorbordeau}{rgb}{0.6350, 0.0780, 0.1840}
-
-% Main color
-\definecolor{maincolor}{RGB}{89, 9, 38}
-\definecolor{secondcolor}{RGB}{20, 9, 89}
+\definecolor{mycolor1}{RGB}{79,115,193}
+\definecolor{mycolor2}{RGB}{213,91,53}
+\definecolor{mycolor3}{RGB}{152,126,49}
 
@@
 
-\pgfplotsset{upperbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=60}}]
-\pgfplotsset{lowerbound}=[line cap=round, postaction={decorate,draw,decoration={border, segment length=0.2cm, amplitude=0.3cm, angle=-60}}]
-
-\pgfplotsset{
-  /pgfplots/upperbound/.style 1 args={
-    legend image code/.code={
-      \draw[##1, upperbound]
-        plot coordinates {
-        (0cm,0cm)
-        (0.6cm,0cm)
-      }
-    }
-  }
-}
-
 \pgfplotsset{%
@@
 
-\newcommand{\AxisRotator}[1][rotate=0]{%
-  \tikz [x=0.1cm,y=0.30cm,-stealth,#1] \draw (0,0) arc (-150:150:1 and 1);%
-}
-
 \tikzstyle{cross}=[path picture={
@@
 }
+
+\tikzset{block/.default={0.8cm}{0.8cm}}
+\tikzset{addb/.append style={scale=0.7}}
+\tikzset{node distance=0.6}

### 2019-11-05 talk/presentation.tex
Add ICCMA2019 talk slides

--- 2019-08-28 presentation/presentation.tex
@@
-% Created 2019-08-28 mer. 13:50
+% Created 2019-11-05 mar. 17:28
 % Intended LaTeX compiler: pdflatex
@@
 \usefonttheme[onlymath]{serif}
-\definecolor{mycolor1}{RGB}{79,115,193}
-\definecolor{mycolor2}{RGB}{213,91,53}
 \usetheme{default}
-\author{Dehaeze Thomas}
-\date{2019-08-28}
+\author{Dehaeze Thomas\textsuperscript{$\dagger$} \\ Vermat Mohit \\ Collette Christophe \\ \vspace{1cm} 08-11-2019 \\ \vspace{1cm} \textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}
+\date{}
 \title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
-\subtitle{Control System Working Group meeting}
-\hypersetup{colorlinks=true}
-\hypersetup{
- pdfauthor={Dehaeze Thomas},
- pdftitle={Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis},
- pdfkeywords={complementary filters, h-infinity, sensor fusion},
- pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
- pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
- pdflang={English}}
+\subtitle{ICCMA 2019}
 \begin{document}
@@
 
-\section{Complementary Filters Shaping}
-\label{sec:orgeac405f}
-\begin{frame}[label={sec:org7acc6c9}]{Sensor Fusion Architecture - Noise Filtering}
+\begin{frame}[label={sec:org3efdf18}]{Sensor Fusion}
+In order to improve the estimate \(\hat{x}\) of \(x\), multiple sensors can be merged together using complementary filters.
+
+This permits to have
+
+High bandwidth
+\begin{itemize}
+\item need of Sensor at low frequency + sensor at high frequency
+\item need of merging the two
+\item complementary filters
+\item design of those filters using \(\mathcal{H}_\infty\)
+\end{itemize}
+
+Goal:
+\begin{itemize}
+\item Higher control bandwidth
+\item Better estimation of some physical value
+\end{itemize}
+
+Applications:
+\begin{itemize}
+\item LIGO - Vibration isolation of precise equipment
+\item UAV - Angle estimation using Accelerometer and Gyroscope
+\end{itemize}
+\end{frame}
+
+\begin{frame}[label={sec:org132896d}]{Sensor Fusion Architecture - Noise Filtering}
 \vspace{-1em}
@@
 \begin{equation*}
-  G_1(s) = G_2(s) = 1 \Longrightarrow \hat{x} = x + H_1 n_1 + H_2 n_2
+  G_1(s) = G_2(s) = 1 \Longrightarrow \tcmbox{\hat{x} = x + H_1 n_1 + H_2 n_2}
 \end{equation*}
@@
 
-\begin{frame}[label={sec:orgc2c6d2b}]{Sensor Fusion Architecture - Robustness}
-\begin{columns}
-\begin{column}{0.5\columnwidth}
-\vspace{-2em}
-\begin{center}
-\includegraphics[scale=1,width=1.1\linewidth]{figs/sensor_fusion_dynamic_uncertainty.pdf}
-\end{center}
-\end{column}
-
-\begin{column}{0.5\columnwidth}
-\textbf{Dynamic Uncertainty}:
-\begin{gather*}
-  G_i^\prime(s) = G_i(s) [1 + w_i(s)\Delta_i(s)],\\
-  \quad \forall\Delta_i, \|\Delta_i\|_\infty < 1
-\end{gather*}
-
-\textbf{Super Sensor Dynamics}:
-\begin{equation*}
-  \frac{\hat{x}}{x} = 1 + w_1 H_1 \Delta_1 + w_2 H_2 \Delta_2
-\end{equation*}
-\end{column}
-\end{columns}
-
-\vspace{0.5em}
-\onslide{\begin{cbox}[Limit the Super Sensor Dynamic uncertainty]{blue}{}
-Design \(H_1(s)\) and \(H_2(s)\) such that:
-\begin{equation*}
-  \begin{aligned}
-                    & \left|w_1 H_1 \Delta_1\right| + \left|w_2 H_2 \Delta_2\right| \le \epsilon \quad \forall\omega,\ \forall \Delta_1, \forall \Delta_2\\
-    \Leftrightarrow & \left|w_1 H_1\right| + \left|w_2 H_2\right| \le \epsilon \quad \forall\omega \\
-    \Longrightarrow & \text{ depends on the filters' norm} \\
-  \end{aligned}
-\end{equation*}
-\end{cbox}}\vspace{0.5em}
-\end{frame}
-
-\begin{frame}[label={sec:orgf43ebc6}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:orgcb2d144}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\begin{frame}[label={sec:org65cb237}]{Validation of the proposed synthesis method}
-\begin{center}
-\includegraphics[scale=1,width=0.85\linewidth]{figs/hinf_synthesis_results.pdf}
-\end{center}
+\begin{frame}[label={sec:orgff066bd}]{Validation of the proposed synthesis method}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
+\caption{\label{fig:hinf_synthesis_results}
+Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
+\end{figure}
 \end{frame}
 
-\begin{frame}[label={sec:org8b0df25}]{Complementary Filters Used at LIGO - Specifications}
-The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}
-
-\begin{center}
-\includegraphics[scale=1,width=0.8\linewidth]{figs/ligo_weights.pdf}
-\end{center}
-
-\onslide{\begin{cbox}[Weighting Functions used]{blue}{}
-\begin{center}
-\begin{tabular}{ll}
-\(\tikz[baseline=-0.5ex]{\draw[color=mycolor1, line width=1.5pt](0,0)--(1,0)}\) & Custom Designed \(7^{\text{th}}\) Order Transfer Function\\
-\(\tikz[baseline=-0.5ex]{\draw[color=mycolor2, line width=1.5pt](0,0)--(1,0)}\) & Type I Chebyshev Filter of Order \(20\)\\
-\end{tabular}
-\end{center}
-\end{cbox}}\vspace{0.5em}
-\end{frame}
-
-\begin{frame}[label={sec:org114463e}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
-\begin{columns}
-\begin{column}{0.6\columnwidth}
-\vspace{-3em}
-\begin{center}
-\includegraphics[scale=1,width=1.1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
-\end{center}
-\end{column}
-
-\begin{column}{0.4\columnwidth}
-\begin{itemize}
-\item FIR Filters: order 512
-\item \(\mathcal{H}_\infty\) Filters: order 27
-\end{itemize}
-
-\vspace{1em}
-
-\onslide{\begin{cbox}[]{blue}{}
-The paper and all the Matlab Scripts used for the paper are accessible \href{https://tdehaeze.github.io/dehaeze19\_desig\_compl\_filte/}{here}.
-\end{cbox}}\vspace{0.5em}
-\end{column}
-\end{columns}
-
-\onslide{\begin{cbox}[Conclusion]{blue}{}
-Specifications: expressed as upper bounds on the filters' norm\\
-\(\mathcal{H}_\infty\) Synthesis: easily shape complex complementary filters
-\end{cbox}}\vspace{0.5em}
+\begin{frame}[label={sec:org92cdf48}]{\(\mathcal{H}_\infty\) Synthesis of Complementary filters used at LIGO}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
+\caption{\label{fig:comp_fir_ligo_hinf}
+Comparison of the FIR filters (solid) designed at LIGO with the filters obtained with \(\mathcal{H}_\infty\) synthesis (dashed)}
+\end{figure}
 \end{frame}

### 2020-07-09 matlab/matlab/comp_filters_ligo.m
Untangle useless code

@@ -262,12 +262,6 @@ xlim([freqs(1), freqs(end)]);
 ylim([1e-3, 10]);
 legend('location', 'southeast');
 
-T = table(freqs', ...
-          1./abs(squeeze(freqresp(wH, freqs, 'Hz'))), ...
-          1./abs(squeeze(freqresp(wL, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'wHm', 'wLm'});
-writetable(T, 'mat/ligo_weights.csv');
-
 % H-Infinity Synthesis
 % We define the generalized plant as shown on figure [[fig:h_infinity_robst_fusion]].
 
@@ -399,19 +393,3 @@ legend('location', 'northeast');
 linkaxes([ax1,ax2],'x');
 xlim([freqs(1), freqs(end)]);
 xticks([0.001, 0.01, 0.1, 1]);
-
-T = table(freqs', ...
-          abs(squeeze(freqresp(Hh, freqs, 'Hz'))), ...
-          abs(squeeze(freqresp(Hl, freqs, 'Hz'))), ...
-          180/pi*angle(squeeze(freqresp(Hh, freqs, 'Hz'))), ...
-          180/pi*angle(squeeze(freqresp(Hl, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'Hhm', 'Hlm', 'Hhp', 'Hlp'});
-writetable(T, 'mat/comp_ligo_fir.csv');
-
-T = table(w', ...
-          abs(H), ...
-          abs(1-H), ...
-          180/pi*angle(H), ...
-          180/pi*angle(1-H), ...
-          'VariableNames', {'freqs', 'Hhm', 'Hlm', 'Hhp', 'Hlp'});
-writetable(T, 'mat/comp_ligo_hinf.csv');

### 2020-07-09 matlab/matlab/h_inf_synthesis_complementary_filters.m

@@ -51,12 +51,6 @@ ylim([5e-4, 20]);
 xticks([0.1, 1, 10, 100, 1000]);
 legend('location', 'northeast');
 
-T = table(freqs', ...
-          1./abs(squeeze(freqresp(W1, freqs, 'Hz'))), ...
-          1./abs(squeeze(freqresp(W2, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'W1', 'W2'});
-writetable(T, 'mat/hinf_weights.csv');
-
 % H-Infinity Synthesis
 % We define the generalized plant $P$ on matlab.
 
@@ -150,11 +144,3 @@ yticks([-360:90:360]);
 linkaxes([ax1,ax2],'x');
 xlim([freqs(1), freqs(end)]);
 xticks([0.1, 1, 10, 100, 1000]);
-
-T = table(freqs', ...
-          abs(squeeze(freqresp(H1, freqs, 'Hz'))), ...
-          abs(squeeze(freqresp(H2, freqs, 'Hz'))), ...
-          180/pi*phase(squeeze(freqresp(H1, freqs, 'Hz'))), ...
-          180/pi*phase(squeeze(freqresp(H2, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'H1', 'H2', 'H1p', 'H2p'});
-writetable(T, 'mat/hinf_filters_results.csv');

### 2020-07-09 matlab/matlab/three_comp_filters.m

@@ -32,13 +32,6 @@ xlim([freqs(1), freqs(end)]);
 xticks([0.01, 0.1, 1, 10, 100, 1000]);
 legend('location', 'northeast');
 
-T = table(freqs', ...
-          1./abs(squeeze(freqresp(W1, freqs, 'Hz'))), ...
-          1./abs(squeeze(freqresp(W2, freqs, 'Hz'))), ...
-          1./abs(squeeze(freqresp(W3, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'W1', 'W2', 'W3'});
-writetable(T, 'mat/hinf_three_weights.csv');
-
 % H-Infinity Synthesis
 % Then we create the generalized plant =P=.
 
@@ -100,13 +93,3 @@ yticks([-360:90:360]);
 linkaxes([ax1,ax2],'x');
 xlim([freqs(1), freqs(end)]);
 xticks([0.1, 1, 10, 100, 1000]);
-
-T = table(freqs', ...
-          abs(squeeze(freqresp(H1, freqs, 'Hz'))), ...
-          abs(squeeze(freqresp(H2, freqs, 'Hz'))), ...
-          abs(squeeze(freqresp(H3, freqs, 'Hz'))), ...
-          180/pi*phase(squeeze(freqresp(H1, freqs, 'Hz'))), ...
-          180/pi*phase(squeeze(freqresp(H2, freqs, 'Hz'))), ...
-          180/pi*phase(squeeze(freqresp(H3, freqs, 'Hz'))), ...
-          'VariableNames', {'freqs', 'H1', 'H2', 'H3', 'H1p', 'H2p', 'H3p'});
-writetable(T, 'mat/hinf_three_results.csv');

### 2020-07-09 talk/talk.tex
Add talk pdf

--- 2019-11-05 talk/presentation.tex
@@
-% Created 2019-11-05 mar. 17:28
+% Created 2019-11-07 jeu. 22:43
 % Intended LaTeX compiler: pdflatex
@@
 \usetheme{default}
-\author{Dehaeze Thomas\textsuperscript{$\dagger$} \\ Vermat Mohit \\ Collette Christophe \\ \vspace{1cm} 08-11-2019 \\ \vspace{1cm} \textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}}
+\author{\textbf{Dehaeze Thomas}\textsuperscript{1,2,$\dagger$} \\ Vermat Mohit \textsuperscript{2} \\ Collette Christophe \textsuperscript{2} \\ \vspace{0.5cm} \textsuperscript{1}European Synchrotron Radiation Facility, Grenoble, France\\ \textsuperscript{2}Precision Mechatronics Laboratory, Brussels, Belgium\\ \textsuperscript{$\dagger$} Email: {\tt\small thomas.dehaeze@esrf.fr}\\ \vspace{0.5cm} 08-11-2019}
 \date{}
@@
 
-\begin{frame}[label={sec:org3efdf18}]{Sensor Fusion}
-In order to improve the estimate \(\hat{x}\) of \(x\), multiple sensors can be merged together using complementary filters.
-
-This permits to have
-
-High bandwidth
-\begin{itemize}
-\item need of Sensor at low frequency + sensor at high frequency
-\item need of merging the two
-\item complementary filters
-\item design of those filters using \(\mathcal{H}_\infty\)
-\end{itemize}
-
-Goal:
-\begin{itemize}
-\item Higher control bandwidth
-\item Better estimation of some physical value
-\end{itemize}
-
-Applications:
-\begin{itemize}
-\item LIGO - Vibration isolation of precise equipment
-\item UAV - Angle estimation using Accelerometer and Gyroscope
-\end{itemize}
-\end{frame}
-
-\begin{frame}[label={sec:org132896d}]{Sensor Fusion Architecture - Noise Filtering}
+\begin{frame}[label={sec:org33dd1ff}]{Motivation - Sensor Fusion Architecture}
 \vspace{-1em}
@@
 
-\onslide{\begin{cbox}[PSD of the Super Sensor's noise]{blue}{ams nodisplayskip}
-\begin{equation*}
-  \Phi_{\hat{x}} = \left|H_1\right|^2 \Phi_{n_1} + \left|H_2\right|^2 \Phi_{n_2} \Longrightarrow \text{depends on filters' norm}
-\end{equation*}
+\onslide{\begin{cbox}[]{blue}{}
+We need a synthesis method of complementary filter that allows to \textbf{shape the norm of the generated filters}.
 \end{cbox}}\vspace{0.5em}
@@
 
-\begin{frame}[label={sec:orgcb2d144}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
+\begin{frame}[label={sec:org4ce585d}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
 \vspace{-1em}
@@
 
-\onslide{\begin{cbox}[]{blue}{}
-\(W_1(s)\) and \(W_2(s)\) are proper, stable and minimum phase transfer functions
-\end{cbox}}\vspace{0.5em}
-\end{column}
-
-\begin{column}{0.5\columnwidth}
-\vspace{-3em}
-\begin{center}
-\includegraphics[scale=1,width=\linewidth]{figs/h_infinity_robust_fusion.pdf}
-\end{center}
-
 \onslide{\begin{cbox}[\(\mathcal{H}_\infty\) Synthesis]{blue}{}
@@
 \end{column}
+
+\begin{column}{0.5\columnwidth}
+\begin{figure}[htbp]
+\centering
+\includegraphics[scale=1,width=\linewidth]{figs/h_infinity_robust_fusion.pdf}
+\caption{\(\mathcal{H}_\infty\) Architecture used for the shaping of complementary filters}
+\end{figure}
+\end{column}
 \end{columns}
@@
 
-\begin{frame}[label={sec:orgff066bd}]{Validation of the proposed synthesis method}
+\begin{frame}[label={sec:org7b86e36}]{Results - \(\mathcal{H}_\infty\) Synthesis of Complementary filters}
+\begin{columns}
+\begin{column}{0.6\columnwidth}
 \begin{figure}[htbp]
 \centering
-\includegraphics[scale=1]{figs/hinf_synthesis_results.pdf}
-\caption{\label{fig:hinf_synthesis_results}
-Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
+\includegraphics[scale=1,width=\linewidth]{figs/hinf_synthesis_results.pdf}
+\caption{Frequency response of the weighting functions and complementary filters obtained using \(\mathcal{H}_\infty\) synthesis}
 \end{figure}
-\end{frame}
+\end{column}
 
-\begin{frame}[label={sec:org92cdf48}]{\(\mathcal{H}_\infty\) Synthesis of Complementary filters used at LIGO}
-\begin{figure}[htbp]
-\centering
-\includegraphics[scale=1]{figs/comp_fir_ligo_hinf.pdf}
-\caption{\label{fig:comp_fir_ligo_hinf}
-Comparison of the FIR filters (solid) designed at LIGO with the filters obtained with \(\mathcal{H}_\infty\) synthesis (dashed)}
-\end{figure}
+\begin{column}{0.4\columnwidth}
+\begin{tikzpicture}[remember picture,overlay]
+    \node[fill=white,draw,anchor=east,xshift=-1em,label={above:Poster TF1-114}] at (current page.east){%
+    \includegraphics[width=\linewidth]{../poster/poster.pdf}};
+\end{tikzpicture}
+\end{column}
+\end{columns}
 \end{frame}
